### 2024-10-23 packages/install_manuscript_packages.Rmd
initial commit

---
title: "packages"
author: "Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file installs packages.

There is no need to do this after the first installation, as it should all be 
controlled by renv().

This file is just for Rich's benefit, so that he can see how he installed them.

And this is not all of the packages. It is just the ones for writing manuscripts.

# install the libraries that we will be using #

## install ##

Next, packages for papaja and manuscript writing

```{r install-pkg}
# install.packages(c("devtools", "remotes"))
# 
devtools::install_github("crsh/papaja")
devtools::install_github("crsh/citr")
# 
install.packages("tinytex")
tinytex::install_tinytex()
# 
# # and now some useful addins for writing .Rmd from R Studio word count
devtools::install_github("benmarwick/wordcountaddin", type = "source", dependencies = TRUE)
# 
# # remedy for shortcuts in markdown writing
remotes::install_github("ThinkR-open/remedy")
# 
# # grammar checking - cool...
devtools::install_github("ropenscilabs/gramr")
```

Finally, use renv() to take a snapshot of installed packages and update the lock.file

```{r snapshot-renv}
# take a snapshot and update the lock.file
renv::snapshot() # this is only necessary when new packages or installed or packages are updated.
```

### 2024-11-26 effects.Rmd
initial commit

---
title: "plot"
author: "Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file tries to make a quick summary plot for the knot dmc project.

I made a plot like this recently to summarise Raph's results.

Eventually, we could add the rt dist for acc/inc in the raw data below, as we did for Raph's data.

# load the libraries that we will be using #

## load packages ##

```{r load-pkg}
source ("dmc/dmc.R")

pkg <- c("tidyverse", "RColorBrewer", "patchwork", "tidybayes")

lapply(pkg, library, character.only = TRUE)
```

## plot settings ##

theme settings for ggplot

```{r, eval = F}
theme_set(
  theme_bw() +
    theme(text = element_text(size = 18, face="bold"), 
          title = element_text(size = 18, face="bold"),
          legend.position = "bottom")
)

## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)
```

## load the model object and/or data ##

```{r}
## The model object is available upon request
## Please email Samantha Parker (samantha.parker@students.mq.edu.au) or Richard Ramsey (richard.ramsey@hest.ethz.ch)
## load("models/modelKN.RData") ##  
load_model ("LBA","lba_B.R")
```

# section 1 - posterior predictions #

Posterior predictions take the model and make predictions in original units (i.e., accuracy and rt).
This is always useful as a model checking process - does the model generate sensible data?

## create a ggplot ready (i.e., tidy) list of dfs at the group level ##

```{r}
## posterior predictions with gglist=TRUE
ppKNgg <- h.post.predict.dmc(hKN, cores=8, gglist = TRUE)
group_ppX <- attr(attr(ppKNgg, "av"), "gglist")
head(group_ppX)
str(group_ppX)
```

## take out relevant dfs for plotting ##

```{r}
# pps - posterior predictive
pps <- group_ppX %>% 
  pluck("pps")
head(pps)
str(pps)

# data 
# not necessary, but keeps it "tidy" i.e., one datapoint / observation per row
d <- pps %>% 
  select(S, GRP, R, data)
head(d)
str(d)

# rt quantiles
rt_q <- group_ppX %>% 
  pluck("RTs")
head(rt_q)
str(rt_q)
```

## plot accuracy ##

- dot for data
- dot and error bar for post preds

```{r}
p1.1 <- ggplot(pps, aes(x=R, y=median, 
                           fill=R, colour=R)) +
   geom_jitter(data = d,
               aes(y=data),
               position=position_jitterdodge(),
               alpha = 1, colour = "darkgrey", size = 3) +
   geom_point(alpha = 3, position = pd2, size = 3) +
   geom_line(aes(group = 1), position = pd2, colour = "black") +
   geom_errorbar(aes(ymin = lower, ymax = upper),
                width=.2, position=pd2) +
   scale_fill_brewer(palette = "Dark2") +
   scale_colour_brewer(palette = "Dark2") +
   ggtitle("accuracy") +
   labs(y="accuracy (%)") + 
   facet_grid(GRP~S)
p1.1
```

## plot the the RT quantiles ##

```{r}
p1.2 <- ggplot(rt_q, aes(x=R, y=median, colour=R)) +
   geom_point(aes(y=data),
              # position = pd2,
              alpha = 1, colour = "darkgrey", size = 3) +
   geom_point(alpha = 3, size = 3) +
   geom_line(aes(group = quantile), colour = "black") +
   geom_errorbar(aes(ymin = lower, ymax = upper),
                width=.2) +
   scale_fill_brewer(palette = "Dark2") +
   scale_colour_brewer(palette = "Dark2") +
   ggtitle("RT quantiles") +
   labs(y="reaction time (s)") + 
   facet_grid(GRP~S)
p1.2
```

## plot them together using patchwork ##

```{r}
p1.3 <- p1.1 | p1.2
p1.3

## you could save a figure at this point, if you wanted
ggsave("figures/ppreds.jpeg",
       width = 10, height = 8)
```

# section 2 #

## what about visualising parameters from the model? ##

As well as the posterior predictions, we also want to plot and summarise the estimated parameters from the posterior distribution. e.g., drift rate, response caution etc. So let's take a look at that.

Note to Raph/Sam and a reminder for Rich: One thing that took a little (or rather a lot of) figuring out was how the DMC compare.p convenience function calculates group average parameter estimates for the posterior distribution. It takes all pid posteriors, averages them first and then calculates the relevant quantiles to display and make inferences from. In other words, it first summarises parameters over pid 1, 2, 3, etc. and then calculates quantiles. This matters, because you could also calculate the quantiles without first averaging. So, the below has been tested to produce the same outputs as the compare.p function, which is re-assuring.

But instead of using compare.p, we take the posterior distributions from the samples object and then summarise and plot the results ourselves.

## wrangle all parameters and take a quick look ##

This is just to get a quick overview of all 9 parameters (before we perform any contrasts/comparisons between conditions).

## wrangle the samples first into a tidy format ##

transpose samples and pluck theta out into a list of arrays

```{r}
array_theta <- hKN %>%
  transpose() %>% 
  pluck("theta")
summary(array_theta)
str(array_theta)
```

make it tidy

```{r}
## and now use the slightly longer way with map and tidyr
theta_pid <-  map(array_theta,~as_tibble(., rownames = "chain")) %>% 
  list_rbind(names_to = "pid") %>%
  rename_with(~str_replace_all(.x, '\\.', '_')) %>% ## replace periods with underscores in names, as things work better below without periods in names
  pivot_longer(-c(pid, chain),
               values_to = "value",
               names_to = c("param", "iter"), ## this is the order of the array
               names_pattern = "([A-Za-z_\\d?]+)_(\\d+)") %>%  ## letters, _, optional digit before the underscore separator. digits after the underscore separator
  select(pid, iter, chain, param, value) %>% ## reorder columns
  arrange(pid, iter, chain, param) %>% 
  mutate(param=factor(param),
         pid=factor(pid)) %>% ## create factors
  mutate_if(is.character, as.integer) ## change from characters to integers
summary(theta_pid)
str(theta_pid)
head(theta_pid)

## data check for param
data.check <- theta_pid %>% 
  distinct(param) %>% 
  print(n=Inf)

## ok, the df has 6,534,000 rows.
## this makes sense to me. 18 pid x 250 iter x 66 chains * 22 params = 6534000
## 18*250*66*22
## =6534000
```

## create a group summary distribution ##

summarise across pid (to be consistent with the DMC compare.p function)

```{r}
theta_group <- theta_pid %>%
  group_by(iter, chain, param) %>% 
  summarise(value = mean(value)) %>% 
  ungroup() %>% 
  add_column(pid = "average") %>% ## add a column which makes clear it is the avg. not needed but useful for plotting later
  relocate(pid, .before = everything())
head(theta_group)
glimpse(theta_group)

## 6534000/18pid = 363,000 rows
```

## calculate quantiles ##

calculate quantiles per parameter at the group level

```{r}
theta_group_q <- theta_group %>%
  group_by(param) %>% 
  median_qi(value)
theta_group_q
```

and do the same per pid

```{r}
theta_pid_q <- theta_pid %>%
  group_by(pid, param) %>% 
  median_qi(value)
theta_pid_q
```

## some quick and dirty plots with all of the parameters ##

plot the distribution per parameter using a tidybayes halfeye plot

```{r}
p2.1 <- ggplot(theta_group, aes(x = value, y = fct_rev(param))) +  
  stat_halfeye(alpha = 0.9) +
  labs(x = "parameter estimate", y = "") 
p2.1

ggsave("figures/all_params.jpeg",
       width = 8, height = 6)
```

plot avg and individual pid parameters

```{r}
p2.2 <- ggplot(theta_group, aes(x = value, y = fct_rev(param))) +  
  stat_halfeye(alpha = 0.9, position = position_nudge(y=-0.5)) +
  geom_pointinterval(data = theta_pid_q, aes(xmin=.lower, xmax=.upper, 
                                           colour = pid, fill = pid),
                     position = position_dodge(width = 0.7)) +
  labs(x = "parameter estimate", y = "") +
  facet_wrap(~param, scales = "free_y") +
  theme(legend.position = "none",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())
p2.2

ggsave("figures/all_params_pid.jpeg",
       width = 10, height = 10)
```

Ok, at this point, we could wrangle the data and make some nice plots.
For code on how to do this, see folder /pilot5_dmc/ in Raph's project.
But Sam has already done that using the compare.p function and so there is no real need to reproduce those.
Instead, we should try to move on to visualise the average parameter estimates from the model in a LBA model type way.  
For that, we only need the average estimates per parameter, which we calculated above already.

# Section 3 - make a plot to visualise the results in LBA model format? ##

Can I produce a plot with RT and acc alongside model terms in a classic LBA model
visualisation?

e.g., take the raw data and make density dists, then plot alongside the parameters but in model format, rather than posterior distributions?

Let's have a play around and see.

For ease, we will just take a median value per parameter and plot to illustrate the main message.This might be justifiable, as the posterior distribution contains the uncertainty and interval estimates and we make our conclusions based on those.

This plot could just characterise/visualise the main results in a LBA schematic kind
of way. 
And that way may be more intuitive and provide an overview for readers of the main findings.

## wrangle threshold and drift rate ##

maybe just plot the average for now.

let's first take some key values of interest from the parameter medians and then combine them into one df

```{r}
## select medians of interest
theta_group_qf <- theta_group_q %>% 
  select(param, value) %>% 
  filter(!param %in% (c("sd_v_true")))
theta_group_qf

## create start point df
a_q <- theta_group_qf %>% 
  filter(param == "A") %>% 
  rename(start_point = value) %>% 
  select(-param)
a_q

## create threshold df
b_q <- theta_group_qf %>% 
  filter(str_detect(param, "^B_")) %>%
  mutate(condition = if_else(str_detect(param, "both"), "both",
                     if_else(str_detect(param, "name"), "name",
                     if_else(str_detect(param, "tie"), "tie", "untrained"))),       
         condition = factor(condition,
                            levels = c("untrained", "name", "tie", "both")),
         response = if_else(str_detect(param, "same"), "same", "diff"),
         response = factor(response,
                            levels = c("same", "diff"))) %>% 
  rename(threshold = value) %>% 
  select(condition, response, threshold)
b_q

## create drift rate df
v_q <- theta_group_qf %>% 
  filter(str_detect(param, "^mean_v")) %>% 
  mutate(condition = if_else(str_detect(param, "both"), "both",
                     if_else(str_detect(param, "name"), "name",
                     if_else(str_detect(param, "tie"), "tie", "untrained"))),       
         condition = factor(condition,
                            levels = c("untrained", "name", "tie", "both")),
         accuracy = if_else(str_detect(param, "true"), "true", "false"),
         accuracy = factor(accuracy,
                            levels = c("true", "false"))) %>% 
  rename(drift_rate = value) %>% 
  select(condition, accuracy, drift_rate)
v_q

## create a ndt df
t0_q <- theta_group_qf %>%
  filter(str_detect(param, "^t0")) %>% 
  mutate(condition = if_else(str_detect(param, "both"), "both",
                     if_else(str_detect(param, "name"), "name",
                     if_else(str_detect(param, "tie"), "tie", "untrained"))),       
         condition = factor(condition,
                            levels = c("untrained", "name", "tie", "both"))) %>%
  rename(ndt = value) %>% 
  select(condition, ndt)
t0_q
```

now create a plotting df and calculate some new variables

```{r}
theta_group_plot <- b_q %>% 
  inner_join(t0_q, by = "condition") %>% 
  inner_join(v_q, by = "condition",
             relationship = "many-to-many") %>% 
  mutate(start_point = a_q$start_point,
         b = start_point + threshold,
         xend = threshold / drift_rate) %>%
  select(condition, response, accuracy, start_point, ndt, drift_rate, threshold, 
         b, xend)
theta_group_plot

## notes on the calculations here:
## b = start point plus threshold as the threshold is the gap between where a trial starts until it reaches the threshold
## xend is required when using geom_segment (instead of geom_abline) and in this case it refers to the point on the x axis that corresponds to the threshold line
```

## plot the average ##

try geom_segment instead to restrict the plot to the threshold limit

```{r}
## if you want text labels, then this is one way to go...
labels <- tibble(x = c(1.1, 1.5, 2,
                       1.1, 1.5, 1.7,
                       1.1, 1.5, 1.7,
                       1.1, 1.5, 2.5),
                 y = c(2.5, 4.6, 3.6,
                       2.5, 3.5, 2.9,
                       2.5, 3.5, 2.9,
                       2.5, 3.4, 2.9),
                 condition = rep(c("untrained", "name",
                                   "tie", "both"), each = 3),
                 label = rep(c("start point (A)",
                               "threshold (b)", "drift rate (v)"), times = 4)) %>%
                 mutate(condition = factor(condition,
                                           levels = c("untrained", "name",
                                                      "tie", "both")))
labels

## define rectangle for ndt
rect <- tibble(condition = c("untrained", "name", "tie", "both")) %>%
  mutate(condition = factor(condition, 
                            levels = c("untrained", "name", "tie", "both")),
         ndt = c(0.258/2, 0.501/2, 0.509/2, 0.524/2))
rect

## plot          
p2.1 <- ggplot(theta_group_plot) +
  geom_hline(aes(yintercept = b, linetype=response), 
             linewidth = 1, linetype = "longdash") +
  scale_y_continuous(limits = c(2,5), breaks = seq(2,5,1)) +
  scale_x_continuous(limits = c(0,3.2), breaks = seq(0,3.2,0.5)) +
  geom_segment(aes(x = ndt/2, y = start_point, 
                   xend = (ndt/2)+xend, yend = b,
                   colour = accuracy, linetype = accuracy), linewidth=1) +
  scale_colour_brewer(palette = "Dark2") +
  theme(legend.position = "none",
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        panel.grid.minor = element_blank()
        ) +
  xlab("accumulation time") +
  ylab("a.u.") +
  geom_rect(data = rect, aes(xmin = 0, xmax = ndt, ymin = -Inf, ymax = Inf), 
            alpha = 0.5, fill="darkgrey") +
  facet_wrap(~condition, nrow = 1) +
  geom_text(data = labels,
            aes(x=x,y=y, label = label),
            fontface = "bold")
p2.1

ggsave("figures/lba_summary.jpeg",
       width = 8, height = 5, dpi=800)
```

How about we try to add rt and acc desnity plots like we did before with Raph's data?

# Section 4 #

## read in the raw data and create density plots ##

```{r}
## extract data from the model object
array_data <- hKN %>%
  transpose() %>% 
  pluck("data")
summary(array_data)
str(array_data)

## make it tidy
data <-  map(array_data,~as_tibble(., rownames = "row")) %>% 
  list_rbind(names_to = "pid")
head(data)
summary(data)

## check it
data %>% 
  distinct(pid)
```

data check

```{r}
data %>% 
  distinct(S, GRP, R) %>% 
  arrange(S, GRP, R)

data %>%
  group_by(S, GRP, R) %>% 
  tally()
```

add an accuracy column

```{r}
data <- data %>%
  rename(rt=RT) %>% 
  mutate(response = R,
         accuracy = if_else(S == "match" & R == "same", "true",
                    if_else(S == "mis" & R == "diff", "true", "false")),       
         response = factor(response,
                          levels=c("same", "diff")),
         accuracy = factor(accuracy,
                           levels=c("true", "false")),
         condition = if_else(str_detect(GRP, "both"), "both",
                     if_else(str_detect(GRP, "name"), "name",
                     if_else(str_detect(GRP, "tie"), "tie", "untrained"))),
         condition = factor(condition,
                            levels = c("untrained", "name", "tie", "both")))
head(data)
```

check

```{r}
data %>% 
  distinct(S, GRP, R, response, accuracy, condition) 
```

## create summary data ##

## summary data ##

at the pid level

```{r}
acc_summary_pid <- data %>% 
  group_by(pid, response, condition) %>%
  summarise(sum = sum(as.numeric(accuracy)),
            n=n(),
            frac = n/sum,
            perc = frac*100,
            .groups = "drop")
acc_summary_pid
```

```{r}
rt_summary_pid <- data %>% 
  group_by(pid, response, condition, accuracy) %>%
  summarise(mean = mean(rt, na.rm = TRUE),
            n=n(),
            sd = sd(rt, na.rm = TRUE),
            sem=sd/sqrt(n),
            .groups = "drop")
rt_summary_pid
```

at the group level

```{r}
acc_summary <- data %>% 
  group_by(response, condition) %>%
  summarise(sum = sum(as.numeric(accuracy)),
            n=n(),
            frac = n/sum,
            perc = frac*100,
            .groups = "drop")
acc_summary
```

```{r}
rt_summary <- data %>% 
  group_by(response, condition, accuracy) %>%
  summarise(mean = mean(rt, na.rm = TRUE),
            n=n(),
            sd = sd(rt, na.rm = TRUE),
            sem=sd/sqrt(n),
            .groups = "drop")
rt_summary
```

join the data (not sure this is necessary, but it helps with plotting text
for the accuracy summary)

```{r}
# data <- data.model.v4 %>%
#   inner_join(select(acc_summary, condition, perc), by = "condition") 
# head(data.model.v4)
```

## some density plots ##

```{r}
p4.1 <- ggplot(data, aes(x=rt, y=after_stat(count))) +
  geom_density(aes(colour = accuracy, fill = accuracy),
               alpha = 0.5, position = "identity") +
  # xlim(0,2.5) +
  scale_x_continuous(limits = c(0,2.5), breaks = c(0,2,1)) +
  geom_vline(data = rt_summary, aes(xintercept = mean, colour = accuracy),
             linetype = "dashed", linewidth = 1) +
  geom_text(data = acc_summary, aes(x=2, y=300,
                                    label = sprintf("%.f%s", perc, "% accuracy")),
            color = "darkgrey", size = 5, fontface="bold") +
  scale_fill_brewer(palette = "Dark2") +
  scale_colour_brewer(palette = "Dark2") +
  facet_grid(response~condition) 
p4.1

ggsave("figures/density_rt_acc.jpeg",
       width = 12, height = 8, dpi=800)
```

## plot density and lba together? ##

```{r}
p4.2 <- (p2.1 / p4.1) +
  plot_layout(guides = "collect")
p4.2

ggsave("figures/lba_rt_acc.jpeg",
       width = 12, height = 10, dpi=800)
```

### 2024-11-26 manuscript/manuscript.Rmd
initial commit

---
title             : "Evidence accumulation modelling offers new insights into the cognitive mechanisms that underlie linguistic and action-based training"
shorttitle        : "Decision models and experience-dependent plasticity"
author: 
  - name          : "Samantha Parker"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "School of Psychological Sciences, 16 University Avenue, Macquarie University, NSW 2109"
    email         : "samantha.parker@students.mq.edu.au"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Data curation"
      - "Formal analysis"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Emily S. Cross"
    affiliation   : "2"
    role:
      - "Conceptualization"
      - "Resources"
      - "Writing - Review & Editing"
  - name          : "Richard Ramsey"
    affiliation   : "2"
    role:
      - "Conceptualization"
      - "Visualisation"
      - "Supervision"
      - "Project Administration"
      - "Validation"
      - "Writing - Review & Editing"
affiliation:
  - id            : "1"
    institution   : "Macquarie University"
  - id            : "2"
    institution   : "ETH Zürich"
authornote: |
  Samantha Parker. School of Psychological Sciences, Macquarie University.
  Emily S. Cross. Social Brain Sciences Lab, Department of Humanities, Social and Political Sciences (D-GESS), ETH Zürich.
  Richard Ramsey. Neural Control of Movement Lab, Department of Health Sciences and Technology (D-HEST) and Social Brain Sciences Lab, Department of Humanities, Social and Political Sciences (D-GESS), ETH Zürich.
  <!-- Enter author note here. -->
abstract: |
  Evidence accumulation modelling has been shown to uncover new insights into the cognitive mechanisms that underlie decision making from behavioural data. By jointly modelling reaction time and accuracy data, such decision models estimate latent variables that represent distinct computaitonal processes, such as stimulus encoding, response caution and the quality of information processing. In this study we use an evidence accumulation model, the Linear Ballistic Accumulator (LBA), to shed new light into the mechanisms that underlie learning based on linguistic and action-based training. The LBA model is applied to behavioural data from a previously published training study where participants learn to name, tie or name and tie a set of knots. Our results show that training is multifaceted and associated with an increase in stimulus-encoding time, a reduction in response caution, as well as an increase in the speed of information accumulation. Furthermore, the results showed that there was an added benefit to the rate of evidence accumulation when naming and tying experience were combined. This latter finding suggests that performance benefits from multi-modal training may be instantiated in computational processes that are associated with the quantity and quality of information accumulation during decision making. Overall, in applying this computational approach to accuracy and reaction time data, we uncover new insights into the mechanisms that govern experience-dependent plasticity.

  *Public significance statement:* The results of this study show that multi-modal training, which spans linguistic and action-based content, increases the quality of information that is gained through perception to make a decision. These results provide a novel computational account of performance benefits that are often observed from multi-modal training, which will aid theory development on learning and plasticity within cognitive science.

  <!-- https://tinyurl.com/ybremelq -->
keywords          : "evidence accumulation modelling, training, learning, action, naming, cognitive mechanisms, plasticity"
wordcount         : "6703"
bibliography      : ["references.bib", "r-references.bib"]
floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man, donotrepeattitle"
output            : papaja::apa6_pdf
# output            : papaja::apa6_word
note              : "\\clearpage" ## this moves the author note section to a second page
editor_options: 
  chunk_output_type: console
header-includes:
  - \raggedbottom
---

```{r, include=FALSE}
## just include when de-bugging tinytex
# options(tinytex.verbose = TRUE)
```

```{r setup, include = FALSE}
pkg <- c("papaja", "citr", "tidyverse", "RColorBrewer", "patchwork")

lapply(pkg, library, character.only = TRUE)

r_refs(file = "r-references.bib")
my_r_citation <- cite_r(file = "r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r plot-settings}
## theme settings for ggplot
theme_set(
  theme_bw() +
    theme(text = element_text(size = 18), 
          title = element_text(size = 18),
          legend.position = "bottom")
)

## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)
```

```{r global-chunk-settings}
## set the figure options
knitr::opts_chunk$set(fig.pos='H', out.extra = '', out.height = "67%",
                      fig.align = "center") # initial version
```

# Introduction

Evidence accumulation models are a class of computational models used to understand the latent cognitive processes that underlie human decision making. Typically, these models use accuracy and reaction times collected in speeded choice tasks to draw insights about the psychological mechanisms that underlie those decisions. The application of this modelling approach within the domain of cognitive psychology has led to a number of novel insights about the mechanisms that underlie processes such as lexical decision making [@wagenmakers2008], ageing [@ratcliff2001; @ratcliff2010] and perceptual discrimination [@ratcliff2008]. Importantly, these insights are often not evident from more conventional analyses of accuracy and reaction time data. Given these characteristics, we applied an evidence accumulation model, the Linear Ballistic Accumulator (LBA; @brown2008), to behavioural data from a prior published study that used neuroimaging to examine the effects of different types of training on object knowledge and perception [@cross2012d]. In contrast to the original study’s analysis, which analysed accuracy and reaction time separately, in this paper we apply an evidence accumulation model to uncover novel insights into the latent computational processes that underlie linguistic and action-based learning.

Whilst it is common for researchers to draw conclusions from a separate analysis of accuracy and reaction time, it is unclear how to combine these measures into a single measure by which to quantify task difficulty or subject ability [@wagenmakers2007]. Consider, for example, a perceptual discrimination task that requires participants to indicate whether two images are of the same or different objects [@cross2012d; @weisberg2007]. Objects could belong to two categories of training, one where the participants learn to name the object (name-based) and the other where the participant interacts physically with the object (action-based). Objects that are subject to name-based training are discriminated faster but with more errors, than objects that are the subject of action-based training. It is unclear from a separate analysis of accuracy and reaction time data in which condition performance is superior. This is because without a principled way to combine accuracy and RT, these measures are incommensurable. While this example demonstrates the well-documented speed-accuracy trade-off, where less cautious responding is associated with faster, but more error prone responding, and more cautious responding is associated with slower but more accurate responses, this is just one of the many ways in which accuracy and reaction times can interact [@ratcliff1998].

Evidence accumulation models provide a principled way to combine accuracy and reaction time, enabling direct insight into the processes that underlie speeded decisions [@brown2008; @ratcliff2002]. They do so by combining accuracy and the distribution of RT for correct and error responses in order to estimate parameters of a model that can separate the effects of response caution from difficulty. While there are many different varieties of evidence accumulation model, they all share a similar basic framework [@donkin2009]. Namely, these models all assume that when making a decision, evidence is sampled from the environment and that information is used as evidence for one of the potential responses. As soon as evidence in favour of a particular response reaches a threshold, the decision process is terminated and the corresponding response is made.

All evidence accumulation models aim to provide estimates of four common aspects of the decision making process: the rate at which evidence accumulates in favour of a decision (drift rate), how much evidence is required before a response is reached (threshold), the amount of evidence in favour of a response that exists at the outset of a decision (start point noise) and the amount of time it takes to complete all processes that are thought to fall outside the decision, including stimulus encoding and motor responding (non-decision time). These parameters quantify the latent variables of the decision-making process. Threshold, for example, measures the amount of evidence necessary to make a response. As threshold increases, responses take longer but are more likely to be correct. In this way, threshold can account for differences in response caution. Drift rate, on the other hand, is thought to reflect the signal-to-noise ratio of the stimulus. In this way, drift rate quantifies the deterministic component of the accumulation process. Drift rate, therefore, measures both the quantity and the quality of information in the system and can provide a direct measure of task difficult or subject ability [@lewandowsky2018].

Assessing how parameters vary as a function of experimental conditions has the potential to reveal more about the mechanisms that underlie the decision-making process than is apparent from an analysis of accuracy and RT alone [@dutilh2019; @donkin2009; @evans2019; @evans2020]. Perhaps one of the most persuasive examples of this approach comes from the ageing literature. One typical finding within the ageing research is that response times increase with increasing age, a finding that led to the conclusion that there is a cognitive decline associated with ageing [@salthouse1996]. Application of an evidence accumulation model to data from such tasks, however, reveals that rather than older adults performing more poorly on speeded response time tasks than younger adults, differences in responses are actually due to differences in response caution [@ratcliff2004]. That is, older adults are more cautious responders than younger adults, requiring a higher level of evidence to trigger a response. Importantly, this inference was not available from a traditional analysis of accuracy and RT. This is just one example in which evidence accumulation modelling has allowed researchers to draw inferences that were unavailable in a traditional analysis of behavioural data [@white2022]. Evidence accumulation modelling thus provides us with an opportunity to interrogate behavioural data to uncover novel insights into the latent variables that underlie decision making in a way that a traditional analysis cannot.

In the present paper, we use the evidence accumulation approach to shed new light on the mechanisms that underlie two kinds of learning based on different types of training experience. Specifically, we apply the Linear Ballistic Accumulator (LBA) (Brown & Heathcote, 2008) to behavioural data from an existing multi-session training dataset that taught participants how to tie and name novel knots (Cross et al., 2012). In making use of existing data not only do we provide novel insights into the mechanisms that underlie different types of training, but we also demonstrate how computational modelling can lead to conclusions that are not readily apparent from a traditional analysis of accuracy and RT alone.

In the domain of training, the most typical behavioural finding is that with increased repetition of a task response times decrease and accuracy increases [@simons2016; @vonbastian2022]. While this finding is most commonly interpreted as evidence of improved task performance, it provides few insights about the latent processes that underlie training-related changes. Evidence accumulation modelling of training effects, on the other hand, has shown that task repetition can influence the rate at which information accumulates, the amount of evidence needed to trigger a response and non-decision time [@dutilh2009; @dutilh2011; @reinhartz2023]. Studies that have used these computational modelling techniques to investigate how task repetition improves response times report an increase in the rate of information accumulation associated with repeated performance of the same speeded task [@dutilh2009; @dutilh2011; @liu2012; @ratcliff2006; @zhang2014].

These studies have also found that while the rate of information accumulation increases during practice, these effects are also associated with decreased boundary separation (Dutilh et al., 2011; Dutilh et al., 2009; Liu & Watanabe, 2012; Zhang & Rowe, 2014). That is, with increased repetition of a task, participants require less evidence to trigger a decision. This finding has led some authors to suggest that training effects may elicit a shift in response caution, leading people to prioritise speed over accuracy. The influence of training on non-decision time has less consistently been reported in the literature, with some studies suggesting that training decreases non-decision timing (Dutilh et al., 2011; Dutilh et al., 2009) and other studies reporting no influence on this parameter [@strobach2013]. Dutilh and colleagues (2011; 2009), for example, found that improved performance on a repeated lexical decision task was associated with faster drift rates, lower response caution and a decrease in non-decision time. This finding led the authors to conclude that training effects were multifaceted.

These conclusions, however, have been drawn from a limited number of perceptual discrimination tasks, with the vast majority of studies using either random dot motion [@cochrane2023] or lexical discrimination tasks (Dutilh et al., 2011). Similarly, these studies typically investigate training related changes that are induced by task repetition (Dutilh et al., 2011; Dutilh et al., 2009). In contrast, we applied evidence accumulation modelling to understand and compare the mechanisms that underlie different types of training during a complex real-word perceptual discrimination task.

Cross and colleagues (2012), across five days, taught knot-naïve participants to tie or name a set of knots that were previously unknown to them. Performance on, and neural activity during, a perceptual discrimination task was then measured. Participants were required to discriminate whether two images were of the same or different knots. Stimuli fell into one of four training categories; training about how to name and tie the knot, knowledge of how to name the knot only (linguistic-based training), training in how to tie the know only (action-based training) and no training of the knot. Consistent with typical training effects the authors reported a decrease in response times as training days progressed. A somewhat surprising effect of training type on response times also emerged, with participants performing the perceptual discrimination task faster for untrained compared to trained knots. There were no effects of training in terms of accuracy data. The authors concluded that these behavioural findings were suggestive that the newly formed linguistic and action knowledge that was developed via training was taking time to process when presented with a familiar set of knots. This conclusion, however, is based upon a traditional analysis of observed variables where reaction times reflect the total time taken to complete the decision-making process, including stimulus processing and motor responding. Application of evidence accumulation modelling, on the other hand, provides us with an opportunity to break down a decision into the latent variables that underlie the acquisition of linguistic and action-based knowledge induced by training.

The aim of the present study was to investigate to what extent parameters in the LBA model vary by each type of training. Given previous studies have suggested that increased drift rate, decreased response caution and decreased non-decision time (Dutilh et al., 2011; Dutilh et al., 2009; Zhang & Rowe, 2014) are all associated with training-related changes, we hypothesised that improvements in perceptual discrimination due to training would be associated with (1) an increase in drift rate; (2) a decrease in response caution; (3) a decrease in non-decision time or (4) some combination of these factors. Furthermore, it was also possible that the extent to which these parameters varied by training type (naming, tying, naming & tying, untrained) may differ, although we had no specific predictions about the direction of this hypothesis.

# Methods

## Transparency and Openness Statement

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [@simmons2012]. In addition, the hypotheses and planned analysis for this paper were preregistered in advance (see our pre-registration here: [https://aspredicted.org/6ztj-45s5.pdf](https://aspredicted.org/6ztj-45s5.pdf)). We deviated from our pre-registration in one way. Originally, we had intended to include in our model data from both a pre- and post-training session. That is, we intended to compute the difference in parameter estimates between the pre- and post-training variable. Instead, we only included data from the post-training session in our final analysis. This deviation from preregistration was necessary as the model building process could not be completed with both pre- and post-training session variables included, due to the large number of parameters being fit and the model failing to converge. By removing the pre-training session data, the number of parameters was reduced by half. As a result, the model could converge and we were able to successfully complete the model building process.

Importantly, given that we were interested in the mechanisms that underlie training vs. no-training, as well as comparisons between different types of training (linguistic vs. action vs. both), only the post-training session was necessary to capture and quantify these effects. Indeed, Cross and colleagues (2012), in their original study, included only results from the post-training session in their final analysis, as this session is thought to be more consistent and reflect the participants' learned state [@weisberg2007]. All other aspects of the pre-registration were unchanged. In addition, all of the analysis code used in this paper have been made available on the open science framework ([https://osf.io/ea6gk/](https://osf.io/ea6gk/). Given that the data were collected several years before 2012, it was not yet routine to request explicit consent to share data publicly. Therefore, the raw data are only available from the authors upon request. Since the current manuscript was written in R using the papaja() package [@R-papaja], it is also computationally reproducible and available via GitHub ([https://github.com/rich-ramsey/knot_dmc](https://github.com/rich-ramsey/knot_dmc)).

## Dataset

We applied the LBA model to a previously published dataset from Cross and colleagues (2012). This study used fMRI to examine brain activity whilst participants completed a speeded perceptual discrimination task before and after training. The data used in the current study, therefore, were collected in or before 2012. Training consisted of participants learning to name 10 knots, tie 10 knots and name and tie a further 10 knots, while a final 10 knots remained untrained (i.e., no information about how to tie the knot or what it was called was experienced during the training period). Before and after the knot training portion of the study, participants were required to complete 80 trials of a perceptual discrimination task. In this task, participants had to decide whether two photographs were of the same or different knots. Each pair of knots was selected from the same learning class (i.e., name, tie, both name and tie or untrained knots). When photographs were of the same knot, the viewing angle of the two photographs differed, so the stimuli presented were never identical. Of the 80 trials, 50% of the knots were the same and 50% of the knots were different. Both accuracy and response times (ms) of the perceptual discrimination task were recorded. As we were interested in modelling only the behavioural results of the perceptual discrimination task, we summarise the aspects of the dataset relevant to the present study below and refer readers to the original paper for all other details (see Cross et al., 2012).

The data included in the present paper differed from that reported by Cross and colleagues (2012) in a number of key ways. First, while 30 participants took part in the behavioural portion of the original study, only data from the 20 participants who comprised the final fMRI sample were available for re-analysis. The decision to include only the final training session in the LBA model meant that a further two participants were excluded from modelling as they did not complete the final session of the perceptual discrimination task. Therefore, 18 participants were included in the present study (M = 19.4 years, age ranged from 17 – 27 years). Second, unlike Cross and colleagues who included the post-training session across all five days in their analysis of accuracy and RT, we included only the post-training session on the final day of training (Day 5 post-training). Given the aim of our study was to use evidence accumulation modelling to examine the cognitive mechanisms underlying linguistic and action-based training, it was sufficient to use the training effects evident on the last day of training for our analysis. That is, general training effects could be compared via a comparison between the untrained and trained conditions, and between each type of training category (e.g. linguistic vs. action vs. both). The benefit of including only the final post-training sessions was a computationally simpler model.

The present study therefore had a single within-subjects factor of training type with four levels (naming/tying/both/untrained). During naming training, participants were shown a video of a knot being rotated through 360 degrees with the name displayed in the top right-hand corner of the screen. During tying training, participants were shown a video of how to tie the knot from a first-person perspective and instructed to correctly tie each of the knots in this category by following along with the video at least once per day of training. During both naming and tying training participants were shown a video of how to tie the knot with the name of the knot displayed in the top right-hand corner of the screen and were instructed to correctly tie each of the knots in this category at least once per day of training. Knots in the untrained condition were unfamiliar to participants. Assignment of each of the 40 knots was counterbalanced across training condition and participant.

## LBA data analysis

### Model Specification

We fit the LBA model to each participants’ data for the final post-training session. The LBA model has one accumulator for each response, each with potentially different parameter values. In this design, that meant that there was one accumulator for pairs of knots that were the same and another accumulator for pairs of knots that were different. Each accumulator possessed the following parameters; start point noise (A), representing the amount of information in each accumulator at the beginning of a decision; threshold (b) which represents the amount of evidence necessary in order to trigger a decision (in the present study this was represented in terms of the difference between the top of the start point distribution and the response threshold ($B = b - A \ge 0$); drift rate (v) the rate at which evidence accumulates for each response; and non-decision time ($Ter \ge 0$) the amount of time it takes to complete all other processes that fall outside the decision making process, including stimulus encoding and motor responding. We allowed the threshold parameter to vary by Training Type (name, tie, both, untrained) and Response (participant’s response as to whether the two knots match vs. no-match). The drift rate parameter was allowed to vary by Training Type and an accumulator match factor, which denotes the match between the accumulator and the stimulus. Specifically, if the stimulus displayed two of the same knots, then the accumulator for the “match” response was the TRUE or matching accumulator, whereas the accumulator for the “no match” response would be the FALSE or mismatching accumulator. In this way the difference between the TRUE and FALSE accumulator captures both the quantity and quality of information accumulating about the stimulus. The larger the difference between the TRUE and FALSE accumulators, the higher the quality of information accumulating in favour of that response (Lewandowsky & Oberauer, 2018). Given this, we operationalised drift rate as the difference between the TRUE and FALSE accumulator. The standard deviation for the TRUE accumulator was allowed to vary by the accumulator match factor, whereas the standard deviation for the FALSE accumulator was fixed at 1 to make the model identifiable (Donkin et al., 2009). The non-decision time parameter was allowed to vary by Training Type, while the standard deviation of non-decision time was fixed at 0. We fixed a single value for start point noise (A).

### Model estimation

Model estimation was carried out in a Bayesian statistical framework using the Dynamic Models of Choice software that is written in the R programming language [@heathcote2019]. Full details of priors and sampling methods are provided in supplementary materials. Following prior work [@castro2019], priors were selected using a weakly informative approach. That is, priors were chosen to have little influence on estimation (graphical summaries of how posteriors were updated relative to priors are provided in supplementary materials). Sampling occurred in two steps. First, sampling was carried out separately for each individual participant. The results of this step then provided the starting points for the full hierarchical model. Inspection of graphical summaries confirmed that the model provided an adequate account for all major aspects of the data. Cumulative distribution functions comparing data with the model are provided in supplementary materials.

### Parameter Estimates

In order to make inferences about the mechanisms that underlie different types of training, we compared the influence of training type in the final post-training session across different parameter estimates. Specifically, the threshold, drift rate difference and non-decision time parameters were estimated for each training type (untrained, naming, tying, both). Each posterior sample for each individual participant was then averaged across individuals to obtain the distribution of group average differences for each parameter. Pairwise comparisons on these posterior distributions were then computed between each training type and the untrained condition, as well as between each training type. To summarise the distribution of parameters of interest we report the median of the posterior distribution together with 95% quantile intervals of the distribution in square brackets.

# Results

## Analysis of Observed Variables

Prior to conducting evidence accumulation modelling, we first analysed accuracy and reaction time separately. The purpose of this analysis was primarily to assess the effect of training as in the original paper (Cross et al., 2012). In particular, given that the data included in our analysis differed in a number of ways to that reported by Cross and colleagues, we sought to estimate the size of training effects evident in a separate analysis of accuracy and RT. These analyses were conducted using a Bayesian estimation approach to multilevel modelling. As these analyses were not the main focus of this paper, we report them briefly below. Full details, however, can be found in supplementary materials.

There was some evidence of an effect of training type on accuracy (see Figure 1A). Relative to the untrained condition (M = 87.4, SD = 33.3) accuracy was higher for knots that received both naming and tying training (M = 88.9, SD = 31.5), but was lower in both the tying (M = 85.1, SD = 35.6) and naming conditions (M = 83.8, SD = 36.9). There also appeared to be an effect of training type in RT (see Figure 1B) relative to knots that received no training (M = 1139 ms, SD = 345 ms), participants responded faster to knots that received naming training (M = 1055 ms, SD = 347 ms), tying training (M = 1119 ms, SD = 356 ms) and knots that received both naming and tying training tying training (M = 1082 ms, SD = 344 ms).

(ref:accuracy-rt-caption) Accuracy and Reaction Time by Training Type and Session. (A) Percent correct on the perceptual discrimination task by training type. (B) Mean reaction time (ms) on the perceptual discrimination task by training type. Black points denote group means, while error bars represent within subjects’ standard errors of the mean. Grey points denote individual subject means.

```{r accuracy-rt-plot, fig.cap = "(ref:accuracy-rt-caption)"}
knitr::include_graphics("../figures/from_file/acc_rt.png")
```

## Evidence Accumulation Modelling

### Thresholds

Inspection of the posterior distributions for the threshold parameter of the LBA model revealed evidence to suggest that thresholds significantly differed by Training Type. Specifically, thresholds were lower in all three training conditions, naming (0.76 [0.64, 0.88]), tying, (0.68 [0.57, 0.79]) and both naming and tying training (1.01 [0.84, 1.19]) relative to the untrained condition (2.80 [2.60, 3.03]) (see Figure 2A).

Pairwise comparisons between each training condition and the untrained condition confirmed that there was a substantial reduction in thresholds in all three trained conditions compared to the untrained condition (see top row of Figure 2B). In contrast, pairwise comparisons between each type of training revealed little evidence to suggest that thresholds differed substantially by type of training (see bottom row of Figure 2B). Therefore, these results suggest that participants were substantially less cautious when responding to all trained knots compared to untrained knots.

(ref:threshold-caption) Posterior Distributions for the Threshold Parameter by Training Condition and Pairwise Differences between Training Conditions. (A) This panel demonstrates the posterior distributions for the threshold parameter of the LBA model by training condition. (B) This panels shows the difference in the posterior distribution for the threshold parameter between each training condition relative to the untrained condition (top row) and between each training condition (bottom row). In all graphs, black points represent the median value of the posterior distribution, while thick black lines represent the 95% quantile interval of the distribution. In difference graphs, the red line represents the zero point of the distribution.

```{r threshold-plot, fig.cap = "(ref:threshold-caption)"}
knitr::include_graphics("../figures/from_file/thresholds.png")
```

### Drift rate

In order to quantify the influence of training type on the quality and quantity of information accumulating from the stimulus, we computed the difference between the TRUE and FALSE drift rate (drift rate difference). As can be seen in Figure 3A drift rate difference appeared substantially higher for knots that received both tying and naming training (3.12 [2.74, 3.53]), relative to naming (2.30 [2.01, 2.60]), tying (2.39 [2.13, 2.67]) and untrained conditions (2.08 [1.85, 2.31]). Pairwise comparisons between training conditions confirmed that there was evidence to suggest that the quality of evidence accruing was higher for knots that received both naming and tying training relative to knots that received naming, tying and no training (See Figure 3B). The posterior distributions for each of these comparisons was positive and with values entirely above zero.

As can be seen in Figure 3B there was also evidence that the drift rate difference was greater for knots that received naming training relative to no training and tying training relative to no training, respectively. The posterior distributions for each of these comparisons was largely positive, with most values falling above zero. In contrast, there was no evidence to suggest that drift rate differed between the naming and tying conditions (bottom right-hand graph in Figure 3B), with the difference centred around zero, with values falling both above and below zero.

(ref:drift-rate-caption) Posterior Distributions for the Drift Rate Difference Parameter by Training Condition and Pairwise Differences between Training Conditions. (A) This panel demonstrates the posterior distributions for the drift-rate parameter of the LBA model by training condition. (B) This panels shows the difference in the posterior distribution for the drift-rate parameter between each training condition relative to the untrained condition (top row) and between each training condition (bottom row). In all graphs, black points represent the median value of the posterior distribution, while thick black lines represent the 95% quantile interval of the distribution. In difference graphs, the red line represents the zero point of the distribution.

```{r drift-rate-plot, fig.cap = "(ref:drift-rate-caption)"}
knitr::include_graphics("../figures/from_file/drift_rate.png")
```

In summary, a clear benefit emerged in terms of the quality and quantity of information processing during task performance following training that jointly involved both types of learning (naming and typing). A smaller benefit was observed for information processing when only one type of training was provided (naming or tying). In other words, all types of training, albeit to different degrees, made the drift-rate parameter associated with the accurate response steeper than the incorrect response. All things being equal, the benefit of such drift-rate effects to performance would be faster and more accurate responses.

### Non-decision time

As Figure 4 demonstrates, relative to the untrained condition (0.26 [0.22, 0.29]) non-decision time was significantly higher for knots that received naming (0.50 [0.47, 0.53]), tying (0.51 [0.48, 0.54]) and both naming and tying training (0.52 [0.50, 0.55]).

Pairwise comparisons showed that non-decision time was substantially higher in all three training conditions relative to the untrained condition with difference values being positive and entirely above zero. In contrast, pairwise comparison revealed there to be no evidence to suggest that non-decision time differed by training type, with difference values centered around zero (see Figure 4B).

Given that motor preparation for such a simple key-pressing task is unlikely to be affected by this type of training, we suggest that these results must reflect the longer time taken to encode the stimulus following the development of newly acquired linguistic or action knowledge.

(ref:ndt-caption) Posterior Distributions for the Non-decision Time (ndt) Parameter by Training Condition and Pairwise Differences between Training Conditions. (A) This panel demonstrates the posterior distributions for the ndt parameter of the LBA model by training condition. (B) This panels shows the difference in the posterior distribution for the ndt parameter between each training condition relative to the untrained condition (top row) and between each training condition (bottom row). In all graphs, black points represent the median value of the posterior distribution, while thick black lines represent the 95% quantile interval of the distribution. In difference graphs, the red line represents the zero point of the distribution.

```{r ndt-plot, fig.cap = "(ref:ndt-caption)"}
knitr::include_graphics("../figures/from_file/ndt.png")
```

### Summary

To help visualise the pattern of results across conditions, in Figure 5 we plot the mean values of each parameter and each condition using the structure of a decision model plot. This plot does not form part of our inferential analytical approach. Instead, the plot provides a visual aid to highlight differences between conditions, as well as how the parameters may combine together within one particular condition. For example, we think that the plot nicely illustrates the differences between conditions in non-decision time (grey rectangle), thresholds (dashed black lines) and drift rate (solid green and dashed orange lines).

(ref:lba-summary-caption) A summary of the key findings visualised using the structure of a decision model plot. Each panel represents an experimental condtion and displays the same information. The grey column represents non-decision time (ndt) with its thickness representing the amount of ndt. Start point (A) was fixed across conditions and does not vary. For ease of presentation, two thresholds (b, dashed black lines) are displayed per condition. The lower threshold represents a mismatch between the displayed knots and the higher threshold represents a match between the displayed knots on a given trial. The mean drift rate (v) for true (solid green) and false (dashed orange) responses are also displayed.

```{r lba-summary-plot, fig.cap = "(ref:lba-summary-caption)"}
knitr::include_graphics("../figures/lba_summary.jpeg")
```

# Discussion

The aim of the present study was to use evidence accumulation modelling to investigate the cognitive mechanisms that underlie linguistic and action-based training in a simple knot-tying and knot-naming task. Our results revealed that the effects of training are multifaceted, in terms of the latent cognitive processes involved. In other words, training impacted several cognitive sub-processes that, in combination, determine subsequent task performance. In addition, an added benefit was observed for the speed of information accumulation when naming and tying experience were combined. This latter finding suggests that a multi-modal training protocol can aid the quantity and quality of information processing during decision making. Below, we discuss several ways in which our findings advance our understanding of how cognitive systems are shaped by different types of knowledge acquisition and experience. More generally, we also outline why future work may benefit from taking a more computational approach to understand the effects of training on learning and performance.

## Training leads to general decreases in response caution and general increases in non-decision time

As predicted, our results showed that relative to the untrained condition, response caution was lower in all of the training conditions. That is, participants required less evidence to trigger a decision in the perceptual discrimination task when presented with any of the trained knots compared to untrained knots. This finding is in consistent with other studies that have found task repetition to be associated with decreased response caution (Dutilh et al., 2011; Dutilh et al., 2009; Liu & Watanabe, 2012; Zhang & Rowe, 2014). Extending these previous studies, our results also suggest that this decrease in response caution is a general effect and does not differ by type of training. Specifically, we found no evidence to suggest that changes in response caution differed whether knots received naming or tying training, or a combination of both. Given that lower response caution signals a tendency to prioritise the speed over the accuracy of responses, these results suggest that training, in part, provides a general bias to favour quicker responses.

The effects of training on non-decision time were consistent with the behavioural findings reported in the original study (Cross et al., 2012). Specifically, the original authors found reaction times to be higher in all three training conditions relative to the untrained condition. In the current study, we found all types of training to be associated with an increase in non-decision time. That is, participants took approximately twice as long to complete all other mechanisms that fall outside the decision-making process, such as stimulus encoding and motor responding, when presented with a trained compared to an untrained knot. We found no evidence to suggest that the non-decision time parameter was modulated by training type. When these results are taken on their own, and given that motor preparation for such a simple key-pressing task is unlikely to be affected by this type of training, we infer that these results reflect the longer time taken to encode the stimulus following the development of newly acquired linguistic or action knowledge. In other words, we consider these effects to reflect the added cognitive processes that are triggered by viewing a stimulus that has been in some way enriched by training experience.

As a point of comparison, however, it is noteworthy that other training studies have either failed to find an association between training and non-decision time (Strobach et al., 2013) or they have reported training to decrease non-decision time (Dutilh et al., 2011; Dutilh et al., 2009). These prior studies used largely different forms of training to the current study. For example, Dutilh and colleagues (2009) trained participants on a lexical decision task. The lexical task involved making a word vs non-word judgment to strings of text and training involved repeatedly performing the same task across several days. Therefore, it is currently unclear how different types of training and experience may impact non-decision time, but it seems a valuable component to include when building models of the computational processes involved in experience-dependent plasticity.

## The combination of linguistic and action-based training increases the quality of information accumulation

We found evidence to support the hypothesis that training increases the rate at which evidence accumulates. Relative to knots that were untrained, there was an increase in the rate at which evidence accumulated following all training conditions (naming, tying and both). The finding that training generally increases the rate at which evidence accumulates is consistent with previous studies that have found repeatedly completing speeded tasks to be associated with an increase in the rate at which information accumulates (Dutilh et al., 2011; Dutilh et al., 2009; Liu & Watanabe, 2012; Ratcliff et al., 2006; Zhang & Rowe, 2014). Thus, de novo acquisition of linguistic and action knowledge made it easier to quickly and accurately arrive at a perceptual judgment.

In an extension of these studies, however, the increase in drift rate was substantially higher for knots that received both naming and tying training, compared to untrained knots and knots that received either type of training alone. A such, the ability to reach a decision quickly and correctly was made easier by a training regime that combined two types of training knowledge. We consider two ways to interpret the added benefit of multi-modal training. First, it is possible that the increase in drift-rate represents a dose-response effect, rather than being due to the unique combination of two types of training. That is, knots that received both training types received more training overall than knots that received only naming training or only tying training. Even so, it is still noteworthy that such a dose-response effect was specific to the drift-rate parameter and not evident in either the threshold or non-decision time parameter.

A second interpretation is that the unique combination of linguistic and action-based training may somehow enhance the quality and quantity of information accumulation during decision making. Such a qualitative interpretation would be consistent with prior studies that have reported multi-modal training protocols to lead to greater improvements in cognitive functions such as visuospatial working and episodic memory, executive functioning and the speed of information processing than single-function training protocols, as well as studies that report multi-model training protocols to engage a broad network of sensorimotor brain regions more than unimodal training protocols [@kirschAdditiveRoutesAction2015]. In the present study, we were unable to tease apart whether the results reflect a dose-response effect or instead reflect a qualitatively different impact of multi-modal training. We encourage future studies to systematically manipulate the combination of training types to determine whether increased exposure to training and/or different types of training influence the quality and rate at which evidence accumulates about a decision.

## Implications for understanding the effects of training and experience

The results of this study have a number of implications for our understanding of how training influences cognitive processes during a perceptual decision making. First, on a more general level, our key inferences about the mechanisms that underlie training would not be possible from a more conventional and separate analysis of accuracy and RT [@parker2023a]. The results of the present study, therefore, make it clear that the application of evidence accumulation modelling to behavioural data from a previously published training paradigm or a future training study can uncover new insights about the cognitive mechanisms responsible for learning and the acquisition of object knowledge.

Second, consistent with prior studies, our results revealed training effects to be multifaceted. That is, training effects were evident across a number of parameters of the LBA model, rather than a single parameter (Dutilh et al., 2011; Dutilh et al., 2009; Reinhartz et al., 2023). This suggests that improvements in task performance that are associated with training can be attributed to a number of underlying mechanisms. It may also be one reason for the wide variety of training-induced outcomes that are observed across different tasks and training protocols, as it is possible that different types and amounts of training can impact underlying cognitive processes in different ways. And this is one clear benefit to understanding cognitive processes that is provided by taking a more mathematical approach to theory building in psychology and cognitive neuroscience, as it forces a more explicit formulation of the relationship between parts of a system that are under investigation [@hintzman1991; @yarkoni2022].

Third, in an extension to previous studies, which typically administer one type of training (Dutilh et al., 2011; Dutilh et al., 2009; Reinhartz et al., 2023), we found no evidence to suggest that training effects differ by training type (linguistic: learning names vs. motor: learning to tie). This finding is noteworthy to consider in the context of the neuroimaging results of the original study, which found action-based training to be uniquely associated with activation in the anterior intraparietal sulcus, a brain region associated with object manipulation (Cross et al., 2012). On the face of it, therefore, these results suggest that are some unique training-specific contributions that shape cognitive and brain-based mechanisms, but our analytical approach was insensitive to such training-type differences. Taken together, these results highlight the value of using multi-method approaches to tackle research questions in cognitive neuroscience, as we are able to provide empirical support for domain-general as well as domain-specific effects of training.

## Limitations and constraints on generality

While we modelled behavioural data collected from one perceptual discrimination task completed on the final day of training, it is possible that there were session-by-session and trial-by-trial training effects that were not captured in the present study. In a recent application of evidence accumulation modelling to trial-by-trial data from a learning study, for example, the authors reported that training effects were best characterised as a continuous changing in drift rate, and a day-by-day variability in response caution (Cochrane et al., 2023). Future studies should, therefore, look to collect enough data per session to enable a computational modelling approach that can examine the time course of learning at both the trial and session level.

It is also important to acknowledge constraints on the generality of our findings [@simons2017]. While we interpret the results of our study as indicative of the mechanisms that underlie training effects broadly, we cannot rule out the possibility that these effects are specific to the type, amount and duration of training used in the original studies training paradigm. Future studies should look to systematically manipulate the type and amount of training participants receive, across a range of tasks in order to further understand the cognitive mechanisms that underlie different forms of training.

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::

### 2024-11-26 manuscript/manuscript.tex
initial commit

--- 2024-11-26 manuscript/manuscript.Rmd
@@
----
-title             : "Evidence accumulation modelling offers new insights into the cognitive mechanisms that underlie linguistic and action-based training"
-shorttitle        : "Decision models and experience-dependent plasticity"
-author: 
-  - name          : "Samantha Parker"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "School of Psychological Sciences, 16 University Avenue, Macquarie University, NSW 2109"
-    email         : "samantha.parker@students.mq.edu.au"
-    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
-      - "Conceptualization"
-      - "Data curation"
-      - "Formal analysis"
-      - "Writing - Original Draft Preparation"
-      - "Writing - Review & Editing"
-  - name          : "Emily S. Cross"
-    affiliation   : "2"
-    role:
-      - "Conceptualization"
-      - "Resources"
-      - "Writing - Review & Editing"
-  - name          : "Richard Ramsey"
-    affiliation   : "2"
-    role:
-      - "Conceptualization"
-      - "Visualisation"
-      - "Supervision"
-      - "Project Administration"
-      - "Validation"
-      - "Writing - Review & Editing"
-affiliation:
-  - id            : "1"
-    institution   : "Macquarie University"
-  - id            : "2"
-    institution   : "ETH Zürich"
-authornote: |
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+  man, donotrepeattitle,floatsintext]{apa6}
+\usepackage{amsmath,amssymb}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math} % this also loads fontspec
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+% Make \paragraph and \subparagraph free-standing
+\makeatletter
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}{
+    \@ifstar
+      \xxxParagraphStar
+      \xxxParagraphNoStar
+  }
+  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
+  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}{
+    \@ifstar
+      \xxxSubParagraphStar
+      \xxxSubParagraphNoStar
+  }
+  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
+  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+\makeatother
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
+  \fi
+  % set entry spacing
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\ifLuaTeX
+\usepackage[bidi=basic]{babel}
+\else
+\usepackage[bidi=default]{babel}
+\fi
+\babelprovide[main,import]{english}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
+% Manuscript styling
+\usepackage{upgreek}
+\captionsetup{font=singlespacing,justification=justified}
+
+% Table formatting
+\usepackage{longtable}
+\usepackage{lscape}
+% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
+\usepackage{multirow}		% Table styling
+\usepackage{tabularx}		% Control Column width
+\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
+\usepackage{threeparttablex}            % Lets threeparttable work with longtable
+
+% Create new environments so endfloat can handle them
+% \newenvironment{ltable}
+%   {\begin{landscape}\centering\begin{threeparttable}}
+%   {\end{threeparttable}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
+
+% Enables adjusting longtable caption width to table width
+% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
+\makeatletter
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+
+% \setlength{\parindent}{0.5in}
+% \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
+% See https://github.com/crsh/papaja/issues/292
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
+\makeatletter
+\usepackage{etoolbox}
+\patchcmd{\maketitle}
+  {\section{\normalfont\normalsize\abstractname}}
+  {\section*{\normalfont\normalsize\abstractname}}
+  {}{\typeout{Failed to patch abstract.}}
+\patchcmd{\maketitle}
+  {\section{\protect\normalfont{\@title}}}
+  {\section*{\protect\normalfont{\@title}}}
+  {}{\typeout{Failed to patch title.}}
+\makeatother
+
+\usepackage{xpatch}
+\makeatletter
+\xapptocmd\appendix
+  {\xapptocmd\section
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi: #1}}
+    {}{\InnerPatchFailed}%
+  }
+{}{\PatchFailed}
+\makeatother
+\keywords{evidence accumulation modelling, training, learning, action, naming, cognitive mechanisms, plasticity\newline\indent Word count: 6679}
+\usepackage{lineno}
+
+\linenumbers
+\usepackage{csquotes}
+\raggedbottom
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\usepackage{bookmark}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same}
+\hypersetup{
+  pdftitle={Evidence accumulation modelling offers new insights into the cognitive mechanisms that underlie linguistic and action-based training},
+  pdfauthor={Samantha Parker1, Emily S. Cross2, \& Richard Ramsey2},
+  pdflang={en-EN},
+  pdfkeywords={evidence accumulation modelling, training, learning, action, naming, cognitive mechanisms, plasticity},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+
+\title{Evidence accumulation modelling offers new insights into the cognitive mechanisms that underlie linguistic and action-based training}
+\author{Samantha Parker\textsuperscript{1}, Emily S. Cross\textsuperscript{2}, \& Richard Ramsey\textsuperscript{2}}
+\date{}
+
+\shorttitle{Decision models and experience-dependent plasticity}
+
+\authornote{
+
 Samantha Parker. School of Psychological Sciences, Macquarie University.
@@
 Neural Control of Movement Lab, Department of Health Sciences and Technology (D-HEST) and Social Brain Sciences Lab, Department of Humanities, Social and Political Sciences (D-GESS), ETH Zürich.
-  <!-- Enter author note here. -->
-abstract: |
+
+The authors made the following contributions.
+Samantha Parker: Conceptualization, Data curation, Formal analysis, Writing - Original Draft Preparation, Writing - Review \& Editing; Emily S.
+Cross: Conceptualization, Resources, Writing - Review \& Editing; Richard Ramsey: Conceptualization, Visualisation, Supervision, Project Administration, Validation, Writing - Review \& Editing.
+
+Correspondence concerning this article should be addressed to Samantha Parker, School of Psychological Sciences, 16 University Avenue, Macquarie University, NSW 2109.
+E-mail: \href{mailto:samantha.parker@students.mq.edu.au}{\nolinkurl{samantha.parker@students.mq.edu.au}}
+
+}
+
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Macquarie University\\\textsuperscript{2} ETH Zürich}
+
+\note{\clearpage}
+
+\abstract{%
 Evidence accumulation modelling has been shown to uncover new insights into the cognitive mechanisms that underlie decision making from behavioural data.
@@
 
-  *Public significance statement:* The results of this study show that multi-modal training, which spans linguistic and action-based content, increases the quality of information that is gained through perception to make a decision.
+\emph{Public significance statement:} The results of this study show that multi-modal training, which spans linguistic and action-based content, increases the quality of information that is gained through perception to make a decision.
 These results provide a novel computational account of performance benefits that are often observed from multi-modal training, which will aid theory development on learning and plasticity within cognitive science.
+}
 
-  <!-- https://tinyurl.com/ybremelq -->
-keywords          : "evidence accumulation modelling, training, learning, action, naming, cognitive mechanisms, plasticity"
-wordcount         : "6703"
-bibliography      : ["references.bib", "r-references.bib"]
-floatsintext      : yes
-linenumbers       : yes
-draft             : no
-mask              : no
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-classoption       : "man, donotrepeattitle"
-output            : papaja::apa6_pdf
-# output            : papaja::apa6_word
-note              : "\\clearpage" ## this moves the author note section to a second page
-editor_options: 
-  chunk_output_type: console
-header-includes:
-  - \raggedbottom
----
+\begin{document}
+\maketitle
 
-```{r, include=FALSE}
-## just include when de-bugging tinytex
-# options(tinytex.verbose = TRUE)
-```
-
-```{r setup, include = FALSE}
-pkg <- c("papaja", "citr", "tidyverse", "RColorBrewer", "patchwork")
-
-lapply(pkg, library, character.only = TRUE)
-
-r_refs(file = "r-references.bib")
-my_r_citation <- cite_r(file = "r-references.bib")
-```
-
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-```
-
-```{r plot-settings}
-## theme settings for ggplot
-theme_set(
-  theme_bw() +
-    theme(text = element_text(size = 18), 
-          title = element_text(size = 18),
-          legend.position = "bottom")
-)
-
-## Set the amount of dodge in figures
-pd <- position_dodge(0.7)
-pd2 <- position_dodge(1)
-```
-
-```{r global-chunk-settings}
-## set the figure options
-knitr::opts_chunk$set(fig.pos='H', out.extra = '', out.height = "67%",
-                      fig.align = "center") # initial version
-```
-
-# Introduction
+\section{Introduction}\label{introduction}
 
@@
 Typically, these models use accuracy and reaction times collected in speeded choice tasks to draw insights about the psychological mechanisms that underlie those decisions.
-The application of this modelling approach within the domain of cognitive psychology has led to a number of novel insights about the mechanisms that underlie processes such as lexical decision making [@wagenmakers2008], ageing [@ratcliff2001; @ratcliff2010] and perceptual discrimination [@ratcliff2008].
+The application of this modelling approach within the domain of cognitive psychology has led to a number of novel insights about the mechanisms that underlie processes such as lexical decision making (Wagenmakers, Ratcliff, Gomez, \& McKoon, 2008), ageing (Ratcliff, Thapar, \& McKoon, 2001, 2010) and perceptual discrimination (Ratcliff \& McKoon, 2008).
 Importantly, these insights are often not evident from more conventional analyses of accuracy and reaction time data.
-Given these characteristics, we applied an evidence accumulation model, the Linear Ballistic Accumulator (LBA; @brown2008), to behavioural data from a prior published study that used neuroimaging to examine the effects of different types of training on object knowledge and perception [@cross2012d].
-In contrast to the original study’s analysis, which analysed accuracy and reaction time separately, in this paper we apply an evidence accumulation model to uncover novel insights into the latent computational processes that underlie linguistic and action-based learning.
+Given these characteristics, we applied an evidence accumulation model, the Linear Ballistic Accumulator (LBA; Brown and Heathcote (2008)), to behavioural data from a prior published study that used neuroimaging to examine the effects of different types of training on object knowledge and perception (Cross et al., 2012).
+In contrast to the original study's analysis, which analysed accuracy and reaction time separately, in this paper we apply an evidence accumulation model to uncover novel insights into the latent computational processes that underlie linguistic and action-based learning.
 
-Whilst it is common for researchers to draw conclusions from a separate analysis of accuracy and reaction time, it is unclear how to combine these measures into a single measure by which to quantify task difficulty or subject ability [@wagenmakers2007].
-Consider, for example, a perceptual discrimination task that requires participants to indicate whether two images are of the same or different objects [@cross2012d; @weisberg2007].
+Whilst it is common for researchers to draw conclusions from a separate analysis of accuracy and reaction time, it is unclear how to combine these measures into a single measure by which to quantify task difficulty or subject ability (Wagenmakers, Van Der Maas, \& Grasman, 2007).
+Consider, for example, a perceptual discrimination task that requires participants to indicate whether two images are of the same or different objects (Cross et al., 2012; Weisberg, van Turennout, \& Martin, 2007).
 Objects could belong to two categories of training, one where the participants learn to name the object (name-based) and the other where the participant interacts physically with the object (action-based).
@@
 This is because without a principled way to combine accuracy and RT, these measures are incommensurable.
-While this example demonstrates the well-documented speed-accuracy trade-off, where less cautious responding is associated with faster, but more error prone responding, and more cautious responding is associated with slower but more accurate responses, this is just one of the many ways in which accuracy and reaction times can interact [@ratcliff1998].
+While this example demonstrates the well-documented speed-accuracy trade-off, where less cautious responding is associated with faster, but more error prone responding, and more cautious responding is associated with slower but more accurate responses, this is just one of the many ways in which accuracy and reaction times can interact (Ratcliff \& Rouder, 1998).
 
-Evidence accumulation models provide a principled way to combine accuracy and reaction time, enabling direct insight into the processes that underlie speeded decisions [@brown2008; @ratcliff2002].
+Evidence accumulation models provide a principled way to combine accuracy and reaction time, enabling direct insight into the processes that underlie speeded decisions (Brown \& Heathcote, 2008; Ratcliff, 2002).
 They do so by combining accuracy and the distribution of RT for correct and error responses in order to estimate parameters of a model that can separate the effects of response caution from difficulty.
-While there are many different varieties of evidence accumulation model, they all share a similar basic framework [@donkin2009].
+While there are many different varieties of evidence accumulation model, they all share a similar basic framework (Donkin, Averell, Brown, \& Heathcote, 2009).
 Namely, these models all assume that when making a decision, evidence is sampled from the environment and that information is used as evidence for one of the potential responses.
@@
 In this way, drift rate quantifies the deterministic component of the accumulation process.
-Drift rate, therefore, measures both the quantity and the quality of information in the system and can provide a direct measure of task difficult or subject ability [@lewandowsky2018].
+Drift rate, therefore, measures both the quantity and the quality of information in the system and can provide a direct measure of task difficult or subject ability (Lewandowsky \& Oberauer, 2018).
 
-Assessing how parameters vary as a function of experimental conditions has the potential to reveal more about the mechanisms that underlie the decision-making process than is apparent from an analysis of accuracy and RT alone [@dutilh2019; @donkin2009; @evans2019; @evans2020].
+Assessing how parameters vary as a function of experimental conditions has the potential to reveal more about the mechanisms that underlie the decision-making process than is apparent from an analysis of accuracy and RT alone (Donkin et al., 2009; Dutilh et al., 2019; Evans, 2019; Evans \& Wagenmakers, 2020).
 Perhaps one of the most persuasive examples of this approach comes from the ageing literature.
-One typical finding within the ageing research is that response times increase with increasing age, a finding that led to the conclusion that there is a cognitive decline associated with ageing [@salthouse1996].
-Application of an evidence accumulation model to data from such tasks, however, reveals that rather than older adults performing more poorly on speeded response time tasks than younger adults, differences in responses are actually due to differences in response caution [@ratcliff2004].
+One typical finding within the ageing research is that response times increase with increasing age, a finding that led to the conclusion that there is a cognitive decline associated with ageing (Salthouse, 1996).
+Application of an evidence accumulation model to data from such tasks, however, reveals that rather than older adults performing more poorly on speeded response time tasks than younger adults, differences in responses are actually due to differences in response caution (Ratcliff, Thapar, Gomez, \& McKoon, 2004).
 That is, older adults are more cautious responders than younger adults, requiring a higher level of evidence to trigger a response.
 Importantly, this inference was not available from a traditional analysis of accuracy and RT.
-This is just one example in which evidence accumulation modelling has allowed researchers to draw inferences that were unavailable in a traditional analysis of behavioural data [@white2022].
+This is just one example in which evidence accumulation modelling has allowed researchers to draw inferences that were unavailable in a traditional analysis of behavioural data (White \& Kitchen, 2022).
 Evidence accumulation modelling thus provides us with an opportunity to interrogate behavioural data to uncover novel insights into the latent variables that underlie decision making in a way that a traditional analysis cannot.
@@
 In the present paper, we use the evidence accumulation approach to shed new light on the mechanisms that underlie two kinds of learning based on different types of training experience.
-Specifically, we apply the Linear Ballistic Accumulator (LBA) (Brown & Heathcote, 2008) to behavioural data from an existing multi-session training dataset that taught participants how to tie and name novel knots (Cross et al., 2012).
+Specifically, we apply the Linear Ballistic Accumulator (LBA) (Brown \& Heathcote, 2008) to behavioural data from an existing multi-session training dataset that taught participants how to tie and name novel knots (Cross et al., 2012).
 In making use of existing data not only do we provide novel insights into the mechanisms that underlie different types of training, but we also demonstrate how computational modelling can lead to conclusions that are not readily apparent from a traditional analysis of accuracy and RT alone.
 
-In the domain of training, the most typical behavioural finding is that with increased repetition of a task response times decrease and accuracy increases [@simons2016; @vonbastian2022].
+In the domain of training, the most typical behavioural finding is that with increased repetition of a task response times decrease and accuracy increases (Simons et al., 2016; von Bastian et al., 2022).
 While this finding is most commonly interpreted as evidence of improved task performance, it provides few insights about the latent processes that underlie training-related changes.
-Evidence accumulation modelling of training effects, on the other hand, has shown that task repetition can influence the rate at which information accumulates, the amount of evidence needed to trigger a response and non-decision time [@dutilh2009; @dutilh2011; @reinhartz2023].
-Studies that have used these computational modelling techniques to investigate how task repetition improves response times report an increase in the rate of information accumulation associated with repeated performance of the same speeded task [@dutilh2009; @dutilh2011; @liu2012; @ratcliff2006; @zhang2014].
+Evidence accumulation modelling of training effects, on the other hand, has shown that task repetition can influence the rate at which information accumulates, the amount of evidence needed to trigger a response and non-decision time (Dutilh, Krypotos, \& Wagenmakers, 2011; Dutilh, Vandekerckhove, Tuerlinckx, \& Wagenmakers, 2009; Reinhartz, Strobach, Jacobsen, \& von Bastian, 2023).
+Studies that have used these computational modelling techniques to investigate how task repetition improves response times report an increase in the rate of information accumulation associated with repeated performance of the same speeded task (Dutilh et al., 2011; Dutilh et al., 2009; Liu \& Watanabe, 2012; Ratcliff, Thapar, \& McKoon, 2006; Zhang \& Rowe, 2014).
 
-These studies have also found that while the rate of information accumulation increases during practice, these effects are also associated with decreased boundary separation (Dutilh et al., 2011; Dutilh et al., 2009; Liu & Watanabe, 2012; Zhang & Rowe, 2014).
+These studies have also found that while the rate of information accumulation increases during practice, these effects are also associated with decreased boundary separation (Dutilh et al., 2011; Dutilh et al., 2009; Liu \& Watanabe, 2012; Zhang \& Rowe, 2014).
 That is, with increased repetition of a task, participants require less evidence to trigger a decision.
 This finding has led some authors to suggest that training effects may elicit a shift in response caution, leading people to prioritise speed over accuracy.
-The influence of training on non-decision time has less consistently been reported in the literature, with some studies suggesting that training decreases non-decision timing (Dutilh et al., 2011; Dutilh et al., 2009) and other studies reporting no influence on this parameter [@strobach2013].
+The influence of training on non-decision time has less consistently been reported in the literature, with some studies suggesting that training decreases non-decision timing (Dutilh et al., 2011; Dutilh et al., 2009) and other studies reporting no influence on this parameter (Strobach, Liepelt, Pashler, Frensch, \& Schubert, 2013).
 Dutilh and colleagues (2011; 2009), for example, found that improved performance on a repeated lexical decision task was associated with faster drift rates, lower response caution and a decrease in non-decision time.
@@
 
-These conclusions, however, have been drawn from a limited number of perceptual discrimination tasks, with the vast majority of studies using either random dot motion [@cochrane2023] or lexical discrimination tasks (Dutilh et al., 2011).
+These conclusions, however, have been drawn from a limited number of perceptual discrimination tasks, with the vast majority of studies using either random dot motion (Cochrane, Sims, Bejjanki, Green, \& Bavelier, 2023) or lexical discrimination tasks (Dutilh et al., 2011).
 Similarly, these studies typically investigate training related changes that are induced by task repetition (Dutilh et al., 2011; Dutilh et al., 2009).
@@
 The aim of the present study was to investigate to what extent parameters in the LBA model vary by each type of training.
-Given previous studies have suggested that increased drift rate, decreased response caution and decreased non-decision time (Dutilh et al., 2011; Dutilh et al., 2009; Zhang & Rowe, 2014) are all associated with training-related changes, we hypothesised that improvements in perceptual discrimination due to training would be associated with (1) an increase in drift rate; (2) a decrease in response caution; (3) a decrease in non-decision time or (4) some combination of these factors.
-Furthermore, it was also possible that the extent to which these parameters varied by training type (naming, tying, naming & tying, untrained) may differ, although we had no specific predictions about the direction of this hypothesis.
+Given previous studies have suggested that increased drift rate, decreased response caution and decreased non-decision time (Dutilh et al., 2011; Dutilh et al., 2009; Zhang \& Rowe, 2014) are all associated with training-related changes, we hypothesised that improvements in perceptual discrimination due to training would be associated with (1) an increase in drift rate; (2) a decrease in response caution; (3) a decrease in non-decision time or (4) some combination of these factors.
+Furthermore, it was also possible that the extent to which these parameters varied by training type (naming, tying, naming \& tying, untrained) may differ, although we had no specific predictions about the direction of this hypothesis.
 
-# Methods
+\section{Methods}\label{methods}
 
-## Transparency and Openness Statement
+\subsection{Transparency and Openness Statement}\label{transparency-and-openness-statement}
 
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [@simmons2012].
-In addition, the hypotheses and planned analysis for this paper were preregistered in advance (see our pre-registration here: [https://aspredicted.org/6ztj-45s5.pdf](https://aspredicted.org/6ztj-45s5.pdf)).
+We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study (Simmons, Nelson, \& Simonsohn, 2012).
+In addition, the hypotheses and planned analysis for this paper were preregistered in advance (see our pre-registration here: \url{https://aspredicted.org/6ztj-45s5.pdf}).
 We deviated from our pre-registration in one way.
@@
 
-Importantly, given that we were interested in the mechanisms that underlie training vs.
-no-training, as well as comparisons between different types of training (linguistic vs.
-action vs.
-both), only the post-training session was necessary to capture and quantify these effects.
-Indeed, Cross and colleagues (2012), in their original study, included only results from the post-training session in their final analysis, as this session is thought to be more consistent and reflect the participants' learned state [@weisberg2007].
+Importantly, given that we were interested in the mechanisms that underlie training vs.~no-training, as well as comparisons between different types of training (linguistic vs.~action vs.~both), only the post-training session was necessary to capture and quantify these effects.
+Indeed, Cross and colleagues (2012), in their original study, included only results from the post-training session in their final analysis, as this session is thought to be more consistent and reflect the participants' learned state (Weisberg et al., 2007).
 All other aspects of the pre-registration were unchanged.
-In addition, all of the analysis code used in this paper have been made available on the open science framework ([https://osf.io/ea6gk/](https://osf.io/ea6gk/).
+In addition, all of the analysis code used in this paper have been made available on the open science framework (\url{https://osf.io/ea6gk/}.
 Given that the data were collected several years before 2012, it was not yet routine to request explicit consent to share data publicly.
 Therefore, the raw data are only available from the authors upon request.
-Since the current manuscript was written in R using the papaja() package [@R-papaja], it is also computationally reproducible and available via GitHub ([https://github.com/rich-ramsey/knot_dmc](https://github.com/rich-ramsey/knot_dmc)).
+Since the current manuscript was written in R using the papaja() package (Aust \& Barth, 2023), it is also computationally reproducible and available via GitHub (\url{https://github.com/rich-ramsey/knot_dmc}).
 
-## Dataset
+\subsection{Dataset}\label{dataset}
 
@@
 When photographs were of the same knot, the viewing angle of the two photographs differed, so the stimuli presented were never identical.
-Of the 80 trials, 50% of the knots were the same and 50% of the knots were different.
+Of the 80 trials, 50\% of the knots were the same and 50\% of the knots were different.
 Both accuracy and response times (ms) of the perceptual discrimination task were recorded.
@@
 The decision to include only the final training session in the LBA model meant that a further two participants were excluded from modelling as they did not complete the final session of the perceptual discrimination task.
-Therefore, 18 participants were included in the present study (M = 19.4 years, age ranged from 17 – 27 years).
+Therefore, 18 participants were included in the present study (M = 19.4 years, age ranged from 17 -- 27 years).
 Second, unlike Cross and colleagues who included the post-training session across all five days in their analysis of accuracy and RT, we included only the post-training session on the final day of training (Day 5 post-training).
 Given the aim of our study was to use evidence accumulation modelling to examine the cognitive mechanisms underlying linguistic and action-based training, it was sufficient to use the training effects evident on the last day of training for our analysis.
-That is, general training effects could be compared via a comparison between the untrained and trained conditions, and between each type of training category (e.g.
-linguistic vs.
-action vs.
-both).
+That is, general training effects could be compared via a comparison between the untrained and trained conditions, and between each type of training category (e.g.~linguistic vs.~action vs.~both).
 The benefit of including only the final post-training sessions was a computationally simpler model.
@@
 
-## LBA data analysis
+\subsection{LBA data analysis}\label{lba-data-analysis}
 
-### Model Specification
+\subsubsection{Model Specification}\label{model-specification}
 
-We fit the LBA model to each participants’ data for the final post-training session.
+We fit the LBA model to each participants' data for the final post-training session.
 The LBA model has one accumulator for each response, each with potentially different parameter values.
 In this design, that meant that there was one accumulator for pairs of knots that were the same and another accumulator for pairs of knots that were different.
-Each accumulator possessed the following parameters; start point noise (A), representing the amount of information in each accumulator at the beginning of a decision; threshold (b) which represents the amount of evidence necessary in order to trigger a decision (in the present study this was represented in terms of the difference between the top of the start point distribution and the response threshold ($B = b - A \ge 0$); drift rate (v) the rate at which evidence accumulates for each response; and non-decision time ($Ter \ge 0$) the amount of time it takes to complete all other processes that fall outside the decision making process, including stimulus encoding and motor responding.
-We allowed the threshold parameter to vary by Training Type (name, tie, both, untrained) and Response (participant’s response as to whether the two knots match vs.
-no-match).
+Each accumulator possessed the following parameters; start point noise (A), representing the amount of information in each accumulator at the beginning of a decision; threshold (b) which represents the amount of evidence necessary in order to trigger a decision (in the present study this was represented in terms of the difference between the top of the start point distribution and the response threshold (\(B = b - A \ge 0\)); drift rate (v) the rate at which evidence accumulates for each response; and non-decision time (\(Ter \ge 0\)) the amount of time it takes to complete all other processes that fall outside the decision making process, including stimulus encoding and motor responding.
+We allowed the threshold parameter to vary by Training Type (name, tie, both, untrained) and Response (participant's response as to whether the two knots match vs.~no-match).
 The drift rate parameter was allowed to vary by Training Type and an accumulator match factor, which denotes the match between the accumulator and the stimulus.
-Specifically, if the stimulus displayed two of the same knots, then the accumulator for the “match” response was the TRUE or matching accumulator, whereas the accumulator for the “no match” response would be the FALSE or mismatching accumulator.
+Specifically, if the stimulus displayed two of the same knots, then the accumulator for the ``match'' response was the TRUE or matching accumulator, whereas the accumulator for the ``no match'' response would be the FALSE or mismatching accumulator.
 In this way the difference between the TRUE and FALSE accumulator captures both the quantity and quality of information accumulating about the stimulus.
-The larger the difference between the TRUE and FALSE accumulators, the higher the quality of information accumulating in favour of that response (Lewandowsky & Oberauer, 2018).
+The larger the difference between the TRUE and FALSE accumulators, the higher the quality of information accumulating in favour of that response (Lewandowsky \& Oberauer, 2018).
 Given this, we operationalised drift rate as the difference between the TRUE and FALSE accumulator.
@@
 
-### Model estimation
+\subsubsection{Model estimation}\label{model-estimation}
 
-Model estimation was carried out in a Bayesian statistical framework using the Dynamic Models of Choice software that is written in the R programming language [@heathcote2019].
+Model estimation was carried out in a Bayesian statistical framework using the Dynamic Models of Choice software that is written in the R programming language (Heathcote et al., 2019).
 Full details of priors and sampling methods are provided in supplementary materials.
-Following prior work [@castro2019], priors were selected using a weakly informative approach.
+Following prior work (Castro, Strayer, Matzke, \& Heathcote, 2019), priors were selected using a weakly informative approach.
 That is, priors were chosen to have little influence on estimation (graphical summaries of how posteriors were updated relative to priors are provided in supplementary materials).
@@
 
-### Parameter Estimates
+\subsubsection{Parameter Estimates}\label{parameter-estimates}
 
@@
 Pairwise comparisons on these posterior distributions were then computed between each training type and the untrained condition, as well as between each training type.
-To summarise the distribution of parameters of interest we report the median of the posterior distribution together with 95% quantile intervals of the distribution in square brackets.
+To summarise the distribution of parameters of interest we report the median of the posterior distribution together with 95\% quantile intervals of the distribution in square brackets.
 
-# Results
+\section{Results}\label{results}
 
-## Analysis of Observed Variables
+\subsection{Analysis of Observed Variables}\label{analysis-of-observed-variables}
 
@@
 
-(ref:accuracy-rt-caption) Accuracy and Reaction Time by Training Type and Session.
+\begin{figure}[H]
+
+{\centering \includegraphics[height=0.67\textheight,]{../figures/from_file/acc_rt}
+
+}
+
+\caption{Accuracy and Reaction Time by Training Type and Session.
 (A) Percent correct on the perceptual discrimination task by training type.
 (B) Mean reaction time (ms) on the perceptual discrimination task by training type.
-Black points denote group means, while error bars represent within subjects’ standard errors of the mean.
-Grey points denote individual subject means.
+Black points denote group means, while error bars represent within subjects' standard errors of the mean.
+Grey points denote individual subject means.}\label{fig:accuracy-rt-plot}
+\end{figure}
 
-```{r accuracy-rt-plot, fig.cap = "(ref:accuracy-rt-caption)"}
-knitr::include_graphics("../figures/from_file/acc_rt.png")
-```
+\subsection{Evidence Accumulation Modelling}\label{evidence-accumulation-modelling}
 
-## Evidence Accumulation Modelling
-
-### Thresholds
+\subsubsection{Thresholds}\label{thresholds}
 
 Inspection of the posterior distributions for the threshold parameter of the LBA model revealed evidence to suggest that thresholds significantly differed by Training Type.
-Specifically, thresholds were lower in all three training conditions, naming (0.76 [0.64, 0.88]), tying, (0.68 [0.57, 0.79]) and both naming and tying training (1.01 [0.84, 1.19]) relative to the untrained condition (2.80 [2.60, 3.03]) (see Figure 2A).
+Specifically, thresholds were lower in all three training conditions, naming (0.76 {[}0.64, 0.88{]}), tying, (0.68 {[}0.57, 0.79{]}) and both naming and tying training (1.01 {[}0.84, 1.19{]}) relative to the untrained condition (2.80 {[}2.60, 3.03{]}) (see Figure 2A).
 
@@
 
-(ref:threshold-caption) Posterior Distributions for the Threshold Parameter by Training Condition and Pairwise Differences between Training Conditions.
+\begin{figure}[H]
+
+{\centering \includegraphics[height=0.67\textheight,]{../figures/from_file/thresholds}
+
+}
+
+\caption{Posterior Distributions for the Threshold Parameter by Training Condition and Pairwise Differences between Training Conditions.
 (A) This panel demonstrates the posterior distributions for the threshold parameter of the LBA model by training condition.
 (B) This panels shows the difference in the posterior distribution for the threshold parameter between each training condition relative to the untrained condition (top row) and between each training condition (bottom row).
-In all graphs, black points represent the median value of the posterior distribution, while thick black lines represent the 95% quantile interval of the distribution.
-In difference graphs, the red line represents the zero point of the distribution.
+In all graphs, black points represent the median value of the posterior distribution, while thick black lines represent the 95\% quantile interval of the distribution.
+In difference graphs, the red line represents the zero point of the distribution.}\label{fig:threshold-plot}
+\end{figure}
 
-```{r threshold-plot, fig.cap = "(ref:threshold-caption)"}
-knitr::include_graphics("../figures/from_file/thresholds.png")
-```
-
-### Drift rate
+\subsubsection{Drift rate}\label{drift-rate}
 
 In order to quantify the influence of training type on the quality and quantity of information accumulating from the stimulus, we computed the difference between the TRUE and FALSE drift rate (drift rate difference).
-As can be seen in Figure 3A drift rate difference appeared substantially higher for knots that received both tying and naming training (3.12 [2.74, 3.53]), relative to naming (2.30 [2.01, 2.60]), tying (2.39 [2.13, 2.67]) and untrained conditions (2.08 [1.85, 2.31]).
+As can be seen in Figure 3A drift rate difference appeared substantially higher for knots that received both tying and naming training (3.12 {[}2.74, 3.53{]}), relative to naming (2.30 {[}2.01, 2.60{]}), tying (2.39 {[}2.13, 2.67{]}) and untrained conditions (2.08 {[}1.85, 2.31{]}).
 Pairwise comparisons between training conditions confirmed that there was evidence to suggest that the quality of evidence accruing was higher for knots that received both naming and tying training relative to knots that received naming, tying and no training (See Figure 3B).
@@
 
-(ref:drift-rate-caption) Posterior Distributions for the Drift Rate Difference Parameter by Training Condition and Pairwise Differences between Training Conditions.
+\begin{figure}[H]
+
+{\centering \includegraphics[height=0.67\textheight,]{../figures/from_file/drift_rate}
+
+}
+
+\caption{Posterior Distributions for the Drift Rate Difference Parameter by Training Condition and Pairwise Differences between Training Conditions.
 (A) This panel demonstrates the posterior distributions for the drift-rate parameter of the LBA model by training condition.
 (B) This panels shows the difference in the posterior distribution for the drift-rate parameter between each training condition relative to the untrained condition (top row) and between each training condition (bottom row).
-In all graphs, black points represent the median value of the posterior distribution, while thick black lines represent the 95% quantile interval of the distribution.
-In difference graphs, the red line represents the zero point of the distribution.
-
-```{r drift-rate-plot, fig.cap = "(ref:drift-rate-caption)"}
-knitr::include_graphics("../figures/from_file/drift_rate.png")
-```
+In all graphs, black points represent the median value of the posterior distribution, while thick black lines represent the 95\% quantile interval of the distribution.
+In difference graphs, the red line represents the zero point of the distribution.}\label{fig:drift-rate-plot}
+\end{figure}
 
@@
 
-### Non-decision time
+\subsubsection{Non-decision time}\label{non-decision-time}
 
-As Figure 4 demonstrates, relative to the untrained condition (0.26 [0.22, 0.29]) non-decision time was significantly higher for knots that received naming (0.50 [0.47, 0.53]), tying (0.51 [0.48, 0.54]) and both naming and tying training (0.52 [0.50, 0.55]).
+As Figure 4 demonstrates, relative to the untrained condition (0.26 {[}0.22, 0.29{]}) non-decision time was significantly higher for knots that received naming (0.50 {[}0.47, 0.53{]}), tying (0.51 {[}0.48, 0.54{]}) and both naming and tying training (0.52 {[}0.50, 0.55{]}).
 
@@
 
-(ref:ndt-caption) Posterior Distributions for the Non-decision Time (ndt) Parameter by Training Condition and Pairwise Differences between Training Conditions.
+\begin{figure}[H]
+
+{\centering \includegraphics[height=0.67\textheight,]{../figures/from_file/ndt}
+
+}
+
+\caption{Posterior Distributions for the Non-decision Time (ndt) Parameter by Training Condition and Pairwise Differences between Training Conditions.
 (A) This panel demonstrates the posterior distributions for the ndt parameter of the LBA model by training condition.
 (B) This panels shows the difference in the posterior distribution for the ndt parameter between each training condition relative to the untrained condition (top row) and between each training condition (bottom row).
-In all graphs, black points represent the median value of the posterior distribution, while thick black lines represent the 95% quantile interval of the distribution.
-In difference graphs, the red line represents the zero point of the distribution.
+In all graphs, black points represent the median value of the posterior distribution, while thick black lines represent the 95\% quantile interval of the distribution.
+In difference graphs, the red line represents the zero point of the distribution.}\label{fig:ndt-plot}
+\end{figure}
 
-```{r ndt-plot, fig.cap = "(ref:ndt-caption)"}
-knitr::include_graphics("../figures/from_file/ndt.png")
-```
-
-### Summary
+\subsubsection{Summary}\label{summary}
 
@@
 
-(ref:lba-summary-caption) A summary of the key findings visualised using the structure of a decision model plot.
+\begin{figure}[H]
+
+{\centering \includegraphics[height=0.67\textheight,]{../figures/lba_summary}
+
+}
+
+\caption{A summary of the key findings visualised using the structure of a decision model plot.
 Each panel represents an experimental condtion and displays the same information.
@@
 The lower threshold represents a mismatch between the displayed knots and the higher threshold represents a match between the displayed knots on a given trial.
-The mean drift rate (v) for true (solid green) and false (dashed orange) responses are also displayed.
+The mean drift rate (v) for true (solid green) and false (dashed orange) responses are also displayed.}\label{fig:lba-summary-plot}
+\end{figure}
 
-```{r lba-summary-plot, fig.cap = "(ref:lba-summary-caption)"}
-knitr::include_graphics("../figures/lba_summary.jpeg")
-```
-
-# Discussion
+\section{Discussion}\label{discussion}
 
@@
 
-## Training leads to general decreases in response caution and general increases in non-decision time
+\subsection{Training leads to general decreases in response caution and general increases in non-decision time}\label{training-leads-to-general-decreases-in-response-caution-and-general-increases-in-non-decision-time}
 
@@
 That is, participants required less evidence to trigger a decision in the perceptual discrimination task when presented with any of the trained knots compared to untrained knots.
-This finding is in consistent with other studies that have found task repetition to be associated with decreased response caution (Dutilh et al., 2011; Dutilh et al., 2009; Liu & Watanabe, 2012; Zhang & Rowe, 2014).
+This finding is in consistent with other studies that have found task repetition to be associated with decreased response caution (Dutilh et al., 2011; Dutilh et al., 2009; Liu \& Watanabe, 2012; Zhang \& Rowe, 2014).
 Extending these previous studies, our results also suggest that this decrease in response caution is a general effect and does not differ by type of training.
@@
 
-## The combination of linguistic and action-based training increases the quality of information accumulation
+\subsection{The combination of linguistic and action-based training increases the quality of information accumulation}\label{the-combination-of-linguistic-and-action-based-training-increases-the-quality-of-information-accumulation}
 
@@
 Relative to knots that were untrained, there was an increase in the rate at which evidence accumulated following all training conditions (naming, tying and both).
-The finding that training generally increases the rate at which evidence accumulates is consistent with previous studies that have found repeatedly completing speeded tasks to be associated with an increase in the rate at which information accumulates (Dutilh et al., 2011; Dutilh et al., 2009; Liu & Watanabe, 2012; Ratcliff et al., 2006; Zhang & Rowe, 2014).
+The finding that training generally increases the rate at which evidence accumulates is consistent with previous studies that have found repeatedly completing speeded tasks to be associated with an increase in the rate at which information accumulates (Dutilh et al., 2011; Dutilh et al., 2009; Liu \& Watanabe, 2012; Ratcliff et al., 2006; Zhang \& Rowe, 2014).
 Thus, de novo acquisition of linguistic and action knowledge made it easier to quickly and accurately arrive at a perceptual judgment.
@@
 A second interpretation is that the unique combination of linguistic and action-based training may somehow enhance the quality and quantity of information accumulation during decision making.
-Such a qualitative interpretation would be consistent with prior studies that have reported multi-modal training protocols to lead to greater improvements in cognitive functions such as visuospatial working and episodic memory, executive functioning and the speed of information processing than single-function training protocols, as well as studies that report multi-model training protocols to engage a broad network of sensorimotor brain regions more than unimodal training protocols [@kirschAdditiveRoutesAction2015].
+Such a qualitative interpretation would be consistent with prior studies that have reported multi-modal training protocols to lead to greater improvements in cognitive functions such as visuospatial working and episodic memory, executive functioning and the speed of information processing than single-function training protocols, as well as studies that report multi-model training protocols to engage a broad network of sensorimotor brain regions more than unimodal training protocols (Kirsch \& Cross, 2015).
 In the present study, we were unable to tease apart whether the results reflect a dose-response effect or instead reflect a qualitatively different impact of multi-modal training.
@@
 
-## Implications for understanding the effects of training and experience
+\subsection{Implications for understanding the effects of training and experience}\label{implications-for-understanding-the-effects-of-training-and-experience}
 
 The results of this study have a number of implications for our understanding of how training influences cognitive processes during a perceptual decision making.
-First, on a more general level, our key inferences about the mechanisms that underlie training would not be possible from a more conventional and separate analysis of accuracy and RT [@parker2023a].
+First, on a more general level, our key inferences about the mechanisms that underlie training would not be possible from a more conventional and separate analysis of accuracy and RT (Parker \& Ramsey, 2023).
 The results of the present study, therefore, make it clear that the application of evidence accumulation modelling to behavioural data from a previously published training paradigm or a future training study can uncover new insights about the cognitive mechanisms responsible for learning and the acquisition of object knowledge.
@@
 It may also be one reason for the wide variety of training-induced outcomes that are observed across different tasks and training protocols, as it is possible that different types and amounts of training can impact underlying cognitive processes in different ways.
-And this is one clear benefit to understanding cognitive processes that is provided by taking a more mathematical approach to theory building in psychology and cognitive neuroscience, as it forces a more explicit formulation of the relationship between parts of a system that are under investigation [@hintzman1991; @yarkoni2022].
+And this is one clear benefit to understanding cognitive processes that is provided by taking a more mathematical approach to theory building in psychology and cognitive neuroscience, as it forces a more explicit formulation of the relationship between parts of a system that are under investigation (Hintzman, 1991; Yarkoni, 2022/ed).
 
-Third, in an extension to previous studies, which typically administer one type of training (Dutilh et al., 2011; Dutilh et al., 2009; Reinhartz et al., 2023), we found no evidence to suggest that training effects differ by training type (linguistic: learning names vs.
-motor: learning to tie).
+Third, in an extension to previous studies, which typically administer one type of training (Dutilh et al., 2011; Dutilh et al., 2009; Reinhartz et al., 2023), we found no evidence to suggest that training effects differ by training type (linguistic: learning names vs.~motor: learning to tie).
 This finding is noteworthy to consider in the context of the neuroimaging results of the original study, which found action-based training to be uniquely associated with activation in the anterior intraparietal sulcus, a brain region associated with object manipulation (Cross et al., 2012).
@@
 
-## Limitations and constraints on generality
+\subsection{Limitations and constraints on generality}\label{limitations-and-constraints-on-generality}
 
@@
 
-It is also important to acknowledge constraints on the generality of our findings [@simons2017].
+It is also important to acknowledge constraints on the generality of our findings (Simons, Shoda, \& Lindsay, 2017).
 While we interpret the results of our study as indicative of the mechanisms that underlie training effects broadly, we cannot rule out the possibility that these effects are specific to the type, amount and duration of training used in the original studies training paradigm.
@@
 
-# References
+\section{References}\label{references}
 
-::: {#refs custom-style="Bibliography"}
-:::
+\phantomsection\label{refs}
+\begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-R-papaja}
+Aust, F., \& Barth, M. (2023). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
+
+\bibitem[\citeproctext]{ref-brown2008}
+Brown, S.
+D., \& Heathcote, A.
+(2008).
+The simplest complete model of choice response time: {Linear} ballistic accumulation.
+\emph{Cognitive Psychology}, \emph{57}(3), 153--178.
+\url{https://doi.org/10.1016/j.cogpsych.2007.12.002}
+
+\bibitem[\citeproctext]{ref-castro2019}
+Castro, S.
+C., Strayer, D.
+L., Matzke, D., \& Heathcote, A.
+(2019).
+Cognitive workload measurement and modeling under divided attention.
+\emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{45}(6), 826--839.
+\url{https://doi.org/10.1037/xhp0000638}
+
+\bibitem[\citeproctext]{ref-cochrane2023}
+Cochrane, A., Sims, C.
+R., Bejjanki, V.
+R., Green, C.
+S., \& Bavelier, D.
+(2023).
+Multiple timescales of learning indicated by changes in evidence-accumulation processes during perceptual decision-making.
+\emph{Npj Science of Learning}, \emph{8}(1), 1--10.
+\url{https://doi.org/10.1038/s41539-023-00168-9}
+
+\bibitem[\citeproctext]{ref-cross2012d}
+Cross, E.
+S., Cohen, N.
+R., C.
+Hamilton, A.
+F.
+de, Ramsey, R., Wolford, G., \& Grafton, S.
+T.
+(2012).
+Physical experience leads to enhanced object perception in parietal cortex: {Insights} from knot tying.
+\emph{Neuropsychologia}, \emph{50}(14), 3207--3217.
+\url{https://doi.org/10.1016/j.neuropsychologia.2012.09.028}
+
+\bibitem[\citeproctext]{ref-donkin2009}
+Donkin, C., Averell, L., Brown, S., \& Heathcote, A.
+(2009).
+Getting more from accuracy and response time data: {Methods} for fitting the linear ballistic accumulator.
+\emph{Behavior Research Methods}, \emph{41}(4), 1095--1110.
+\url{https://doi.org/10.3758/BRM.41.4.1095}
+
+\bibitem[\citeproctext]{ref-dutilh2019}
+Dutilh, G., Annis, J., Brown, S.
+D., Cassey, P., Evans, N.
+J., Grasman, R.
+P.
+P.
+P., \ldots{} Donkin, C.
+(2019).
+The quality of response time data inference: A blinded, collaborative assessment of the validity of cognitive models.
+\emph{Psychonomic Bulletin \& Review}, \emph{26}(4), 1051--1069.
+\url{https://doi.org/10.3758/s13423-017-1417-2}
+
+\bibitem[\citeproctext]{ref-dutilh2011}
+Dutilh, G., Krypotos, A.-M., \& Wagenmakers, E.-J.
+(2011).
+Task-{Related Versus Stimulus-Specific Practice}.
+\emph{Experimental Psychology}, \emph{58}(6), 434--442.
+\url{https://doi.org/10.1027/1618-3169/a000111}
+
+\bibitem[\citeproctext]{ref-dutilh2009}
+Dutilh, G., Vandekerckhove, J., Tuerlinckx, F., \& Wagenmakers, E.-J.
+(2009).
+A diffusion model decomposition of the practice effect.
+\emph{Psychonomic Bulletin \& Review}, \emph{16}(6), 1026--1036.
+\url{https://doi.org/10.3758/16.6.1026}
+
+\bibitem[\citeproctext]{ref-evans2019}
+Evans, N.
+J.
+(2019).
+A method, framework, and tutorial for efficiently simulating models of decision-making.
+\emph{Behavior Research Methods}, \emph{51}(5), 2390--2404.
+\url{https://doi.org/10.3758/s13428-019-01219-z}
+
+\bibitem[\citeproctext]{ref-evans2020}
+Evans, N.
+J., \& Wagenmakers, E.-J.
+(2020).
+Evidence {Accumulation Models}: {Current Limitations} and {Future Directions}.
+\emph{The Quantitative Methods for Psychology}, \emph{16}(2), 73--90.
+\url{https://doi.org/10.20982/tqmp.16.2.p073}
+
+\bibitem[\citeproctext]{ref-heathcote2019}
+Heathcote, A., Lin, Y.-S., Reynolds, A., Strickland, L., Gretton, M., \& Matzke, D.
+(2019).
+Dynamic models of choice.
+\emph{Behavior Research Methods}, \emph{51}(2), 961--985.
+\url{https://doi.org/10.3758/s13428-018-1067-y}
+
+\bibitem[\citeproctext]{ref-hintzman1991}
+Hintzman, D.
+L.
+(1991).
+Why are formal models useful in psychology?
+In \emph{Relating theory and data: {Essays} on human memory in honor of {Bennet B}.
+{Murdock}.} (pp.
+39--56).
+Hillsdale, NJ, US: Lawrence Erlbaum Associates, Inc.
+
+\bibitem[\citeproctext]{ref-kirschAdditiveRoutesAction2015}
+Kirsch, L. P., \& Cross, E. S. (2015). Additive routes to action learning: Layering experience shapes engagement of the action observation network. \emph{Cerebral Cortex}, \emph{25}(12), 4799--4811.
+
+\bibitem[\citeproctext]{ref-lewandowsky2018}
+Lewandowsky, S., \& Oberauer, K.
+(2018).
+Computational {Modeling} in {Cognition} and {Cognitive Neuroscience}.
+In \emph{Stevens' {Handbook} of {Experimental Psychology} and {Cognitive Neuroscience}} (pp.
+1--35).
+John Wiley \& Sons, Ltd.
+\url{https://doi.org/10.1002/9781119170174.epcn501}
+
+\bibitem[\citeproctext]{ref-liu2012}
+Liu, C. C., \& Watanabe, T. (2012). Accounting for speed--accuracy tradeoff in perceptual learning. \emph{Vision Research}, \emph{61}, 107--114. \url{https://doi.org/10.1016/j.visres.2011.09.007}
+
+\bibitem[\citeproctext]{ref-parker2023a}
+Parker, S., \& Ramsey, R.
+(2023).
+What can evidence accumulation modelling tell us about human social cognition?
+\emph{Quarterly Journal of Experimental Psychology}, \emph{77}(3), 17470218231176950.
+\url{https://doi.org/10.1177/17470218231176950}
+
+\bibitem[\citeproctext]{ref-ratcliff2002}
+Ratcliff, R.
+(2002).
+A diffusion model account of response time and accuracy in a brightness discrimination task: {Fitting} real data and failing to fit fake but plausible data.
+\emph{Psychonomic Bulletin \& Review}, \emph{9}(2), 278--291.
+\url{https://doi.org/10.3758/BF03196283}
+
+\bibitem[\citeproctext]{ref-ratcliff2008}
+Ratcliff, R., \& McKoon, G.
+(2008).
+The {Diffusion Decision Model}: {Theory} and {Data} for {Two-Choice Decision Tasks}.
+\emph{Neural Computation}, \emph{20}(4), 873--922.
+\url{https://doi.org/10.1162/neco.2008.12-06-420}
+
+\bibitem[\citeproctext]{ref-ratcliff1998}
+Ratcliff, R., \& Rouder, J. N. (1998). Modeling {Response Times} for {Two-Choice Decisions}. \emph{Psychological Science}, \emph{9}(5), 347--356. \url{https://doi.org/10.1111/1467-9280.00067}
+
+\bibitem[\citeproctext]{ref-ratcliff2004}
+Ratcliff, R., Thapar, A., Gomez, P., \& McKoon, G.
+(2004).
+A {Diffusion Model Analysis} of the {Effects} of {Aging} in the {Lexical-Decision Task}.
+\emph{Psychology and Aging}, \emph{19}(2), 278--289.
+\url{https://doi.org/10.1037/0882-7974.19.2.278}
+
+\bibitem[\citeproctext]{ref-ratcliff2001}
+Ratcliff, R., Thapar, A., \& McKoon, G.
+(2001).
+The effects of aging on reaction time in a signal detection task.
+\emph{Psychology and Aging}, \emph{16}(2), 323--341.
+\url{https://doi.org/10.1037/0882-7974.16.2.323}
+
+\bibitem[\citeproctext]{ref-ratcliff2006}
+Ratcliff, R., Thapar, A., \& McKoon, G.
+(2006).
+Aging, practice, and perceptual tasks: {A} diffusion model analysis.
+\emph{Psychology and Aging}, \emph{21}(2), 353--371.
+\url{https://doi.org/10.1037/0882-7974.21.2.353}
+
+\bibitem[\citeproctext]{ref-ratcliff2010}
+Ratcliff, R., Thapar, A., \& McKoon, G.
+(2010).
+Individual differences, aging, and {IQ} in two-choice tasks.
+\emph{Cognitive Psychology}, \emph{60}(3), 127--157.
+\url{https://doi.org/10.1016/j.cogpsych.2009.09.001}
+
+\bibitem[\citeproctext]{ref-reinhartz2023}
+Reinhartz, A., Strobach, T., Jacobsen, T., \& von Bastian, C.
+C.
+(2023).
+Mechanisms of {Training-Related Change} in {Processing Speed}: {A Drift-Diffusion Model Approach}.
+\emph{Journal of Cognition}, \emph{6}(1), 46.
+\url{https://doi.org/10.5334/joc.310}
+
+\bibitem[\citeproctext]{ref-salthouse1996}
+Salthouse, T. A. (1996). The processing-speed theory of adult age differences in cognition. \emph{Psychological Review}, \emph{103}(3), 403--428. \url{https://doi.org/10.1037/0033-295X.103.3.403}
+
+\bibitem[\citeproctext]{ref-simmons2012}
+Simmons, J.
+P., Nelson, L.
+D., \& Simonsohn, U.
+(2012).
+\emph{A 21 {Word Solution}} (SSRN Scholarly Paper No.
+2160588).
+Rochester, NY: Social Science Research Network.
+\url{https://doi.org/10.2139/ssrn.2160588}
+
+\bibitem[\citeproctext]{ref-simons2016}
+Simons, D.
+J., Boot, W.
+R., Charness, N., Gathercole, S.
+E., Chabris, C.
+F., Hambrick, D.
+Z., \& Stine-Morrow, E.
+A.
+L.
+(2016).
+Do {``{Brain-Training}''} {Programs Work}?
+\emph{Psychological Science in the Public Interest}, \emph{17}(3), 103--186.
+\url{https://doi.org/10.1177/1529100616661983}
+
+\bibitem[\citeproctext]{ref-simons2017}
+Simons, D.
+J., Shoda, Y., \& Lindsay, D.
+S.
+(2017).
+Constraints on {Generality} ({COG}): {A Proposed Addition} to {All Empirical Papers}.
+\emph{Perspectives on Psychological Science}, \emph{12}(6), 1123--1128.
+\url{https://doi.org/10.1177/1745691617708630}
+
+\bibitem[\citeproctext]{ref-strobach2013}
+Strobach, T., Liepelt, R., Pashler, H., Frensch, P.
+A., \& Schubert, T.
+(2013).
+Effects of extensive dual-task practice on processing stages in simultaneous choice tasks.
+\emph{Attention, Perception, \& Psychophysics}, \emph{75}(5), 900--920.
+\url{https://doi.org/10.3758/s13414-013-0451-z}
+
+\bibitem[\citeproctext]{ref-vonbastian2022}
+von Bastian, C.
+C., Belleville, S., Udale, R.
+C., Reinhartz, A., Essounni, M., \& Strobach, T.
+(2022).
+Mechanisms underlying training-induced cognitive change.
+\emph{Nature Reviews Psychology}, \emph{1}(1), 30--41.
+\url{https://doi.org/10.1038/s44159-021-00001-3}
+
+\bibitem[\citeproctext]{ref-wagenmakers2008}
+Wagenmakers, E.-J., Ratcliff, R., Gomez, P., \& McKoon, G.
+(2008).
+A diffusion model account of criterion shifts in the lexical decision task.
+\emph{Journal of Memory and Language}, \emph{58}(1), 140--159.
+\url{https://doi.org/10.1016/j.jml.2007.04.006}
+
+\bibitem[\citeproctext]{ref-wagenmakers2007}
+Wagenmakers, E.-J., Van Der Maas, H.
+L.
+J., \& Grasman, R.
+P.
+P.
+P.
+(2007).
+An {EZ-diffusion} model for response time and accuracy.
+\emph{Psychonomic Bulletin \& Review}, \emph{14}(1), 3--22.
+\url{https://doi.org/10.3758/BF03194023}
+
+\bibitem[\citeproctext]{ref-weisberg2007}
+Weisberg, J., van Turennout, M., \& Martin, A.
+(2007).
+A {Neural System} for {Learning} about {Object Function}.
+\emph{Cerebral Cortex}, \emph{17}(3), 513--521.
+\url{https://doi.org/10.1093/cercor/bhj176}
+
+\bibitem[\citeproctext]{ref-white2022}
+White, C.
+N., \& Kitchen, K.
+N.
+(2022).
+On the {Need} to {Improve} the {Way Individual Differences} in {Cognitive Function Are Measured With Reaction Time Tasks}.
+\emph{Current Directions in Psychological Science}, \emph{31}(3), 223--230.
+\url{https://doi.org/10.1177/09637214221077060}
+
+\bibitem[\citeproctext]{ref-yarkoni2022}
+Yarkoni, T. (2022/ed). The generalizability crisis. \emph{Behavioral and Brain Sciences}, \emph{45}, e1. \url{https://doi.org/10.1017/S0140525X20001685}
+
+\bibitem[\citeproctext]{ref-zhang2014}
+Zhang, J., \& Rowe, J.
+B.
+(2014).
+Dissociable mechanisms of speed-accuracy tradeoff during visual perceptual learning are revealed by a hierarchical drift-diffusion model.
+\emph{Frontiers in Neuroscience}, \emph{8}.
+\url{https://doi.org/10.3389/fnins.2014.00069}
+
+\end{CSLReferences}
+
+\end{document}

### 2024-11-29 effects_lba.Rmd
added wrangle, model and effects .Rmd files

---
title: "effects_lba"
author: "Sam & Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file plots the posterior distributions for the LBA model results, including average estimates per training condition, as well as comparisons between training conditions.

# load packages #

Make sure the working directory is the top folder with the dmc and models folder

```{r}
source ("dmc/dmc.R")
load_model ("LBA","lba_B.R") # LBA model with B=b-A parameterization

pkg <- c("tidyverse", "RColorBrewer", "patchwork", "tidybayes")

lapply(pkg, library, character.only = TRUE)
```

# load the model #

```{r}
## The model object is available upon request
## Please email Samantha Parker (samantha.parker@students.mq.edu.au) or Richard Ramsey (richard.ramsey@hest.ethz.ch)
load("models/ea/modelKN.RData")
```

# set the grid for the multi-panel graph #

```{r}
design <- "
  11234
  11567
"
```

# plot settings #

theme settings for ggplot

```{r, eval = F}
theme_set(
  theme_bw() +
    theme(text = element_text(size = 18, face = "bold"), 
          title = element_text(size = 18, face = "bold"),
          legend.position = "bottom")
)

## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)
```

# 1. DRIFT RATE COMPARISONS - FIGURE 2 #

## calculate subject average medians for drift rates for TRUE - FALSE drift rate ##

```{r}
fun <- function(x){
  name <- diff(x[c("mean_v.name.false","mean_v.name.true")])            
  untrained <- diff(x[c("mean_v.untrained.false","mean_v.untrained.true")])            
  diff <- (untrained-name)
  c(name,untrained,diff)
}

knots.dv.1 <- compare.p(hKN,show.plot=TRUE,pretty=c("name","untrained"),
                        fun=fun,xlab="Average Rate")
knots.dv.1 <- as.data.frame(knots.dv.1)
knots.dv.1_long <- gather(knots.dv.1, training, value, name:contrast,
                          factor_key=TRUE)

#Remove contrast condition
knots.dv.1_long <- knots.dv.1_long %>% 
  filter(!training =="contrast")

#Do the same thing for tie and both
fun <- function(x){
  tie <- diff(x[c("mean_v.tie.false","mean_v.tie.true")])            
  both <- diff(x[c("mean_v.both.false","mean_v.both.true")])            
  diff <- (both-tie)
  c(tie,both,diff)
}

knots.dv.2 <- compare.p(hKN,show.plot=TRUE,pretty=c("tie","both"),
                        fun=fun,xlab="Average Rate")
knots.dv.2 <- as.data.frame(knots.dv.2)
knots.dv.2_long <- gather(knots.dv.2, training, value, tie:contrast, factor_key=TRUE)

#Remove contrast condition
knots.dv.2_long <- knots.dv.2_long %>% 
  filter(!training =="contrast")

#combine data frames
dv.comb  <- rbind(knots.dv.1_long, knots.dv.2_long)
dv.comb <- droplevels(dv.comb)

#reorder the levels
dv.comb$training <- factor(dv.comb$training, 
                           levels = c("untrained", "name", "tie", "both"))
```

## FIGURE 2A ##

Plot the drift rate difference by training condition

```{r}
p1.1 <- ggplot(dv.comb, aes(x = value, fill=training, y = training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(title = 'A',
       x = "Drift Rate Difference", y = "Training Condition") +
  scale_fill_brewer(palette = "Dark2") +
  # scale_y_discrete(limits=rev) +
  theme(legend.position="none")
p1.1
```

## FIGURE 2B ##

PAIRWISE COMPARISONS OF DRIFT RATE DIFFERENCE

Compute the differences

```{r}
#Name vs. untrained
fun <- function(x){
  name <- diff(x[c("mean_v.name.false","mean_v.name.true")])            
  untrained <- diff(x[c("mean_v.untrained.false","mean_v.untrained.true")])       
  diff <- (name-untrained)
  c(name,untrained,diff)
}

dr.1 <- compare.p(hKN,show.plot=TRUE,pretty=c("name","untrained"),
                  fun=fun,xlab="Average Rate")
dr.1 <- as.data.frame(dr.1)
dr.1_long <- gather(dr.1, training, value, name:contrast, factor_key=TRUE)

#Remove contrast condition
dr.1_long <- dr.1_long %>% 
  filter(training =="contrast")

#tie vs. untrained
fun <- function(x){
  tie <- diff(x[c("mean_v.tie.false","mean_v.tie.true")])            
  untrained <- diff(x[c("mean_v.untrained.false","mean_v.untrained.true")])     
  diff <- (tie-untrained)
  c(tie,untrained,diff)
}

dr.2 <- compare.p(hKN,show.plot=TRUE,pretty=c("tie","untrained"),
                  fun=fun,xlab="Average Rate")
dr.2 <- as.data.frame(dr.2)
dr.2_long <- gather(dr.2, training, value, tie:contrast, factor_key=TRUE)
dr.2_long <- dr.2_long %>% 
  filter(training =="contrast")

#both vs. untrained
fun <- function(x){
  both <- diff(x[c("mean_v.both.false","mean_v.both.true")])            
  untrained <- diff(x[c("mean_v.untrained.false","mean_v.untrained.true")])       
  diff <- (both-untrained)
  c(both,untrained,diff)
}

dr.3 <- compare.p(hKN,show.plot=TRUE,pretty=c("both","untrained"),
                  fun=fun,xlab="Average Rate")
dr.3 <- as.data.frame(dr.3)
dr.3_long <- gather(dr.3, training, value, both:contrast, factor_key=TRUE)
dr.3_long <- dr.3_long %>% 
  filter(training =="contrast")

#both vs. name
fun <- function(x){
  both <- diff(x[c("mean_v.both.false","mean_v.both.true")])            
  name <- diff(x[c("mean_v.name.false","mean_v.name.true")])            
  diff <- (both-name)
  c(both,name,diff)
}

dr.4 <- compare.p(hKN,show.plot=TRUE,pretty=c("both","name"),
                  fun=fun,xlab="Average Rate")
dr.4 <- as.data.frame(dr.4)
dr.4_long <- gather(dr.4, training, value, both:contrast, factor_key=TRUE)
dr.4_long <- dr.4_long %>% 
  filter(training =="contrast")

#both vs. tie
fun <- function(x){
  both <- diff(x[c("mean_v.both.false","mean_v.both.true")])            
  tie <- diff(x[c("mean_v.tie.false","mean_v.tie.true")])            
  diff <- (both-tie)
  c(both,tie,diff)
}

dr.5 <- compare.p(hKN,show.plot=TRUE,pretty=c("both","tie"),
                  fun=fun,xlab="Average Rate")
dr.5 <- as.data.frame(dr.5)
dr.5_long <- gather(dr.5, training, value, both:contrast, factor_key=TRUE)
dr.5_long <- dr.5_long %>% 
  filter(training =="contrast")

#name vs. tie
fun <- function(x){
  name <- diff(x[c("mean_v.name.false","mean_v.name.true")])            
  tie <- diff(x[c("mean_v.tie.false","mean_v.tie.true")])            
  diff <- (name-tie)
  c(name,tie,diff)
}

dr.6 <- compare.p(hKN,show.plot=TRUE,pretty=c("name","tie"),
                  fun=fun,xlab="Average Rate")
dr.6 <- as.data.frame(dr.6)
dr.6_long <- gather(dr.6, training, value, name:contrast, factor_key=TRUE)
dr.6_long <- dr.6_long %>% 
  filter(training =="contrast")
```

Plot the pairwise comparisons

```{r}
p1.1.1 <- ggplot(dr.1_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(title = 'B',
       x = "Name vs Untrained", y = "Density") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1,2), breaks = seq(-1,2,1))
p1.1.1
```

```{r}
p1.1.2 <- ggplot(dr.2_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .8, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(title = ' ',
       x = "Tie vs Untrained", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1,2), breaks = seq(-1,2,1))
p1.1.2
```

```{r}
p1.1.3 <- ggplot(dr.3_long, aes(x = value, fill=training)) +
     stat_halfeye(alpha = .7, .width = .95) +
    geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(title = NULL,
       x = "Both vs Untrained", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1,2), breaks = seq(-1,2,1))
p1.1.3
```

```{r}
p1.1.4 <- ggplot(dr.4_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(title = NULL,
       x = "Both vs Name", y = "Density") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1,2), breaks = seq(-1,2,1))
p1.1.4 
```

```{r}
p1.1.5 <- ggplot(dr.5_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .8, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(title = NULL,
       x = "Both vs Tie", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1,2), breaks = seq(-1,2,1))
p1.1.5
```

```{r}
p1.1.6 <- ggplot(dr.6_long, aes(x = value, fill=training)) +
     stat_halfeye(alpha = .8, .width = .95) +
    geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(title = NULL,
       x = "Name vs Tie", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1,2), breaks = seq(-1,2,1))
p1.1.6
```

Plot in multipanel

```{r}
p_drift <- p1.1 + p1.1.1 + p1.1.2 + p1.1.3 + p1.1.4 + p1.1.5 + p1.1.6 + 
  plot_layout(design=design)
p_drift

ggsave("figures/ea/drift_rate.jpeg",
       width = 14, height = 6, dpi = 800)
```

# 2. THRESHOLDS - FIGURE 3 #

## calculate subject average medians ##

```{r}
fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.name <- (name.same+name.diff)/2
  B.untrained <- (untrained.same+untrained.diff)/2
  c(B.name, B.untrained, B.name - B.untrained)
}

knots.b.1 <- compare.p(hKN,show.plot=TRUE,pretty=c("name","untrained"),
                 fun=fun,xlab="Threshold Name v Untrained")
knots.b.1 <- as.data.frame(knots.b.1)
knots.b.1_long <- gather(knots.b.1, training, value, name:contrast, factor_key=TRUE)

#Remove contrast condition
knots.b.1_long <- knots.b.1_long %>% 
  filter(!training =="contrast")

#Do the same for tie and both
fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.both <- (both.same+both.diff/2)
  B.tie <- (tie.same+tie.diff)/2
  c(B.both, B.tie, B.both - B.tie)
}
knots.b.2 <- compare.p(hKN,show.plot=TRUE,pretty=c("both","tie"),
                 fun=fun,xlab="Threshold Both v Tie")
knots.b.2 <- as.data.frame(knots.b.2)
knots.b.2_long <- gather(knots.b.2, training, value, both:contrast, factor_key=TRUE)

#Remove contrast condition
knots.b.2_long <- knots.b.2_long %>% 
  filter(!training =="contrast")

#combine data frames
b.comb  <- rbind(knots.b.1_long, knots.b.2_long)
b.comb <- droplevels(b.comb)

#reorder the levels
b.comb$training <- factor(b.comb$training, 
                          levels = c("untrained", "name", "tie", "both"))
```

## FIGURE 3A ##

plot thresholds

```{r}
p2.1 <- ggplot(b.comb, aes(x = value, fill=training, y = training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(title = 'A',
       x = "Threshold", y = "Training Condition") +
  scale_fill_brewer(palette = "Dark2") +
  theme(legend.position="none")
p2.1
```

## FIGURE 3B ##

PAIRWISE COMPARISONS - FIGURE 3B

Compute the differences

```{r}
fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.name <- (name.same+name.diff)/2
  B.untrained <- (untrained.same+untrained.diff)/2
  c(B.name, B.untrained, B.name - B.untrained)
}

b.1 <- compare.p(hKN,show.plot=TRUE,pretty=c("name","untrained"),
                 fun=fun,xlab="Threshold Name v Untrained")
b.1 <- as.data.frame(b.1)
b.1_long <- gather(b.1, training, value, name:contrast, factor_key=TRUE)
b.1_long <- b.1_long %>% 
  filter(training =="contrast")

fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.tie <- (tie.same+tie.diff)/2
  B.untrained <- (untrained.same+untrained.diff)/2
  c(B.tie, B.untrained, B.tie - B.untrained)
}

b.2 <- compare.p(hKN,show.plot=TRUE,pretty=c("tie","untrained"),
                 fun=fun,xlab="Threshold Tie v Untrained")
b.2 <- as.data.frame(b.2)
b.2_long <- gather(b.2, training, value, tie:contrast, factor_key=TRUE)
b.2_long <- b.2_long %>% 
  filter(training =="contrast")

fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.both <- (both.same+both.diff)/2
  B.untrained <- (untrained.same+untrained.diff)/2
  c(B.both, B.untrained, B.both - B.untrained)
}

b.3 <- compare.p(hKN,show.plot=TRUE,pretty=c("both","untrained"),
                 fun=fun,xlab="Threshold both v Untrained")
b.3 <- as.data.frame(b.3)
b.3_long <- gather(b.3, training, value, both:contrast, factor_key=TRUE)
b.3_long <- b.3_long %>% 
  filter(training =="contrast")

fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.both <- (both.same+both.diff)/2
  B.name <- (name.same+name.diff)/2
  c(B.both, B.name, B.both - B.name)
}

b.4 <- compare.p(hKN,show.plot=TRUE,pretty=c("both","name"),
                 fun=fun,xlab="Threshold both v name")
b.4 <- as.data.frame(b.4)
b.4_long <- gather(b.4, training, value, both:contrast, factor_key=TRUE)
b.4_long <- b.4_long %>% 
  filter(training =="contrast")

fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.both <- (both.same+both.diff)/2
  B.tie <- (tie.same+tie.diff)/2
  c(B.both, B.tie, B.both - B.tie)
}

b.5 <- compare.p(hKN,show.plot=TRUE,pretty=c("both","tie"),
                 fun=fun,xlab="Threshold both v tie")
b.5 <- as.data.frame(b.5)
b.5_long <- gather(b.5, training, value, both:contrast, factor_key=TRUE)
b.5_long <- b.5_long %>% 
  filter(training =="contrast")

fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.name <- (name.same+name.diff)/2
  B.tie <- (tie.same+tie.diff)/2
  c(B.name, B.tie, B.name - B.tie)
}

b.6<- compare.p(hKN,show.plot=TRUE,pretty=c("name","tie"),
                fun=fun,xlab="Threshold both v name")
b.6<- as.data.frame(b.6)
b.6_long <- gather(b.6, training, value, name:contrast, factor_key=TRUE)
b.6_long <- b.6_long %>% 
  filter(training =="contrast")
```

plot pairwise comparisons

```{r}
p2.1.1 <- ggplot(b.1_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(title = "B",
       x = "Name vs Untrained", y = "Density") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1.5,0.5), breaks = seq(-1,0))
p2.1.1
```

```{r}
p2.1.2 <- ggplot(b.2_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(x = "Tie vs Untrained", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1.5,0.5), breaks = seq(-1,0))
p2.1.2
```

```{r}
p2.1.3 <- ggplot(b.3_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(x = "Both vs Untrained", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1.5,0.5), breaks = seq(-1,0))
p2.1.3
```

```{r}
p2.1.4 <- ggplot(b.4_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(x = "Both vs Name", y = "Density") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1.5,0.5), breaks = seq(-1,0))
p2.1.4
```

```{r}
p2.1.5 <- ggplot(b.5_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(x = "Both vs Tie", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1.5,0.5), breaks = seq(-1,0))
p2.1.5
```

```{r}
p2.1.6 <- ggplot(b.6_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(x = "Name vs Tie", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1.5,0.5), breaks = seq(-1,0))
p2.1.6
```

Plot together

```{r}
p_thresh <- p2.1 + p2.1.1 + p2.1.2 + p2.1.3 + p2.1.4 + p2.1.5 + p2.1.6 +
  plot_layout(design=design)
p_thresh

ggsave("figures/ea/thresholds.jpeg",
       width = 14, height = 6, dpi = 800)
```

# 3. NON-DECISION TIME - FIGURE 4 #

## calculate subject average medians ##

```{r}
knots.t.1 <- compare.p(hKN,show.plot=TRUE,pnames=c("t0.name","t0.untrained"),
                 pretty=c("name","untrained"),xlab="Average t0")
knots.t.1 <- as.data.frame(knots.t.1)
knots.t.1_long <- gather(knots.t.1, training, value, name:contrast, factor_key=TRUE)

#Remove contrast condition
knots.t.1_long <- knots.t.1_long %>% 
  filter(!training =="contrast")

#Do the same for both and tie
knots.t.2 <- compare.p(hKN,show.plot=TRUE,pnames=c("t0.both","t0.tie"),
                 pretty=c("both","tie"),xlab="Average t0")
knots.t.2 <- as.data.frame(knots.t.2)
knots.t.2_long <- gather(knots.t.2, training, value, both:contrast, factor_key=TRUE)

#Remove contrast condition
knots.t.2_long <- knots.t.2_long %>% 
  filter(!training =="contrast")

#combine data frames
t.comb  <- rbind(knots.t.1_long, knots.t.2_long)
t.comb <- droplevels(t.comb)

#reorder the levels
t.comb$training <- factor(t.comb$training, 
                          levels = c("untrained", "name", "tie", "both"))
```

## FIGURE 4A ##

NON-DECISION TIME BY TRAINING CONDITION

```{r}
p3.1 <- ggplot(t.comb, aes(x = value, fill= training, y = training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "darkgrey",alpha = 5/10) +
  labs(title = 'A',
       x = "Non-decision Time", y = "Training Condition") +
  scale_fill_brewer(palette = "Dark2") +
  theme(legend.position="none")
p3.1
```

## FIGURE 4B ##

PAIRWISE COMPARISONS

Compute the differences between each training condition

```{r}
t.1 <- compare.p(hKN,show.plot=TRUE,pnames=c("t0.name","t0.untrained"),
                 pretty=c("name","untrained"),xlab="Average t0")
t.1 <- as.data.frame(t.1)
t.1_long <- gather(t.1, training, value, name:contrast, factor_key=TRUE)
t.1_long <- t.1_long %>% 
  filter(training =="contrast")

t.2 <- compare.p(hKN,show.plot=TRUE,pnames=c("t0.tie","t0.untrained"),
                 pretty=c("tie","untrained"),xlab="Average t0")
t.2 <- as.data.frame(t.2)
t.2_long <- gather(t.2, training, value, tie:contrast, factor_key=TRUE)
t.2_long <- t.2_long %>% 
  filter(training =="contrast")

t.3 <- compare.p(hKN,show.plot=TRUE,pnames=c("t0.both","t0.untrained"),
                 pretty=c("both","untrained"),xlab="Average t0")
t.3 <- as.data.frame(t.3)
t.3_long <- gather(t.3, training, value, both:contrast, factor_key=TRUE)
t.3_long <- t.3_long %>% 
  filter(training =="contrast")

t.4 <- compare.p(hKN,show.plot=TRUE,pnames=c("t0.both","t0.name"),
                 pretty=c("both","name"),xlab="Average t0")
t.4 <- as.data.frame(t.4)
t.4_long <- gather(t.4, training, value, both:contrast, factor_key=TRUE)
t.4_long <- t.4_long %>% 
  filter(training =="contrast")

t.5 <- compare.p(hKN,show.plot=TRUE,pnames=c("t0.both","t0.tie"),
                 pretty=c("both","tie"),xlab="Average t0")
t.5 <- as.data.frame(t.5)
t.5_long <- gather(t.5, training, value, both:contrast, factor_key=TRUE)
t.5_long <- t.5_long %>% 
  filter(training =="contrast")

t.6 <- compare.p(hKN,show.plot=TRUE,pnames=c("t0.name","t0.tie"),
                 pretty=c("name","tie"),xlab="Average t0")
t.6 <- as.data.frame(t.6)
t.6_long <- gather(t.6, training, value, name:contrast, factor_key=TRUE)
t.6_long <- t.6_long %>% 
  filter(training =="contrast")
```

plot pairwise comparisons

```{r}
p3.1.1 <- ggplot(t.1_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(title = 'B',
       x = "Name vs Untrained", y = "Density") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-0.1,0.4), breaks = seq(0,0.4,0.2))
p3.1.1
```

```{r}
p3.1.2 <- ggplot(t.2_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(x = "Tie vs Untrained", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-0.1,0.4), breaks = seq(0,0.4,0.2))
p3.1.2
```

```{r}
p3.1.3 <- ggplot(t.3_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(x = "Both vs Untrained", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-0.1,0.4), breaks = seq(0,0.4,0.2))
p3.1.3
```

```{r}
p3.1.4 <- ggplot(t.4_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(x = "Both vs Name", y = "Density") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-0.1,0.4), breaks = seq(0,0.4,0.2))
p3.1.4
```

```{r}
p3.1.5 <- ggplot(t.5_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(x = "Both vs Tie", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-0.1,0.4), breaks = seq(0,0.4,0.2))
p3.1.5
```

```{r}
p3.1.6 <- ggplot(t.6_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(x = "Name vs Tie", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-0.1,0.4), breaks = seq(0,0.4,0.2))
p3.1.6
```

Arrange together
```{r}
p_ndt <- p3.1 + p3.1.1 + p3.1.2 + p3.1.3 + p3.1.4 + p3.1.5 + p3.1.6 + 
  plot_layout(design =design)
p_ndt

ggsave("figures/ea/ndt.jpeg",
       width = 14, height = 6, dpi = 800)
```

### 2024-11-29 effects_lba_summary.Rmd
added wrangle, model and effects .Rmd files

--- 2024-11-26 effects.Rmd
@@
 
-I made a plot like this recently to summarise Raph's results.
-
-Eventually, we could add the rt dist for acc/inc in the raw data below, as we did for Raph's data.
-
 # load the libraries that we will be using #
-
-## load packages ##
 
@@
 
-## plot settings ##
+# plot settings #
 
@@
 
-## load the model object and/or data ##
+# load the model object #
 
@@
 ## Please email Samantha Parker (samantha.parker@students.mq.edu.au) or Richard Ramsey (richard.ramsey@hest.ethz.ch)
-## load("models/modelKN.RData") ##  
+load("models/ea/modelKN.RData") ##  
 load_model ("LBA","lba_B.R")
@@
 
-# section 1 - posterior predictions #
+# 1. posterior predictions #
 
@@
 ## create a ggplot ready (i.e., tidy) list of dfs at the group level ##
+
+This might take 30 seconds or so...
 
@@
 ## you could save a figure at this point, if you wanted
-ggsave("figures/ppreds.jpeg",
-       width = 10, height = 8)
+ggsave("figures/ea/ppreds_fit.jpeg",
+       width = 10, height = 8, dpi = 800)
 ```
 
-# section 2 #
-
-## what about visualising parameters from the model? ##
+# 2. visualise parameters from the model ##
 
@@
 
-Note to Raph/Sam and a reminder for Rich: One thing that took a little (or rather a lot of) figuring out was how the DMC compare.p convenience function calculates group average parameter estimates for the posterior distribution.
+Note to Sam and a reminder for Rich: One thing that took a little (or rather a lot of) figuring out was how the DMC compare.p convenience function calculates group average parameter estimates for the posterior distribution.
 It takes all pid posteriors, averages them first and then calculates the relevant quantiles to display and make inferences from.
@@
 
-ggsave("figures/all_params.jpeg",
-       width = 8, height = 6)
+# ggsave("figures/ea/all_params.jpeg",
+#        width = 8, height = 6)
 ```
@@
 p2.2
-
-ggsave("figures/all_params_pid.jpeg",
-       width = 10, height = 10)
+# ggsave("figures/all_params_pid.jpeg",
+#        width = 10, height = 10)
 ```
 
-Ok, at this point, we could wrangle the data and make some nice plots.
-For code on how to do this, see folder /pilot5_dmc/ in Raph's project.
+Ok, at this point, we could wrangle the data further and make some nice plots.
 But Sam has already done that using the compare.p function and so there is no real need to reproduce those.
-Instead, we should try to move on to visualise the average parameter estimates from the model in a LBA model type way.  
+
+Instead, we will try to move on to visualise the average parameter estimates from the model in a LBA model type way.  
 For that, we only need the average estimates per parameter, which we calculated above already.
 
-# Section 3 - make a plot to visualise the results in LBA model format? ##
+# 3. make a plot to visualise the results in LBA model format ##
 
@@
 visualisation?
-
-e.g., take the raw data and make density dists, then plot alongside the parameters but in model format, rather than posterior distributions?
 
@@
 of way. 
-And that way may be more intuitive and provide an overview for readers of the main findings.
+And by doing so, it may be more intuitive and provide an overview for readers of the main findings.
+However, the main conclusions will stem from the formal analysis of the posterior distribution (see effects_lba.Rmd for details).
 
@@
 
-ggsave("figures/lba_summary.jpeg",
+ggsave("figures/ea/lba_summary.jpeg",
        width = 8, height = 5, dpi=800)
@@
 
-How about we try to add rt and acc desnity plots like we did before with Raph's data?
-
-# Section 4 #
+# 4. How about we try to add rt and acc density plots? #
 
@@
 
-## summary data ##
+at the pid level
 
-at the pid level
+accuracy
 
@@
 ```
+
+rt
 
@@
 
+accuracy
+
 ```{r}
@@
 
-ggsave("figures/density_rt_acc.jpeg",
+ggsave("figures/ea/density_rt_acc.jpeg",
        width = 12, height = 8, dpi=800)
@@
 
-ggsave("figures/lba_rt_acc.jpeg",
+ggsave("figures/ea/lba_rt_acc.jpeg",
        width = 12, height = 10, dpi=800)

### 2024-11-29 effects_rt_acc.Rmd
added wrangle, model and effects .Rmd files

---
title: "effects_rt_acc"
author: "Sam & Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

Secondary analysis of manifest measures in knots data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file visualises and tabulates parameters in the most complex model from the manifest analysis of the knots data.

This file focusses on the effects from reaction time and accuracy models.

# load libraries #

```{r load-pkg}
pkg <- c("tidyverse", "RColorBrewer", "patchwork", "brms", "tidybayes", 
         "ggdist", "future", "bayesplot", "parallel", "here", "tinytable",
         "webshot2")

lapply(pkg, library, character.only = TRUE)
```

# plot settings #

theme settings for ggplot

```{r, eval = F}
theme_set(
  theme_bw() +
    theme(text = element_text(size = 18, face = "bold"), 
          title = element_text(size = 18, face = "bold"),
          legend.position = "bottom")
)

## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)
```

# table options #

```{r}
options(tinytable_tt_digits = 2,
        tinytable_print_output = "markdown")
```

# 1. look at reaction time #

## 1.1 read in model object, fits and data (as necessary) ##

```{r}
# rt
b1 <- readRDS("models/manifest/b1.rds")
```

read in the data

```{r}
# rt data
data_rt <- read_csv("data/processed/data_rt.csv") %>% 
  mutate(PID=factor(PID),
         GROUP = factor(GROUP,
                        levels = c("untrained", "name", "tie", "both")))
head(data_rt)
```

## 1.2 Look at the point and interval estimates for the full models ##

### summarise point and interval estimates for all aspects of the model ###

using posterior_samples and tidybayes

```{r}
post <- as_draws_df(b1) %>% #
  select(-lp__) %>% 
  as_tibble()

post_summary <- posterior_summary(b1, robust = TRUE)

# all fixed effects
post_qi_b <- post %>%
  select(starts_with("b_")) %>% 
  pivot_longer(everything()) %>% 
  group_by(name) %>% 
  median_qi(value)
head(post_qi_b)

# average varying effects - SD
post_qi_sd <- post %>%
  select(starts_with("sd_")) %>% 
  pivot_longer(everything()) %>% 
  group_by(name) %>% 
  median_qi(value)
head(post_qi_sd)

# varying effects by participant 
# I take this to be 18 pts x 5 terms (ndt_intercept, intercept, 3 levels of group) = 90 in total
vary_vals <- post %>%
  select(starts_with("r_")) %>% 
  pivot_longer(everything()) %>% 
  group_by(name) %>% 
  median_qi(value)
head(vary_vals)
```

### visualise fixed effects ###

Using posterior_samples and tidybayes

```{r}
## fixed effects of interest, excluding basic intercepts 
## Is this the right way to label the interaction?
tidy_fixed <- post %>% 
  select(starts_with("b_")) %>% # select and rename in simpler labels.
  pivot_longer(everything()) %>% # move from wide to long
  mutate(key = factor(name, levels=unique(name)),
         term = if_else(str_detect(name, "ndt"), "ndt_intercept",
                if_else(str_detect(name, "name"), "name",
                if_else(str_detect(name, "tie"), "tie",
                if_else(str_detect(name, "both"), "both", "intercept")))),
         term = factor(term, levels=unique(term)))
head(tidy_fixed)
tail(tidy_fixed)

## check labels
check.labels <- tidy_fixed %>% 
  group_by(key, term) %>% 
  distinct(key, term)
check.labels

# remove intercepts as they are on a different scale and make it difficult to plot
tidy_fixed <- tidy_fixed %>%
  filter(!term %in% c("intercept", "ndt_intercept"))
head(tidy_fixed)

check.labels <- tidy_fixed %>% 
  group_by(key, term) %>% 
  distinct(key, term)
check.labels

p_tidy_fixed <- ggplot(tidy_fixed, aes(x = value, y = fct_rev(term), 
                                       fill=term)) +  
  geom_vline(xintercept = 0, color = "grey", alpha = 5/10) +
  stat_halfeye(alpha=0.7) +
  labs(title = "fixed effects of condition",
       x = "Log(RT)", y = NULL) +
  scale_fill_brewer(palette = "Dark2")
p_tidy_fixed

ggsave ("figures/manifest/b1_fixef.jpeg")
```

### visualise varying effects ###

using posterior samples and tidybayes.

variance at the group level (i.e., intercepts and effects across participants)

```{r}
## random effects of interest, including item, as well as participant and effects across pts
tidy_varying <- post %>% 
  select(contains("sd_")) %>% 
  pivot_longer(everything()) %>% 
  mutate(key = factor(name, levels=unique(name)),
         term = if_else(str_detect(name, "ndt"), "ndt_intercept",
                if_else(str_detect(name, "name"), "name",
                if_else(str_detect(name, "tie"), "tie",
                if_else(str_detect(name, "both"), "both", "intercept")))),
         term = factor(term, levels=c("ndt_intercept", "intercept",
                                      "name", "tie", "both")))
head(tidy_varying)
tail(tidy_varying)
str(tidy_varying)

check.varying <- tidy_varying %>% 
  group_by(key, term) %>% 
  distinct(key, term)
check.varying

p_tidy_varying_pid <- ggplot(tidy_varying, aes(x = value, y = fct_rev(term))) +  
  geom_vline(xintercept = 0, color = "grey", alpha = 5/10) +
  stat_halfeye(alpha = 0.7) +
  labs(title = "SD plot for varying participant effects",
       x = NULL, y = NULL) +
  coord_cartesian(xlim =c(0, 0.5))+
  scale_x_continuous(breaks=seq(0,1,0.1))
p_tidy_varying_pid

ggsave ("figures/manifest/b1_varying_pid.jpeg")
```

### visualise variance within group levels ###

i.e., at the individual participant level

Note - this should be in a centred metric so that deviation from the group average (zero) can be visualised. All good, but interpreting intercepts in some cases can difficult because it is when all other factors are zero. It can therefore be a little difficult to interpret and they may not be completely symmetric around zero for that reason.

use output from posterior summary and wrangle

```{r}
# first filter and create new tibbles
# mutate here to create factors to preserve order of term - useful when plotting. Also create a new outlier variable and factor it. You could do the outlier variable in one step possibly using as_factor, but this does the job.

# participant level
vary_pt <- post_summary %>%
  data.frame() %>% 
  rownames_to_column("param") %>% 
  filter(str_detect(param, "r_PID"),
         str_detect(param, "cor", negate = TRUE)) %>% 
  mutate(term = if_else(str_detect(param, "ndt"), "ndt_intercept",
                if_else(str_detect(param, "name"), "name",
                if_else(str_detect(param, "tie"), "tie",
                if_else(str_detect(param, "both"), "both", "intercept")))),
        term = factor(term, levels=c("ndt_intercept", "intercept",
                                      "name", "tie", "both"))) %>%  
  arrange(term, Estimate) %>% 
  mutate(rank = rep(1:18, times=5),
         outlier = if_else(Q2.5 > 0 | Q97.5 < 0, "yes", "no"), 
         outlier = factor(outlier, levels = c("no", "yes")))
head(vary_pt)
```

plot varying effects via caterpillar plots

variation by participant

```{r}
p_tidy_varyvals <- ggplot(vary_pt, aes(x=rank, y=Estimate,
                                           colour=outlier))+
  geom_pointrange(aes(ymin=Q2.5,ymax=Q97.5),fatten = 0.5)+
  geom_hline(yintercept=0, colour = "red")+
  scale_colour_manual(values=c("darkgrey","black")) +
  labs(title = "Varying effects by participant",
       x = "participant id")+
  facet_wrap(~term) +
  theme(legend.position = "none")
p_tidy_varyvals

ggsave ("figures/manifest/b1_varyvals.jpeg")
```

## 1.3 plot in the original metric as a function of conditions ##

This can be useful to see what the model predicts in terms of reaction time or points on a scale, rather than parameter estimates. This is especially relevant for more complex models like shifted log normal models where individual parameters may be hard to interpret on their own.

### posterior predictions ###

calculate

```{r}
ppreds_rt <- data_rt %>%
  distinct(PID, GROUP) %>%
  add_epred_draws(b1) 
head(ppreds_rt)
tail(ppreds_rt)
```

summary

```{r}
ppreds_rt_g <- ppreds_rt %>% 
  group_by(GROUP, .draw) %>% 
  summarise(.epred = mean(.epred))
ppreds_rt_g
```

plot

```{r}
p_ppreds_rt <- ggplot(ppreds_rt_g, aes(x = GROUP, y = .epred, 
                                       fill=GROUP)) +  
  stat_halfeye(alpha=0.7) +
  labs(x = "condition", y = "RT (ms)") +
  scale_fill_brewer(palette = "Dark2") +
  theme(legend.position = "none")
p_ppreds_rt
```

calculate quantiles

```{r}
ppreds_rt_q <- ppreds_rt_g %>% 
  group_by(GROUP) %>% 
  median_qi(.epred)
ppreds_rt_q
```

make a table

```{r}
ppred_rt_tab <- ppreds_rt_q %>%
  select(GROUP, .epred, .lower, .upper) %>% 
  rename(condition = GROUP)
ppred_rt_tab

# ## make a table using tinytable
tt_rt_tab <- tt(ppred_rt_tab,
                caption="Posterior predictions for RT") %>% 
  theme_tt("striped")
tt_rt_tab

## save it as a png
save_tt(tt_rt_tab, here("tables/manifest", "b1_ppreds_rt.png"),
        overwrite = T)
```

# 2. look at accuracy #

## 2.1 read in model object, fits and data (as necessary) ##

```{r}
# acc
ab1 <- readRDS("models/manifest/ab1.rds")
```

read in the data

```{r}
# acc data
data_acc <- read_csv("data/processed/data_acc.csv") %>% 
    mutate(PID=factor(PID),
           GROUP = factor(GROUP,
                          levels = c("untrained", "name", "tie", "both")))
head(data_acc)
```

## 2.2 Look at the point and interval estimates for the full models ##

### summarise point and interval estimates for all aspects of the model ###

using posterior_samples and tidybayes

```{r}
post <- as_draws_df(ab1) %>% #
  select(-lp__) %>% 
  as_tibble()

post_summary <- posterior_summary(ab1, robust = TRUE)

# all fixed effects
post_qi_b <- post %>%
  select(starts_with("b_")) %>% 
  pivot_longer(everything()) %>% 
  group_by(name) %>% 
  median_qi(value)
head(post_qi_b)

# average varying effects - SD
post_qi_sd <- post %>%
  select(starts_with("sd_")) %>% 
  pivot_longer(everything()) %>% 
  group_by(name) %>% 
  median_qi(value)
head(post_qi_sd)

# varying effects by participant 
# I take this to be 18 pts x 4 terms (intercept, 3 levels of group) = 72 in total
vary_vals <- post %>%
  select(starts_with("r_")) %>% 
  pivot_longer(everything()) %>% 
  group_by(name) %>% 
  median_qi(value)
head(vary_vals)
```

### visualise fixed effects ###

Using posterior_samples and tidybayes

```{r}
## fixed effects of interest, excluding basic intercepts 
## Is this the right way to label the interaction?
tidy_fixed <- post %>% 
  select(starts_with("b_")) %>% # select and rename in simpler labels.
  pivot_longer(everything()) %>% # move from wide to long
  mutate(key = factor(name, levels=unique(name)),
         term = if_else(str_detect(name, "name"), "name",
                if_else(str_detect(name, "tie"), "tie",
                if_else(str_detect(name, "both"), "both", "intercept"))),
         term = factor(term, levels=unique(term)))
head(tidy_fixed)
tail(tidy_fixed)

## check labels
check.labels <- tidy_fixed %>% 
  group_by(key, term) %>% 
  distinct(key, term)
check.labels

# remove intercepts as they are on a different scale and make it difficult to plot
tidy_fixed <- tidy_fixed %>%
  filter(!term %in% c("intercept"))
head(tidy_fixed)

check.labels <- tidy_fixed %>% 
  group_by(key, term) %>% 
  distinct(key, term)
check.labels

p_tidy_fixed <- ggplot(tidy_fixed, aes(x = value, y = fct_rev(term), 
                                       fill=term)) +  
  geom_vline(xintercept = 0, color = "grey", alpha = 5/10) +
  stat_halfeye(alpha=0.7) +
  labs(title = "fixed effects of condition",
       x = "Accuracy", y = NULL) +
  scale_fill_brewer(palette = "Dark2")
p_tidy_fixed

ggsave ("figures/manifest/ab1_fixef.jpeg")
```

### visualise varying effects ###

using posterior samples and tidybayes.

variance at the group level (i.e., intercepts and effects across participants)

```{r}
## random effects of interest, including item, as well as participant and effects across pts
tidy_varying <- post %>% 
  select(contains("sd_")) %>% 
  pivot_longer(everything()) %>% 
  mutate(key = factor(name, levels=unique(name)),
         term = if_else(str_detect(name, "name"), "name",
                if_else(str_detect(name, "tie"), "tie",
                if_else(str_detect(name, "both"), "both", "intercept"))),
         term = factor(term, levels=c("intercept",
                                      "name", "tie", "both")))
head(tidy_varying)
tail(tidy_varying)
str(tidy_varying)

check.varying <- tidy_varying %>% 
  group_by(key, term) %>% 
  distinct(key, term)
check.varying

p_tidy_varying_pid <- ggplot(tidy_varying, aes(x = value, 
                                               y = fct_rev(term))) +  
  geom_vline(xintercept = 0, color = "grey", alpha = 5/10) +
  stat_halfeye(alpha = 0.7) +
  labs(title = "SD plot for varying participant effects",
       x = NULL, y = NULL) +
  coord_cartesian(xlim =c(0, 1))+
  scale_x_continuous(breaks=seq(0,1,0.1))
p_tidy_varying_pid

ggsave ("figures/manifest/ab1_varying_pid.jpeg")
```

### visualise variance within group levels ###

i.e., at the individual participant level

Note - this should be in a centred metric so that deviation from the group average (zero) can be visualised. All good, but interpreting intercepts in some cases can difficult because it is when all other factors are zero. It can therefore be a little difficult to interpret and they may not be completely symmetric around zero for that reason.

use output from posterior summary and wrangle

```{r}
# first filter and create new tibbles
# mutate here to create factors to preserve order of term - useful when plotting. Also create a new outlier variable and factor it. You could do the outlier variable in one step possibly using as_factor, but this does the job.

# participant level
vary_pt <- post_summary %>%
  data.frame() %>% 
  rownames_to_column("param") %>% 
  filter(str_detect(param, "r_PID"),
         str_detect(param, "cor", negate = TRUE)) %>% 
  mutate(term = if_else(str_detect(param, "name"), "name",
                if_else(str_detect(param, "tie"), "tie",
                if_else(str_detect(param, "both"), "both", "intercept"))),
         term = factor(term, levels=c("intercept",
                                      "name", "tie", "both"))) %>%  
  arrange(term, Estimate) %>% 
  mutate(rank = rep(1:18, times=4),
         outlier = if_else(Q2.5 > 0 | Q97.5 < 0, "yes", "no"), 
         outlier = factor(outlier, levels = c("no", "yes")))
head(vary_pt)
```

plot varying effects via caterpillar plots

variation by participant

```{r}
p_tidy_varyvals <- ggplot(vary_pt, aes(x=rank, y=Estimate,
                                           colour=outlier))+
  geom_pointrange(aes(ymin=Q2.5,ymax=Q97.5),fatten = 0.5)+
  geom_hline(yintercept=0, colour = "red")+
  scale_colour_manual(values=c("darkgrey","black")) +
  labs(title = "Varying effects by participant",
       x = "participant id")+
  facet_wrap(~term) +
  theme(legend.position = "none")
p_tidy_varyvals

ggsave ("figures/manifest/ab1_varyvals.jpeg")
```

## 2.3 plot in the original metric as a function of conditions ##

This can be useful to see what the model predicts in terms of reaction time or points on a scale, rather than parameter estimates. This is especially relevant for more complex models like shifted log normal models where individual parameters may be hard to interpret on their own.

### posterior predictions ###

calculate

```{r}
ppreds_acc <- data_acc %>%
  distinct(PID, GROUP) %>%
  add_epred_draws(ab1) 
head(ppreds_acc)
tail(ppreds_acc)
```

summary

```{r}
ppreds_acc_g <- ppreds_acc %>% 
  group_by(GROUP, .draw) %>% 
  summarise(.epred = mean(.epred))
ppreds_acc_g
```

plot

```{r}
p_ppreds_acc <- ggplot(ppreds_acc_g, aes(x = GROUP, y = .epred, 
                                       fill=GROUP)) +  
  stat_halfeye(alpha=0.7) +
  labs(x = "condition", y = "accuracy (%)") +
  scale_fill_brewer(palette = "Dark2") +
  theme(legend.position = "none")
p_ppreds_acc
```

calculate quantiles

```{r}
ppreds_acc_q <- ppreds_acc_g %>% 
  group_by(GROUP) %>% 
  median_qi(.epred)
ppreds_acc_q
```

make a table

```{r}
ppred_acc_tab <- ppreds_acc_q %>%
  select(GROUP, .epred, .lower, .upper) %>% 
  rename(condition = GROUP)
ppred_acc_tab

# ## make a table using tinytable
tt_acc_tab <- tt(ppred_acc_tab,
                caption="Posterior predictions for accuracy") %>% 
  theme_tt("striped")
tt_acc_tab

## save it as a png
save_tt(tt_acc_tab, here("tables/manifest", "ab1_ppreds_acc.png"),
        overwrite = T)
```

# 3. plot ppreds for RT and Accuracy together #

```{r}
p_ppreds <- (p_ppreds_acc | p_ppreds_rt) +
  plot_annotation(title = "Posterior predictions for accuracy and RT",
                  tag_levels = 'A')
p_ppreds

ggsave("figures/manifest/ppreds.jpeg",
       width = 10, height = 6, dpi = 800)
```

### 2024-11-29 model_lba.Rmd
added wrangle, model and effects .Rmd files

---
title: "model_lba"
author: "Sam & Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This script sets up the LBA model, loads in the raw data, fits the model to the data and then samples the hLBA. There are tests at the bottom that compare parameter estimates.

Note - you need to make sure the working directory is the top directory with the models and dmc folder

# load data, models and packages #

```{r}
source ("dmc/dmc.R")
load_model ("LBA","lba_B.R") # LBA model with B=b-A parameterization

library(tidyverse)
```

Load in the model object if previously run

```{r}
## The model object is available upon request
## Please email Samantha Parker (samantha.parker@students.mq.edu.au) or Richard Ramsey (richard.ramsey@hest.ethz.ch)
# load("models/ea/modelKN.RData")
```

Load in the raw data (and convert names to match the labels that Sam used when fitting the LBA model)

Knots Data 
s: Subject ID (1-18)
S: Stimulus (match vs. mismatch)
GRP: Training Group (name vs. tie vs. both vs. untrained)
R: Response (same vs. different)
RT: Reaction Time (seconds)

For DMC, we also need to rename the levels of the response so that they are unique to stimulus.

```{r}
data_lba <- read_csv("data/processed/data_lba.csv") %>%
  ## rename group
  rename(GRP = GROUP) %>% 
  ## reorder
  select(s, S, GRP, R, RT) %>% 
  ## rename levels of variables
  mutate(S = if_else(S==1, "match", "mis"),
         R = if_else(R==1, "same", "diff")) %>% 
  ## create factors
  mutate(s = factor(s),
         S = factor(S,
                    levels = c("match", "mis")),
         GRP = factor(GRP,
                      levels = c("name", "tie", "both", "untrained")), ## this is the order Sam used.
         R = factor(R,
                    levels = c("same", "diff"))) %>% 
  as.data.frame() ## dmc prefers a data frame rather than a tibble
head(data_lba)
str(data_lba)
```

rename the data to match Sam's naming

```{r}
data_knots <- data_lba
```

# STEP 1: Set up the Model Object #

1) List the factors

In this design have a stimulus factor and a group factor (GRP)

```{r}
factors <- list(S=c("match","mis"), GRP=c("name","tie", "both", "untrained")) 
```

2) List of responses

```{r}
responses <- c("same","diff") # Can identify two pictures as the same or different
```

3) Match map
Specify which accumulator matches which response

```{r}
match.map <- list(M=list(match="same",mis="diff"))
```

4) p.map specifies how the model parameters match to the factors

In this design the threshold parameter (B) can be influenced by GRP and Response (R)
The drift rate parameter (mean_v) is influenced by GRP and Match
The non-decision time parameter (t0) can be influenced by the GRP factor
When specified as 1 this assumes that the parameter is the same for all accumulators

```{r}
p.map <- list(A="1",B=c("GRP", "R"),t0=c("GRP"),mean_v=c("GRP", "M"),sd_v="M",st0="1") #M needs to be put last
```

5) Constants

```{r}
const <- c(sd_v.false=1,st0=0)
```

6) Create data.model object

```{r}
model <- model.dmc(p.map,match.map=match.map,constants=const,responses=responses,
                   factors=factors)
```

Parameter vector names are: ( see attr(,"p.vector") )
 [1] "A"                      "B.name.same"            "B.tie.same"             "B.both.same"            "B.untrained.same"      
 [6] "B.name.diff"            "B.tie.diff"             "B.both.diff"            "B.untrained.diff"       "t0.name"               
[11] "t0.tie"                 "t0.both"                "t0.untrained"           "mean_v.name.true"       "mean_v.tie.true"       
[16] "mean_v.both.true"       "mean_v.untrained.true"  "mean_v.name.false"      "mean_v.tie.false"       "mean_v.both.false"     
[21] "mean_v.untrained.false" "sd_v.true"

Constants are (see attr(,"constants") ):
sd_v.false        st0 
         1          0

Model type = norm (posdrift= TRUE )

# STEP 2: COMBINE MODEL WITH DATA #

7) Simulate the data to make sure the model is set up correctly

```{r}
p.vector<- c(A = 1, 
             B.name.same = 0.5, 
             B.tie.same = 0.5, 
             B.both.same = 0.5, 
             B.untrained.same = 0.5, 
             B.name.diff = 0.5, 
             B.tie.diff = 0.5, 
             B.both.diff = 0.5, 
             B.untrained.diff = 0.5, 
             t0.name = .2, 
             t0.tie = .2, 
             t0.both = .2,
             t0.untrained = .2,
             mean_v.name.true = 1, 
             mean_v.tie.true = 1, 
             mean_v.both.true = 1, 
             mean_v.untrained.true = 1,
             mean_v.name.false = 0, 
             mean_v.tie.false = 0, 
             mean_v.both.false = 0, 
             mean_v.untrained.false = 0,
             sd_v.true = 0.5) #
check.p.vector(p.vector,model) #If everything ok nothing returned
print.cell.p(p.vector,model)

# Simulate this is for one subject
data <- simulate.dmc(p.vector,model,1e4)
data.model <- data.model.dmc(data,model)
plot.cell.density(data.model[data.model$S=='match',],C="same")
plot.cell.density(data.model[data.model$S=='match',],C="diff")

#This is for 20 subjects, 40 data points per subject
data1 <- h.simulate.dmc(model,ps=p.vector,ns=20,n=40)
data1.model <- data.model.dmc(data1,model)
```

8) Create the data model object

```{r}
data.model <- data.model.dmc(data_knots,model)
```

Plot the first two subjects to check

```{r}
 par(mfcol=c(2,4)) 
 for (i in 1:2) {
   plot.cell.density(data.cell=data.model[[i]][data.model[[i]]$GRP=="name" & data.model[[i]]$S=="match",],C="same")
   plot.cell.density(data.cell=data.model[[i]][data.model[[i]]$GRP=="name" & data.model[[i]]$S=="match",],C="diff")
   plot.cell.density(data.cell=data.model[[i]][data.model[[i]]$GRP=="tie" & data.model[[i]]$S=="mis",],C="mis")
   plot.cell.density(data.cell=data.model[[i]][data.model[[i]]$GRP=="tie" & data.model[[i]]$S=="mis",],C="same")
 }  
```

Save the data model object

```{r}
dmKN <- data.model
save(data.model, file = "data/ea/models/dmKN.RData")
```

# STEP 3: CREATE PRIORS #

Threshold parameters are 1
Start point parameters is 1
Rate parameters are 1 for matching accumulators and 0 for mismatching accumulators
sv for matching is .5
t0 is .2
t0 is truncated at 1 seconds, v is unbounded, A, B, and sd

```{r}
## Standard deviations of population priors should be broad. Means should be roughly plausible values. 
pop.mean <- c(A = 1, 
             B.name.same = 0.5, 
             B.tie.same = 0.5, 
             B.both.same = 0.5, 
             B.untrained.same = 0.5, 
             B.name.diff = 0.5, 
             B.tie.diff = 0.5, 
             B.both.diff = 0.5, 
             B.untrained.diff = 0.5, 
             t0.name = .2, 
             t0.tie = .2, 
             t0.both = .2,
             t0.untrained = .2,
             mean_v.name.true = 1, 
             mean_v.tie.true = 1, 
             mean_v.both.true = 1, 
             mean_v.untrained.true = 1,
             mean_v.name.false = 0, 
             mean_v.tie.false = 0, 
             mean_v.both.false = 0, 
             mean_v.untrained.false = 0,
             sd_v.true = 0.5) #
pop.scale <-c(A = 2, 
             B.name.same = 2, 
             B.tie.same = 2, 
             B.both.same = 2, 
             B.untrained.same = 2, 
             B.name.diff = 2, 
             B.tie.diff = 2, 
             B.both.diff = 2, 
             B.untrained.diff = 2, 
             t0.name = 2, 
             t0.tie = 2, 
             t0.both = 2,
             t0.untrained = 2,
             mean_v.name.true = 2, 
             mean_v.tie.true = 2, 
             mean_v.both.true = 2, 
             mean_v.untrained.true = 2,
             mean_v.name.false = 2, 
             mean_v.tie.false = 2, 
             mean_v.both.false = 2, 
             mean_v.untrained.false = 2,
             sd_v.true = 2) #
pop.prior <- prior.p.dmc(
  dists = rep("tnorm",22),
  p1=pop.mean,p2=pop.scale,
  lower=c(0,0,0,0,0,0,0,0,0,0.1,0.1,0.1,0.1,NA,NA,NA,NA,NA,NA,NA,NA,0),
  upper=c(NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,1)
)
```

Check the distributions

```{r}
par(mfcol=c(2,5)); for (i in names(pop.prior)) plot.prior(i,pop.prior)
```

# STEP 4: SAMPLING - FIT FIXED EFFECTS AND HIERARCHICAL #

1) Specify the priors

```{r}
p.prior <- prior.p.dmc(
  dists = rep("tnorm",22),
  p1=pop.mean,p2=pop.scale,
  lower=c(0,0,0,0,0,0,0,0,0,0.1,0.1,0.1,0.1,NA,NA,NA,NA,NA,NA,NA,NA,0),
  upper=c(NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,1)
)
```

2) Set up the sampling object called sKN

```{r}
sKN  <- h.samples.dmc(nmc = 120, p.prior, data.model)
```

## Automatic Script for sampling ##

Fits fixed effects first and uses these as starting appoints for the full hierarchical model

```{r}
tmp=load("models/ea/modelKN.RData")
cores=length(sKN)

# Fixed effects, comment out on subsequent runs
sKN <- h.RUN.dmc(sKN,cores=cores)
save(dmKN,sKN,file="models/ea/donesmodelKN.RData")
# Make hierarchical, comment out on subsequent runs
p.prior <- sKN[[1]]$p.prior
p1 <- get.p.vector(sKN[[1]])[names(p.prior)]
s.prior <- prior.p.dmc(p1=p1,p2=p1,
                       dists=rep("gamma",length(p1)))
pp.prior=list(p.prior,s.prior)
hstart <- make.hstart(sKN)
theta1 <- make.theta1(sKN)
hKN <- h.samples.dmc(nmc=100,p.prior,dmKN,pp.prior,
                    hstart.prior=hstart,theta1=theta1,thin=10)
rm(dmKN,sKN); gc()

# Hierarhcial fit, comment out all but the next line on subsequent runs
pp.prior <- attr(hKN,"hyper")$pp.prior
hKN  <- h.run.unstuck.dmc(hKN, p.migrate = .05, cores = cores)
save(hKN,file="models/ea/modelKN.RData")
hKN <- h.run.converge.dmc(h.samples.dmc(nmc=100, samples=hKN),
                      thorough=TRUE,nmc=50,cores=cores,finalrun=TRUE,finalI=250)
save(hKN,file="models/ea/modelKN.RData")

# Uncomment the following and make more copies to run more fits.
# hX <- h.run.dmc(h.samples.dmc(samples=hX,nmc=250),cores=cores,report=10)
# save(hX,file="models/ea/modelX.RData")

# Make diagnostics, tweak layout as desired
pdf("figures/ea/modelKN_chains.pdf",height=6,width = 8)
plot.dmc(hKN,hyper=TRUE,pll.chain=TRUE) 
plot.dmc(hKN,hyper=TRUE,layout=c(3,3))
plot.dmc(hKN,hyper=TRUE,layout=c(4,4),p.prior=pp.prior)
dev.off()

ppKN <- h.post.predict.dmc(hKN)
save(hKN,ppKN,file="models/ea/modelKN.RData")
pdf("figures/ea/KN_fit.pdf",height=6, width=8)
plot.pp.dmc(ppKN,model.legend = TRUE,layout=c(2,4))
dev.off()

h.IC.dmc(hKN,DIC=TRUE)

gelman.diag.dmc(hKN,hyper=TRUE)
gelman.diag.dmc(hKN)

parsKN <- summary.dmc(hKN,hyper=TRUE) # Summary of the hyper posterior sample
round(parsKN$quantiles[,c(1,3,5)],3)
parsKN <- summary.dmc(hKN) # Summary of the posterior samples for each participant.
save(hKN, ppKN, parsKN,file="models/ea/modelKN.RData")
```

# STEP 5: PARAMETER ESTIMATES #

List of parameters since you will use these names in the parameter tests

Parameter vector names are: ( see attr(,"p.vector") )
 [1] "A"                      "B.name.same"            "B.tie.same"             "B.both.same"            "B.untrained.same"      
 [6] "B.name.diff"            "B.tie.diff"             "B.both.diff"            "B.untrained.diff"       "t0.name"               
[11] "t0.tie"                 "t0.both"                "t0.untrained"           "mean_v.name.true"       "mean_v.tie.true"       
[16] "mean_v.both.true"       "mean_v.untrained.true"  "mean_v.name.false"      "mean_v.tie.false"       "mean_v.both.false"     
[21] "mean_v.untrained.false" "sd_v.true"

Constants are (see attr(,"constants") ):
sd_v.false        st0 
         1          0

## DRIFT RATES ##

Calculate subject average medians for drift rates for TRUE - FALSE drift rate

```{r}
fun <- function(x) {
  c(diff(x[c("mean_v.name.false","mean_v.name.true")]),
    diff(x[c("mean_v.tie.false","mean_v.tie.true")]),
    diff(x[c("mean_v.both.false", "mean_v.both.true")]),
    diff(x[c("mean_v.untrained.false", "mean_v.untrained.true")]))
}

pretty <-  c("name","tie", "both", "untrained") #Set the names

ci.dv <- subject.average.ci(hKN,fun=fun,pretty=pretty)
round(ci.dv,2)

#       name  tie both untrained
# 2.5%  2.01 2.13 2.74      1.85
# 50%   2.30 2.39 3.12      2.08
# 97.5% 2.60 2.67 3.53      2.31
```

Parameter test of difference

```{r}
#Compare training effects against untrained

#Name vs. untrained
fun <- function(x){
  name <- diff(x[c("mean_v.name.false","mean_v.name.true")])            
  untrained <- diff(x[c("mean_v.untrained.false","mean_v.untrained.true")])            
  diff <- (untrained-name)
  c(name,untrained,diff)
}

compare.p(hKN,show.plot=TRUE,pretty=c("name","untrained"),fun=fun,xlab="Average Rate")

#        name untrained contrast
# 2.5%  2.011     1.848   -0.596
# 50%   2.296     2.076   -0.222
# 97.5% 2.595     2.315    0.154
# p.gt.0 
#  0.126

#tie vs. untrained
fun <- function(x){
  tie <- diff(x[c("mean_v.tie.false","mean_v.tie.true")])            
  untrained <- diff(x[c("mean_v.untrained.false","mean_v.untrained.true")])            
  diff <- (untrained-tie)
  c(tie,untrained,diff)
}

compare.p(hKN,show.plot=TRUE,pretty=c("tie","untrained"),fun=fun,xlab="Average Rate")

#         tie untrained contrast
# 2.5%  2.129     1.848   -0.671
# 50%   2.390     2.076   -0.313
# 97.5% 2.666     2.315    0.043
# p.gt.0 
#  0.042

#both vs. untrained
fun <- function(x){
  both <- diff(x[c("mean_v.both.false","mean_v.both.true")])            
  untrained <- diff(x[c("mean_v.untrained.false","mean_v.untrained.true")])            
  diff <- (untrained-both)
  c(both,untrained,diff)
}

compare.p(hKN,show.plot=TRUE,pretty=c("both","untrained"),fun=fun,xlab="Average Rate")

#        both untrained contrast
# 2.5%  2.744     1.848   -1.511
# 50%   3.122     2.076   -1.044
# 97.5% 3.531     2.315   -0.606
# p.gt.0 
#      0

#both vs. name
fun <- function(x){
  both <- diff(x[c("mean_v.both.false","mean_v.both.true")])            
  name <- diff(x[c("mean_v.name.false","mean_v.name.true")])            
  diff <- (name-both)
  c(both,name,diff)
}

compare.p(hKN,show.plot=TRUE,pretty=c("both","name"),fun=fun,xlab="Average Rate")

#        both     name contrast
# 2.5%  2.744     2.011   -1.322
# 50%   3.122     2.296   -0.825
# 97.5% 3.531     2.595   -0.327
# p.gt.0 
#  0.001

#both vs. tie
fun <- function(x){
  both <- diff(x[c("mean_v.both.false","mean_v.both.true")])            
  tie <- diff(x[c("mean_v.tie.false","mean_v.tie.true")])            
  diff <- (tie-both)
  c(both,tie,diff)
}

compare.p(hKN,show.plot=TRUE,pretty=c("both","tie"),fun=fun,xlab="Average Rate")

#        both   tie contrast
# 2.5%  2.744 2.129   -1.204
# 50%   3.122 2.390   -0.734
# 97.5% 3.531 2.666   -0.262
# p.gt.0 
#  0.001

```

## THRESHOLDS ##

Thresholds

 "B.name.same"            "B.tie.same"             "B.both.same"            "B.untrained.same"      
 "B.name.diff"            "B.tie.diff"             "B.both.diff"            "B.untrained.diff"

Not interested in these differences but check anyway.
Look at B for same v diff collapsing over training type
```{r}
fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  c(B.same <- (name.same+tie.same+both.same+untrained.same)/4,
  B.diff <- (name.diff+tie.diff+both.diff+untrained.diff)/4)
}

pretty <-  c("B.same","B.diff") #Set the names

ci.dv <- subject.average.ci(hKN,fun=fun,pretty=pretty)
round(ci.dv,2)

#       B.same B.diff
# 2.5%    1.03   0.78
# 50%     1.11   0.84
# 97.5%   1.19   0.90

#Parameter test to compare B for RJA vs. Con
fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.same <- (name.same+tie.same+both.same+untrained.same)/4
  B.diff <- (name.diff+tie.diff+both.diff+untrained.diff)/4
  c(B.same, B.diff, B.same - B.diff)
}
compare.p(hKN,show.plot=TRUE,pretty=c("BSame","BDiff"),fun=fun,xlab="Threshold Same v Diff")

#       BSame BDiff contrast
# 2.5%  1.035 0.778    0.195
# 50%   1.110 0.840    0.270
# 97.5% 1.188 0.903    0.346
# p.gt.0 
#      1 
```

Check B collapsing across same and diff by training condition

```{r}
fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  c(B.name <- (name.same+name.diff)/2,
  B.tie <- (tie.same+tie.diff)/2,
  B.both <- (both.same+both.diff/2),
  B.untrained <- (untrained.same+untrained.diff/2))
}

pretty <-  c("B.name","B.tie", "B.both", "B.untrained") #Set the names

ci.dv <- subject.average.ci(hKN,fun=fun,pretty=pretty)
round(ci.dv,2)

#       B.name B.tie B.both B.untrained
# 2.5%    0.64  0.57   0.84        2.60
# 50%     0.76  0.68   1.01        2.80
# 97.5%   0.88  0.79   1.19        3.03

#Parameter Tests

#Name vs. untrained
fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.name <- (name.same+name.diff)/2
  B.untrained <- (untrained.same+untrained.diff)/2
  c(B.name, B.untrained, B.name - B.untrained)
}
compare.p(hKN,show.plot=TRUE,pretty=c("BName","BUntrained"),fun=fun,xlab="Threshold Name v Untrained")

#       BName BUntrained contrast
# 2.5%  0.635      1.702   -1.250
# 50%   0.756      1.829   -1.075
# 97.5% 0.880      1.970   -0.894
# p.gt.0 
#      0

#Tie vs. untrained
fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.tie <- (tie.same+tie.diff)/2
  B.untrained <- (untrained.same+untrained.diff)/2
  c(B.tie, B.untrained, B.tie - B.untrained)
}
compare.p(hKN,show.plot=TRUE,pretty=c("BTie","BUntrained"),fun=fun,xlab="Threshold Tie v Untrained")

#        BTie BUntrained contrast
# 2.5%  0.573      1.702   -1.332
# 50%   0.677      1.829   -1.150
# 97.5% 0.787      1.970   -0.985
# p.gt.0 
#      0

#Both vs. untrained
fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.both <- (both.same+both.diff/2)
  B.untrained <- (untrained.same+untrained.diff)/2
  c(B.both, B.untrained, B.both - B.untrained)
}
compare.p(hKN,show.plot=TRUE,pretty=c("BBoth","BUntrained"),fun=fun,xlab="Threshold Both v Untrained")

#       BBoth BUntrained contrast
# 2.5%  0.845      1.702   -1.041
# 50%   1.012      1.829   -0.815
# 97.5% 1.189      1.970   -0.595
# p.gt.0 
#      0

#Both vs. name
fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.both <- (both.same+both.diff/2)
  B.name <- (name.same+name.diff)/2
  c(B.both, B.name, B.both - B.name)
}
compare.p(hKN,show.plot=TRUE,pretty=c("BBoth","BName"),fun=fun,xlab="Threshold Both v Name")

#      BBoth BName contrast
# 2.5%  0.845 0.635    0.042
# 50%   1.012 0.756    0.256
# 97.5% 1.189 0.880    0.477
# p.gt.0 
#   0.99

#Both vs. tie
fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.both <- (both.same+both.diff/2)
  B.tie <- (tie.same+tie.diff)/2
  c(B.both, B.tie, B.both - B.tie)
}
compare.p(hKN,show.plot=TRUE,pretty=c("BBoth","BTie"),fun=fun,xlab="Threshold Both v Tie")

#       BBoth  BTie contrast
# 2.5%  0.845 0.573    0.136
# 50%   1.012 0.677    0.335
# 97.5% 1.189 0.787    0.538
# p.gt.0 
#      1

#Name v Tie
fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.name <- (name.same+name.diff)/2
  B.tie <- (tie.same+tie.diff)/2
  c(B.name, B.tie, B.name - B.tie)
}
compare.p(hKN,show.plot=TRUE,pretty=c("Bname","BTie"),fun=fun,xlab="Threshold Name v Tie")

#       Bname  BTie contrast
# 2.5%  0.635 0.573   -0.087
# 50%   0.756 0.677    0.079
# 97.5% 0.880 0.787    0.240
# p.gt.0 
#  0.819

```

Parameter test of difference
"t0.name"               "t0.tie"                 "t0.both"                "t0.untrained"

```{r}
#Compare validity effect at each level of congruency

fun <- function(x){
  name <- (x[c( "t0.name")])  
  tie <- (x[c("t0.tie")])             
  both <- (x[c("t0.both")])             
  untrained <- (x[c("t0.untrained")])             
  c(t0.name <- (name),
  t0.tie <- (tie),
  t0.both <- (both),
  t0.untrained <- (untrained))
}

pretty <-  c("name","tie", "both", "untrained") #Set the names

ci.dv <- subject.average.ci(hKN,fun=fun,pretty=pretty)
round(ci.dv,2)

#       name  tie both untrained
# 2.5%  0.47 0.48 0.50      0.22
# 50%   0.50 0.51 0.52      0.26
# 97.5% 0.53 0.54 0.55      0.29

#Parameter tests 
# Name vs. untrained
compare.p(hKN,show.plot=TRUE,pnames=c("t0.name","t0.untrained"),pretty=c("name","untrained"),xlab="Average t0")

#        name untrained contrast
# 2.5%  0.469     0.222    0.194
# 50%   0.501     0.258    0.243
# 97.5% 0.533     0.295    0.291
# p.gt.0 
#      1

#Tie vs untrained
compare.p(hKN,show.plot=TRUE,pnames=c("t0.tie","t0.untrained"),pretty=c("tie","untrained"),xlab="Average t0")
#         tie untrained contrast
# 2.5%  0.481     0.222    0.205
# 50%   0.509     0.258    0.250
# 97.5% 0.536     0.295    0.298
# p.gt.0 
#      1

#Both vs. untrained
compare.p(hKN,show.plot=TRUE,pnames=c("t0.both","t0.untrained"),pretty=c("both","untrained"),xlab="Average t0")

#        both untrained contrast
# 2.5%  0.495     0.222    0.219
# 50%   0.524     0.258    0.266
# 97.5% 0.553     0.295    0.314
# p.gt.0 
#      1

```

### 2024-11-29 model_rt_acc.Rmd
added wrangle, model and effects .Rmd files

---
title: "model_rt_acc"
author: "Sam & Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file builds Bayesian regression models using brms in order to analyses the manifest measures (accuracy and RT).

# load libraries #

```{r load-pkg}
pkg <- c("tidyverse", "RColorBrewer", "patchwork", "brms", "tidybayes", 
         "ggdist", "future", "bayesplot", "cmdstanr", "parallel", "rstan")

lapply(pkg, library, character.only = TRUE)
```

# plot settings #

theme settings for ggplot

```{r, eval = F}
theme_set(
  theme_bw() +
    theme(text = element_text(size = 18, face = "bold"), 
          title = element_text(size = 18, face = "bold"),
          legend.position = "bottom")
)

## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)
```

# package settings #

```{r}
options(brms.backend = "cmdstanr",
        mc.cores = parallel::detectCores(),
        future.fork.enable = TRUE,
        future.rng.onMisuse = "ignore") ## automatically set in RStudio

rstan_options(auto_write = TRUE)

supportsMulticore()

detectCores()
```

# 1. load the data #

accuracy data

```{r}
data_acc <- read_csv("data/processed/data_acc.csv") %>%
  mutate(PID = factor(PID),
         GROUP = factor(GROUP,
                        levels = c("untrained", "name", "tie", "both")))
head(data_acc)
glimpse(data_acc)
```

rt data

```{r}
data_rt <- read_csv("data/processed/data_rt.csv") %>%
  mutate(PID = factor(PID),
         GROUP = factor(GROUP,
                        levels = c("untrained", "name", "tie", "both")))
head(data_rt)
glimpse(data_rt)
```

# 2. load some models (as necessary) #

you will only need to load models if you've already created them and you want to take another look at them.

```{r}
# b0.1 <- readRDS("models/manifest/b0.1.rds")
# b0.2 <- readRDS("models/manifest/b0.2.rds")
# b0.3 <- readRDS("models/manifest/b0.3.rds")
# b1 <- readRDS("models/manifest/b1.rds")
# 
# ab0.1 <- readRDS("models/manifest/ab0.1.rds")
# ab0.2 <- readRDS("models/manifest/ab0.2.rds")
# ab1 <- readRDS("models/manifest/ab1.rds")
```

# 3. take a quick look at the lowest RT per person and on average across the group #

This is useful to get a feel for the ndt parameter

```{r}
pid_min <- data_rt %>% 
  group_by(PID) %>%
  summarise(min = min(RT), 
            avg = mean(RT))
pid_min

group_min <- pid_min %>% 
  summarise(min_avg = mean(min), 
            avg = mean(avg))
group_min
```

# 4. build some models #

## A note on priors for shifted log normal models ##

I think the ndt prior changes once it moves from a 'family specific parameter' to a population-level effect. In the former I think it is specified in different units to the latter - in the latter it is specified in log units. Short story is as follows: if you specify ndt in the wrong units, the model will scream and kick up a fuss. It matters if the prior is:

- class = 'ndt'
or
- class = 'Intercept', dpar = "ndt" (e.g., a distributional model, I think)

the latter prior is specified in log units (if I am following correctly).

Also, it seems sensible to keep the rt dv in ms. I think in log normal models, brms/stan freaks out when it is in seconds and log units because you get crazy negative initial starting numbers (inits) too easily and problems arise and no sampling is done.

## rt models ##

build some reaction time models first

### Model b0.1 - intercepts only model ###

formula

```{r}
formula = bf(RT ~ 1)
```

check the priors available

```{r}
get_prior(formula,
          data = data_rt, family = shifted_lognormal())
```

set priors

```{r}
priors = c(
  set_prior('normal(6.68, 0.5)', class = 'Intercept'),  # around 800ms
  set_prior('normal(5.99, 0.5)', class = 'ndt'),  # around 400ms
  # set_prior('normal(0, 0.5)', class = 'b'),
  # set_prior('normal(0, 0.5)', class = 'sd'), # variation across pID (in future models)
  # set_prior('normal(0, 0.5)', class = 'sd', dpar='ndt'),
  set_prior('normal(0, 0.5)', class = 'sigma') # SD of individual rts in
  # set_prior("lkj(2)", class = "cor") # correlation between varying effects log-units
)
```

build the model

```{r}
plan(multicore)
b0.1 <- brm(formula = formula,
        data = data_rt, family = shifted_lognormal(),
        prior = priors,
        iter = 2000, warmup = 1000, cores = 8, chains = 4,
        save_pars = save_pars(all=TRUE),
        seed = 123,
        file = "models/manifest/b0.1")
summary(b0.1)
```

pp_checks

```{r}
ppb0.1 <- pp_check(b0.1, ndraws = 100)
ppb0.1

pmed0.1 <- pp_check(b0.1, type = "stat", stat = 'median', ndraws = 100)
pmed0.1
```

### Model b0.2 - intercepts only model with variation by pid ###

formula

```{r}
formula = bf(RT ~ 1 +
               (1 | PID))
```

check the priors available

```{r}
get_prior(formula,
          data = data_rt, family = shifted_lognormal())
```

set priors

```{r}
priors = c(
  set_prior('normal(6.68, 0.5)', class = 'Intercept'),  # around 800ms
  set_prior('normal(5.99, 0.5)', class = 'ndt'),  # around 400ms
  # set_prior('normal(0, 0.05)', class = 'b'),
  set_prior('normal(0, 0.5)', class = 'sd'), # variation across pID (in future models)
  # set_prior('normal(0, 0.5)', class = 'sd', dpar='ndt'),
  set_prior('normal(0, 0.5)', class = 'sigma') # SD of individual rts in
  # set_prior("lkj(2)", class = "cor") # correlation between varying effects log-units
)
```

build the model

```{r}
plan(multicore)
b0.2 <- brm(formula = formula,
        data = data_rt, family = shifted_lognormal(),
        prior = priors,
        iter = 4000, warmup = 1000, cores = 8, chains = 4,
        save_pars = save_pars(all=TRUE),
        seed = 123,
        file = "models/manifest/b0.2")
summary(b0.2)
```

pp_checks

```{r}
ppb0.2 <- pp_check(b0.2, ndraws = 100)
ppb0.2

pmed0.2 <- pp_check(b0.2, type = "stat", stat = 'median', ndraws = 100)
pmed0.2
```

### Model b0.3 - b0.2 plus variation by pid in ndt ###

formula

```{r}
formula = bf(RT ~ 1 +
               (1 | PID),
               ndt ~ (1 | PID))
```

check the priors available

```{r}
get_prior(formula,
          data = data_rt, family = shifted_lognormal())
```

set priors

```{r}
priors = c(
  set_prior('normal(6.68, 0.5)', class = 'Intercept'),  # around 800ms
  set_prior('normal(5.99, 0.5)', class = 'Intercept', dpar = 'ndt'),  # around 400ms
  # set_prior('normal(0, 0.05)', class = 'b'),
  set_prior('normal(0, 0.5)', class = 'sd'), # variation across pID (in future models)
  set_prior('normal(0, 0.5)', class = 'sd', dpar='ndt'),
  set_prior('normal(0, 0.5)', class = 'sigma') # SD of individual rts in
  # set_prior("lkj(2)", class = "cor") # correlation between varying effects log-units
)
```

build the model

```{r}
plan(multicore)
b0.3 <- brm(formula = formula,
        data = data_rt, family = shifted_lognormal(),
        prior = priors,
        iter = 4000, warmup = 1000, cores = 8, chains = 4,
        save_pars = save_pars(all=TRUE),
        seed = 123,
        file = "models/manifest/b0.3")
summary(b0.3)
```

pp_checks

```{r}
ppb0.3 <- pp_check(b0.3, ndraws = 100)
ppb0.3

pmed0.3 <- pp_check(b0.3, type = "stat", stat = 'median', ndraws = 100)
pmed0.3
```

### model b1 - add cue GROUP (training condition) as a predictor ###

Note - this includes GROUP (training condition) as a fixed / population effect, as well as a varying effect by pid.

formula

```{r}
formula = bf(RT ~ 1 + GROUP +
             (1 + GROUP | PID),
             ndt ~ (1 | PID))
```

check the priors available.

```{r}
get_prior(formula,
          data = data_rt, family = shifted_lognormal())
```

set priors

```{r}
priors = c(
  set_prior('normal(6.68, 0.5)', class = 'Intercept'),  # around 800ms
  set_prior('normal(5.99, 0.5)', class = 'Intercept', dpar = "ndt"),  # around 500ms
  set_prior('normal(0, 0.5)', class = 'b'),
  set_prior('normal(0, 0.5)', class = 'sd'), # variation across pID 
  set_prior('normal(0, 0.5)', class = 'sd', dpar='ndt'),
  set_prior('normal(0, 0.5)', class = 'sigma'), # SD of individual rts in
  set_prior("lkj(2)", class = "cor") # correlation between varying effects log-units
)
```

build the model

```{r}
plan(multicore)
b1 <- brm(formula = formula,
        data = data_rt, family = shifted_lognormal(),
        prior = priors,
        iter = 6000, warmup = 2000, cores = 8, chains = 4,
        control = list(adapt_delta = 0.99, max_treedepth = 15),
        save_pars = save_pars(all=TRUE),
        seed = 123,
        init = 0.1,
        file = "models/manifest/b1")
summary(b1)
```

Plot

```{r}
# p1 = plot(conditional_effects(b1), plot=FALSE)
# 
# wrap_plots(p1)
```

pp_checks

```{r}
ppb1 <- pp_check(b1, ndraws = 100)
ppb1

pmedb1 <- pp_check(b1, type = "stat", stat = 'median', ndraws = 100)
pmedb1
```

## accuracy models ##

Ok, so my thinking is that accuracy should be modelled as a Bernoulli distribution. Bernoulli is a special case of the binomial when N=1 i.e., trials = 1. As these data are being modelled as trial-level data, then each trial is modelled as a Bernoulli. It is identical (I think) in brms to do a binomial with trials = 1. I guess this would be different if we were using aggregate data e.g., data aggregated over conditions, for example. In which case, N would be > 1 and the number correct could be a lot more than 0/1.

prepend 'a' to model names to denote accuracy

### model ab0.1 - intercepts only model ###

formula

```{r}
formula = bf(ACC ~ 1)
```

check the priors available

```{r}
get_prior(formula,
          data = data_acc, family = bernoulli(link = "logit"))
```

set priors

```{r}
priors = c(
  set_prior('normal(0, 1)', class = 'Intercept')  # 
)
```

build the model

```{r}
plan(multicore)
ab0.1 <- brm(formula = formula,
        data = data_acc, family = bernoulli(link = "logit"),
        prior = priors,
        iter = 4000, warmup = 1000, cores = 8, chains = 4,
        save_pars = save_pars(all=TRUE),
        seed = 123,
        file = "models/manifest/ab0.1")
summary(ab0.1)
```

pp_checks

```{r}
ppab0.1 <- pp_check(ab0.1, ndraws = 100)
ppab0.1
```

### model ab0.2 - intercepts only model with variation by pid ###

formula

```{r}
formula = bf(ACC ~ 1 +
               (1 | PID))
```

check the priors available

```{r}
get_prior(formula,
          data = data_acc, family = bernoulli(link = "logit"))
```

set priors

```{r}
priors = c(
  set_prior('normal(0, 1)', class = 'Intercept'),
  set_prior('normal(0, 0.5)', class = 'sd')
)
```

build the model

```{r}
plan(multicore)
ab0.2 <- brm(formula = formula,
        data = data_acc, family = bernoulli(link = "logit"),
        prior = priors,
        iter = 4000, warmup = 1000, cores = 8, chains = 4,
        save_pars = save_pars(all=TRUE),
        seed = 123,
        file = "models/manifest/ab0.2")
summary(ab0.2)
```

pp_checks

```{r}
ppab0.2 <- pp_check(ab0.2, ndraws = 100)
ppab0.2
```

### model ab1 - add GROUP (training condition) as a predictor ###

Note - this includes group (training type) as a fixed / population effect, as well as a varying effect by pid

formula

```{r}
formula = bf(ACC ~ 1 + GROUP +
             (1 + GROUP | PID))
```

check the priors available

```{r}
get_prior(formula,
          data = data_acc, family = bernoulli(link = "logit"))
```

set priors

```{r}
priors = c(
  set_prior('normal(0, 1)', class = 'Intercept'),
  set_prior('normal(0, 0.5)', class = 'sd'),
  set_prior('normal(0, 0.5)', class = 'b'),
  set_prior("lkj(2)", class = "cor")
)
```

build the model

```{r}
plan(multicore)
ab1 <- brm(formula = formula,
        data = data_acc, family = bernoulli(link = "logit"),
        prior = priors,
        iter = 4000, warmup = 1000, cores = 8, chains = 4,
        save_pars = save_pars(all=TRUE),
        seed = 123,
        file = "models/manifest/ab1")
summary(ab1)
```

pp_checks

```{r}
ppab1 <- pp_check(ab1, ndraws = 100)
ppab1
```

# 5. model diagnostics #

take a quick look at model diagnostics for the full rt and acc models

## rt model ##

### look at the chains ###

Here we visualise if the chains mixed reasonably well. We do this to see if there are any alarming patterns of non-mixing. You should see nicely overlapping caterpillar plots if all is well. This is only for the full model as it is the most complex, we would expect the less complex models to behave if this one behaves ok.

full rt model

```{r}
# this adds the chains from model b1 and creates a posterior samples dataframe called post
post_b1 <- as_draws_df(b1)
head(post_b1)

## here I only focus on the chains for the key variables of interest, but one can easily visualise all the variables if one wishes. Although you'll need a lot of separate figures...

post_b1 <- post_b1 %>%
  select(contains(c("b_", "sd_", ".chain"))) %>% # here I select fixed effects and sds. 
  mutate(chain = .chain)

# now we plot them and save them as necessary
p_chains1 <- post_b1 %>%
  mcmc_trace(facet_args = list(ncol = 4)) +
  scale_x_continuous(breaks = c(0, 4000)) + # if you have 4000 post warm-up samples per chain
  theme_bw() +
  theme(legend.position = "bottom")
p_chains1
# save it
ggsave ("figures/manifest/b1_chains.jpeg",
        width = 8, height = 6)
```

chains look good

### other diagnostics ###

```{r}
b1_neff <- mcmc_plot(b1, type = "neff")
b1_neff

b1_rhat <- mcmc_plot(b1, type = "rhat")
b1_rhat

# this creates a combined plot
b1_diag <- b1_neff / b1_rhat 
b1_diag

ggsave("figures/manifest/b1_diag.jpeg",
       width = 8, height = 6)
```

## accuracy model ##

### look at the chains ###

```{r}
# this adds the chains from model ab1 and creates a posterior samples dataframe called post
post_ab1 <- as_draws_df(ab1)
head(post_ab1)

## here I only focus on the chains for the key variables of interest, but one can easily visualise all the variables if one wishes. Although you'll need a lot of separate figures...

post_ab1 <- post_ab1 %>%
  select(contains(c("b_", "sd_", ".chain"))) %>% # here I select fixed effects and sds. 
  mutate(chain = .chain)

# now we plot them and save them as necessary
p_chains2 <- post_ab1 %>%
  mcmc_trace(facet_args = list(ncol = 3)) +
  scale_x_continuous(breaks = c(0, 3000)) + # if you have 4000 post warm-up samples per chain
  theme_bw() +
  theme(legend.position = "bottom")
p_chains2
# save it
ggsave ("figures/manifest/ab1_chains.jpeg",
        width = 8, height = 6)
```

chains look good

### other diagnostics ###

```{r}
ab1_neff <- mcmc_plot(ab1, type = "neff")
ab1_neff

ab1_rhat <- mcmc_plot(ab1, type = "rhat")
ab1_rhat

# this creates a combined plot
ab1_diag <- ab1_neff / ab1_rhat 
ab1_diag

ggsave("figures/manifest/ab1_diag.jpeg",
       width = 8, height = 6)
```

### 2024-11-29 wrangle.Rmd
added wrangle, model and effects .Rmd files

---
title: "wrangle"
author: "Sam & Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the main data wrangling file for the analysis of knots data from Cross et al. (2012).

This script loads the processed data, wrangles the data, makes summary plots and writes out dataframes that are appropriate for the different types of analyses that will follow in the modelling scripts.

# load libraries #

```{r load-pkg}
pkg <- c("tidyverse", "RColorBrewer", "patchwork")

lapply(pkg, library, character.only = TRUE)
```

# plot settings #

theme settings for ggplot

```{r, eval = F}
theme_set(
  theme_bw() +
    theme(text = element_text(size = 18, face = "bold"), 
          title = element_text(size = 18, face = "bold"),
          legend.position = "bottom")
)

## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)
```

# 1. load the data #

this is the processed data for day 5 session 2

```{r}
raw <- read_csv("data/processed/day5_post_knots_data.csv")
head(raw)
```

check only day 5, session 2

```{r}
raw %>%
  distinct(DAY, SESSION)
```

# 2. do some wrangling #

select relevant variables.
create an accuracy variable.
rename group.
create factors.

```{r}
data <- raw %>% 
  select(PID, GROUP, MATCH, RESPONSE, RT) %>% 
  mutate(ACC = if_else(MATCH == RESPONSE, 1, 0)) %>% 
  mutate(GROUP = case_when(
    GROUP == 1 ~ "name",
    GROUP == 2 ~ "tie",
    GROUP == 3 ~ "both",
    .default = "untrained")) %>% 
  mutate(PID = factor(PID),
         GROUP = factor(GROUP,
                        levels = c("untrained", "name", "tie", "both")))
head(data)
glimpse(data)
```

```{r}
# Relevant variables as follows:
# PID = ID each participants should be n = 18 (with day 5, session 2 data)
# RESPONSE = Whether the participant selects a match or not? (1 = match, 2 = mismatch)
# RT = Response times in ms
# GROUP = 1-4 (name, tie, both, untrained)
# MATCH = Whether they match or not (1 = match and 2 = mismatch)
# ACC = correct = 1, incorrect = 0
```

create a reaction time dataframe

```{r}
data_rt <- data %>% 
  filter(ACC==1)
data_rt
```

# 3. take a quick look at the data #

trial count per PID

```{r}
trials_pid <- data %>%
  group_by(PID) %>%
  tally() %>% 
  arrange(n) # take a look at the lowest trial count
head(trials_pid)
```

per condition

```{r}
trials_cond <- data %>%
  group_by(GROUP) %>%
  tally() %>% 
  arrange(n) # take a look at the lowest trial count
head(trials_cond)
```

per PID and condition

```{r}
trials_pid_cond <- data %>%
  group_by(PID, GROUP) %>%
  tally() %>% 
  arrange(n) 
head(trials_pid_cond)
```

and print it

```{r}
trials_pid_cond %>% 
  print(n=Inf)
```

# 4. create summary data #

## accuracy ##

at the pid level

```{r}
data_s_pid <- data %>% 
  group_by(PID, GROUP) %>% 
  summarise(sum_acc = sum(ACC), 
            mean_acc = mean(ACC, na.rm = TRUE) * 100, 
            sd_acc = sd(ACC, na.rm = TRUE) * 100)
head(data_s_pid)
```

at the group level

```{r}
data_s_g <- data %>% 
  group_by(GROUP) %>% 
  summarise(n=length(unique(PID)),
            sum_acc = sum(ACC), 
            mean_acc = mean(ACC, na.rm = TRUE) * 100, 
            sd_acc = sd(ACC, na.rm = TRUE) * 100, 
            sem_acc = (sd_acc/sqrt(n)))
data_s_g
```

## reaction time ##

at the pid level

```{r}
data_s_rt_pid <- data_rt %>% 
  group_by(PID, GROUP) %>%
  summarise(mean_rt = mean(RT, na.rm = TRUE), 
            sd_rt = sd(RT, na.rm = TRUE))
head(data_s_rt_pid)
```

at the group level

```{r}
data_s_rt_g <- data_rt %>% 
  group_by(GROUP) %>%
  summarise(n=length(unique(PID)),
            mean_rt = mean(RT, na.rm = TRUE), 
            sd_rt = sd(RT, na.rm = TRUE), 
            sem_rt = (sd_rt/sqrt(n)))
data_s_rt_g
```

# 5. make some plots #

plot accuracy

```{r}
p5.1 <- ggplot(data_s_pid, aes(x = GROUP, y = mean_acc, 
                               fill = GROUP, colour = GROUP)) +
  geom_jitter(position=position_jitterdodge(dodge.width =1), 
              size = 2.5, colour="grey") +
  geom_violin(alpha = 0.5, position=pd2) +
  geom_errorbar(data = data_s_g, aes(ymin=mean_acc-sem_acc, ymax=mean_acc+sem_acc), 
                width=.3, size =0.5, colour = "black", position=pd2) +
  geom_point(data = data_s_g, colour = "black", position=pd2, size =4) +
  geom_line(data=data_s_g, group=1, colour = "black") +
  xlab("Training Condition") + 
  ylab('Percentage Correct') + 
  scale_fill_brewer(palette = "Dark2") +
  scale_colour_brewer(palette = "Dark2") +
  theme(legend.position = "none")
p5.1
```

plot rt

```{r}
p5.2 <- ggplot(data_s_rt_pid, aes(x = GROUP, y = mean_rt, 
                               fill = GROUP, colour = GROUP)) +
  geom_jitter(position=position_jitterdodge(dodge.width =1), 
              size = 2.5, colour="grey") +
  geom_violin(alpha = 0.5, position=pd2) +
  geom_errorbar(data = data_s_rt_g, aes(ymin=mean_rt-sem_rt,
                                        ymax=mean_rt+sem_rt), 
                width=.3, size =0.5, colour = "black", position=pd2) +
  geom_point(data = data_s_rt_g, colour = "black", position=pd2, size =4) +
  geom_line(data=data_s_rt_g, group=1, colour = "black") +
  xlab("Training Condition") + 
  ylab('Mean Reaction Time (ms)') + 
  scale_fill_brewer(palette = "Dark2") +
  scale_colour_brewer(palette = "Dark2") +
  theme(legend.position = "none")
p5.2
```

plot together

```{r}
p5.3 <- (p5.1 | p5.2) +
  plot_annotation(tag_levels = 'A')
p5.3

ggsave("figures/descriptive/violin_acc_rt.jpeg",
       width = 10, height = 6, dpi = 800)
```

# 6. write out the data #

## data for plotting and modelling via brms ##

this is the data for acc and rt labelled as it is in plots
It can be used for modelling in the manifest analysis of rt and acc separately

```{r}
write_csv(data, "data/processed/data_acc.csv")
write_csv(data_rt, "data/processed/data_rt.csv")
```

## data for use in LBA modelling ##

this is for modelling with DMC software when using an LBA model.
DMC has specific rules about how the data are structured.

Rules for data to be used in dmc

1) Make sure you have an "s" column identifying the data for each subject that is a factor
2) Follow that by columns specifying the factors in your design. Again each must be a factor
3) The second last column give the response (again a factor)
4) The last columns is called RT, make sure the unit is seconds.

And we can remove the ACC column as DMC makes the match between Stimulus and Response.

```{r}
data_lba <- data %>%
  rename(s = PID, S = MATCH, R = RESPONSE) %>% 
  mutate(RT = RT/1000,
         S = factor(S),
         R = factor(R)) %>%
  select(s, GROUP, S, R, RT) %>% 
  as.data.frame()
head(data_lba)

## technically, since we are saving out a .csv file then reading it in when we get to the model script the factors and data frame (vs tibble) are not necessary here as they will need to be re-done when they are read in later. But I think it is probably good practice to get this in the format that is later required.
```

save it as a .csv file

```{r}
write_csv(data_lba, "data/processed/data_lba.csv")
```

### 2024-11-29 manuscript/manuscript.Rmd
added the updated figures to the manuscript

@@
 ```{r accuracy-rt-plot, fig.cap = "(ref:accuracy-rt-caption)"}
-knitr::include_graphics("../figures/from_file/acc_rt.png")
+knitr::include_graphics("../figures/descriptive/violin_acc_rt.jpeg")
 ```
@@
 ```{r threshold-plot, fig.cap = "(ref:threshold-caption)"}
-knitr::include_graphics("../figures/from_file/thresholds.png")
+knitr::include_graphics("../figures/ea/thresholds.jpeg")
 ```
@@
 ```{r drift-rate-plot, fig.cap = "(ref:drift-rate-caption)"}
-knitr::include_graphics("../figures/from_file/drift_rate.png")
+knitr::include_graphics("../figures/ea/drift_rate.jpeg")
 ```
@@
 ```{r ndt-plot, fig.cap = "(ref:ndt-caption)"}
-knitr::include_graphics("../figures/from_file/ndt.png")
+knitr::include_graphics("../figures/ea/ndt.jpeg")
 ```
@@
 ```{r lba-summary-plot, fig.cap = "(ref:lba-summary-caption)"}
-knitr::include_graphics("../figures/lba_summary.jpeg")
+knitr::include_graphics("../figures/ea/lba_summary.jpeg")
 ```

### 2024-11-29 manuscript/manuscript.tex
added the updated figures to the manuscript

@@
 \makeatother
-\keywords{evidence accumulation modelling, training, learning, action, naming, cognitive mechanisms, plasticity\newline\indent Word count: 6679}
+\keywords{evidence accumulation modelling, training, learning, action, naming, cognitive mechanisms, plasticity\newline\indent Word count: 6703}
 \usepackage{lineno}
@@
 
-{\centering \includegraphics[height=0.67\textheight,]{../figures/from_file/acc_rt}
+{\centering \includegraphics[height=0.67\textheight,]{../figures/descriptive/violin_acc_rt}
 
@@
 
-{\centering \includegraphics[height=0.67\textheight,]{../figures/from_file/thresholds}
+{\centering \includegraphics[height=0.67\textheight,]{../figures/ea/thresholds}
 
@@
 
-{\centering \includegraphics[height=0.67\textheight,]{../figures/from_file/drift_rate}
+{\centering \includegraphics[height=0.67\textheight,]{../figures/ea/drift_rate}
 
@@
 
-{\centering \includegraphics[height=0.67\textheight,]{../figures/from_file/ndt}
+{\centering \includegraphics[height=0.67\textheight,]{../figures/ea/ndt}
 
@@
 
-{\centering \includegraphics[height=0.67\textheight,]{../figures/lba_summary}
+{\centering \includegraphics[height=0.67\textheight,]{../figures/ea/lba_summary}
 

### 2024-11-29 manuscript/manuscript.Rmd
updated manuscript

@@
 keywords          : "evidence accumulation modelling, training, learning, action, naming, cognitive mechanisms, plasticity"
-wordcount         : "6703"
+wordcount         : "6698"
 bibliography      : ["references.bib", "r-references.bib"]
@@
 All other aspects of the pre-registration were unchanged.
-In addition, all of the analysis code used in this paper have been made available on the open science framework ([https://osf.io/ea6gk/](https://osf.io/ea6gk/).
+In addition, the analysis code used in this paper is available online, and the manuscript was written in R using the papaja() package [@R-papaja], which means it is  computationally reproducible.
+The code and manuscript are available via GitHub ([https://github.com/rich-ramsey/knot_dmc](https://github.com/rich-ramsey/knot_dmc)).
 Given that the data were collected several years before 2012, it was not yet routine to request explicit consent to share data publicly.
 Therefore, the raw data are only available from the authors upon request.
-Since the current manuscript was written in R using the papaja() package [@R-papaja], it is also computationally reproducible and available via GitHub ([https://github.com/rich-ramsey/knot_dmc](https://github.com/rich-ramsey/knot_dmc)).
 

### 2024-11-29 manuscript/manuscript.tex
updated manuscript

@@
 \makeatother
-\keywords{evidence accumulation modelling, training, learning, action, naming, cognitive mechanisms, plasticity\newline\indent Word count: 6703}
+\keywords{evidence accumulation modelling, training, learning, action, naming, cognitive mechanisms, plasticity\newline\indent Word count: 6698}
 \usepackage{lineno}
@@
 All other aspects of the pre-registration were unchanged.
-In addition, all of the analysis code used in this paper have been made available on the open science framework (\url{https://osf.io/ea6gk/}.
+In addition, the analysis code used in this paper is available online, and the manuscript was written in R using the papaja() package (Aust \& Barth, 2023), which means it is computationally reproducible.
+The code and manuscript are available via GitHub (\url{https://github.com/rich-ramsey/knot_dmc}).
 Given that the data were collected several years before 2012, it was not yet routine to request explicit consent to share data publicly.
 Therefore, the raw data are only available from the authors upon request.
-Since the current manuscript was written in R using the papaja() package (Aust \& Barth, 2023), it is also computationally reproducible and available via GitHub (\url{https://github.com/rich-ramsey/knot_dmc}).
 

### 2024-12-06 effects_rt_acc.Rmd
added a few new plots and tables for supps

@@
          "ggdist", "future", "bayesplot", "parallel", "here", "tinytable",
-         "webshot2")
+         "webshot2", "rstan")
 
@@
   stat_halfeye(alpha=0.7) +
-  labs(title = "fixed effects of condition",
+  labs(#title = "fixed effects of condition",
        x = "Log(RT)", y = NULL) +
@@
 
-ggsave ("figures/manifest/b1_fixef.jpeg")
+# ggsave ("figures/manifest/b1_fixef.jpeg",
+#         width = 8, height = 6, dpi = 800)
+```
+
+### make a table of fixed effects ###
+
+```{r}
+b1_fixef_tab <- tidy_fixed %>%
+  select(term, value) %>% 
+  group_by(term) %>% 
+  median_qi(value) %>% 
+  mutate(dv = "reaction time") %>% 
+  select(dv, term, value, .lower, .upper) 
+b1_fixef_tab
 ```
@@
 
-ggsave ("figures/manifest/b1_varying_pid.jpeg")
+ggsave ("figures/manifest/b1_varying_pid.jpeg",
+        width = 8, height = 6, dpi = 800)
 ```
@@
 
-ggsave ("figures/manifest/b1_varyvals.jpeg")
+ggsave ("figures/manifest/b1_varyvals.jpeg",
+        width = 8, height = 6, dpi = 800)
 ```
@@
 ```{r}
-post <- as_draws_df(ab1) %>% #
+ab1_post <- as_draws_df(ab1) %>% #
   select(-lp__) %>% 
@@
 
-post_summary <- posterior_summary(ab1, robust = TRUE)
+ab1_post_summary <- posterior_summary(ab1, robust = TRUE)
 
 # all fixed effects
-post_qi_b <- post %>%
+ab1_post_qi_b <- ab1_post %>%
   select(starts_with("b_")) %>% 
@@
   median_qi(value)
-head(post_qi_b)
+head(ab1_post_qi_b)
 
 # average varying effects - SD
-post_qi_sd <- post %>%
+ab1_post_qi_sd <- ab1_post %>%
   select(starts_with("sd_")) %>% 
@@
   median_qi(value)
-head(post_qi_sd)
+head(ab1_post_qi_sd)
 
@@
 # I take this to be 18 pts x 4 terms (intercept, 3 levels of group) = 72 in total
-vary_vals <- post %>%
+ab1_vary_vals <- ab1_post %>%
   select(starts_with("r_")) %>% 
@@
   median_qi(value)
-head(vary_vals)
+head(ab1_vary_vals)
 ```
@@
 ## Is this the right way to label the interaction?
-tidy_fixed <- post %>% 
+ab1_tidy_fixed <- ab1_post %>% 
   select(starts_with("b_")) %>% # select and rename in simpler labels.
@@
          term = factor(term, levels=unique(term)))
-head(tidy_fixed)
-tail(tidy_fixed)
+head(ab1_tidy_fixed)
+tail(ab1_tidy_fixed)
 
 ## check labels
-check.labels <- tidy_fixed %>% 
+check.labels <- ab1_tidy_fixed %>% 
   group_by(key, term) %>% 
@@
 # remove intercepts as they are on a different scale and make it difficult to plot
-tidy_fixed <- tidy_fixed %>%
+ab1_tidy_fixed <- ab1_tidy_fixed %>%
   filter(!term %in% c("intercept"))
-head(tidy_fixed)
+head(ab1_tidy_fixed)
 
-check.labels <- tidy_fixed %>% 
+check.labels <- ab1_tidy_fixed %>% 
   group_by(key, term) %>% 
@@
 
-p_tidy_fixed <- ggplot(tidy_fixed, aes(x = value, y = fct_rev(term), 
+p_tidy_fixed_ab1 <- ggplot(ab1_tidy_fixed, aes(x = value, y = fct_rev(term), 
                                        fill=term)) +  
@@
   stat_halfeye(alpha=0.7) +
-  labs(title = "fixed effects of condition",
+  labs(#title = "fixed effects of condition",
        x = "Accuracy", y = NULL) +
   scale_fill_brewer(palette = "Dark2")
-p_tidy_fixed
+p_tidy_fixed_ab1
 
-ggsave ("figures/manifest/ab1_fixef.jpeg")
+# ggsave ("figures/manifest/ab1_fixef.jpeg",
+#         width = 8, height = 6, dpi = 800)
+```
+
+### make a table of fixed effects ###
+
+```{r}
+ab1_fixef_tab <- ab1_tidy_fixed %>%
+  select(term, value) %>% 
+  group_by(term) %>% 
+  median_qi(value) %>% 
+  mutate(dv = "accuracy") %>% 
+  select(dv, term, value, .lower, .upper) 
+ab1_fixef_tab
 ```
@@
 ## random effects of interest, including item, as well as participant and effects across pts
-tidy_varying <- post %>% 
+ab1_tidy_varying <- ab1_post %>% 
   select(contains("sd_")) %>% 
@@
                                       "name", "tie", "both")))
-head(tidy_varying)
-tail(tidy_varying)
-str(tidy_varying)
+head(ab1_tidy_varying)
+tail(ab1_tidy_varying)
+str(ab1_tidy_varying)
 
-check.varying <- tidy_varying %>% 
+check.varying <- ab1_tidy_varying %>% 
   group_by(key, term) %>% 
@@
 
-p_tidy_varying_pid <- ggplot(tidy_varying, aes(x = value, 
+p_tidy_varying_pid_ab1 <- ggplot(ab1_tidy_varying, aes(x = value, 
                                                y = fct_rev(term))) +  
@@
   scale_x_continuous(breaks=seq(0,1,0.1))
-p_tidy_varying_pid
+p_tidy_varying_pid_ab1
 
-ggsave ("figures/manifest/ab1_varying_pid.jpeg")
+ggsave ("figures/manifest/ab1_varying_pid.jpeg",
+        width = 8, height = 6, dpi = 800)
 ```
@@
 # participant level
-vary_pt <- post_summary %>%
+ab1_vary_pt <- ab1_post_summary %>%
   data.frame() %>% 
@@
          outlier = factor(outlier, levels = c("no", "yes")))
-head(vary_pt)
+head(ab1_vary_pt)
 ```
@@
 ```{r}
-p_tidy_varyvals <- ggplot(vary_pt, aes(x=rank, y=Estimate,
+p_tidy_varyvals_ab1 <- ggplot(ab1_vary_pt, aes(x=rank, y=Estimate,
                                            colour=outlier))+
@@
   theme(legend.position = "none")
-p_tidy_varyvals
+p_tidy_varyvals_ab1
 
-ggsave ("figures/manifest/ab1_varyvals.jpeg")
+ggsave ("figures/manifest/ab1_varyvals.jpeg",
+        width = 8, height = 6, dpi = 800)
 ```
@@
 
-# 3. plot ppreds for RT and Accuracy together #
+# 3. make plots for RT and Accuracy together #
+
+fixed effects
+
+```{r}
+p_fixef <- (p_tidy_fixed_ab1 | p_tidy_fixed) +
+  plot_annotation(title = "Fixed effects of condition for accuracy and RT",
+                  tag_levels = 'A') +
+  plot_layout(guides = 'collect',
+              axes = 'collect')
+p_fixef
+
+ggsave("figures/manifest/fixef.jpeg",
+       width = 10, height = 6, dpi = 800)
+```
+
+posterior predictions
 
@@
 ```
+
+# 4. make a table of fixed effects for rt and accuracy #
+
+```{r}
+fix_tab <- bind_rows(ab1_fixef_tab, b1_fixef_tab) %>% 
+   mutate(across(where(is.double), \(x) round(x, 2)))
+fix_tab
+
+write_csv(fix_tab, "tables/manifest/fixef.csv")
+```

### 2024-12-06 model_lba.Rmd
small typo fix to model loading

@@
 ```{r}
-tmp=load("models/ea/modelKN.RData")
+tmp=load("models/ea/dmKN.RData")
 cores=length(sKN)
@@
 plot.dmc(hKN,hyper=TRUE,layout=c(3,3))
-plot.dmc(hKN,hyper=TRUE,layout=c(4,4),p.prior=pp.prior)
+plot.dmc(hKN,hyper=TRUE,layout=c(3,3),p.prior=pp.prior)
 dev.off()

### 2024-12-06 manuscript/manuscript.Rmd
plot settings update

@@
   theme_bw() +
-    theme(text = element_text(size = 18), 
-          title = element_text(size = 18),
+    theme(text = element_text(size = 18, face = "bold"), 
+          title = element_text(size = 18, face = "bold"),
           legend.position = "bottom")

### 2024-12-06 manuscript/supplementary/supplementary.Rmd
added a supplementary file

---
title             : no
shorttitle        : "Decision models and experience-dependent plasticity"
floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man"
output            : papaja::apa6_pdf
editor_options: 
  chunk_output_type: console
header-includes:
  - \raggedbottom
---

```{r setup, include = FALSE}
pkg <- c("papaja", "citr", "tidyverse", "RColorBrewer", "patchwork")

lapply(pkg, library, character.only = TRUE)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r plot-settings}
## theme settings for ggplot
theme_set(
  theme_bw() +
    theme(text = element_text(size = 18, face = "bold"), 
          title = element_text(size = 18, face = "bold"),
          legend.position = "bottom")
)

## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)
```

```{r global-chunk-settings}
## set the figure options
knitr::opts_chunk$set(fig.pos='H', out.extra = '', out.height = "67%",
                      fig.align = "center") # initial version
```

```{r papaja-terms-settings}
# supp_terms <- getOption("papaja.terms")
# supp_terms$table <- "Supplementary Table"
# supp_terms$figure <- "Supplementary Figure"
# options("papaja.terms" = supp_terms) 
```

# Supplementary Materials #

## Analysis of Observed Variables ##

In addition to our evidence accumulation modelling analysis, we first analysed accuracy and reaction time (RT). Analyses was conducted using a Bayesian estimation approach to multilevel modelling (McElreath, 2020). Specifically, we used the Bayesian modelling package “brms” to run multilevel models in the R (Bürkner, 2017).

Models were built incrementally towards the most complex model. This meant that all fixed and varying effects that the design would permit were included in the full model (Barr et al., 2013). Model 0 for both accuracy and reaction time were intercept only models so that we could compare all subsequent models that included effects of interest to a model without any predictors. The most complex model included an effect of training type (naming, tying, both, untrained). Shifted lognormal model was used to fit reaction time, while accuracy data was fit with a Bernoulli model. Priors were set using a weakly informative approach (see Table 1 for all priors used for modelling) (Gelman, 2006). The formula for the full model (Model 1) used to fit reaction time data is specified below:

$$rt \sim 1 + training type + \\
(1 + training type | pid), \\
ndt \sim (1 | pid)$$

Note: RT = reaction time (ms); training type = training condition (untrained vs. naming vs. tying vs. both); pid = subject/participant identifier; ndt = non-decision time.

The priors we used followed a weakly informative approach and are reported in Supplementary Table 1.

(ref:prior-table-caption) Priors used for models.

(ref:prior-table-note) dpar = distributional parameter; sd = standard deviation; b = fixed effect; cor = correlation; ndt = nondecision time.

```{r prior-table}
prior_acc_table <- tibble(
  Variable = c("Accuracy", NA, NA, NA),
  Prior = c("normal (0,1)", "normal (0,.5)", "normal (0,.5)", "Lkj(2)"),
  Class = c("Intercept", "sd", "b", "cor"),
  dpar = c(NA, "ndt", NA, NA)
)

prior_rt_table <- tibble(
  Variable = c("Reaction time", NA, NA, NA, NA, NA, NA),
  Prior = c("normal (6.68,0.5)", "normal (5.99,0.5)", 
            rep("normal (0,.5)", times =4),
            "Lkj(2)"),
  Class = c("Intercept", "Intercept", "b", "sd", "sd", "sigma", "cor"),
  dpar = c(NA, "ndt", NA, NA, "ndt", NA, NA)
)

prior_table <- bind_rows(prior_acc_table, prior_rt_table) %>% 
   mutate(across(everything(), ~replace_na(.x, "")))

apa_table(
  prior_table,
  caption = "(ref:prior-table-caption)",
  note = "(ref:prior-table-note)"
)
```

There was some evidence for relatively small effects of training type on accuracy (see Supplementary Figure 1A). The posterior distribution for the effect of each training type overlapped with zero, but did have values which fell mainly below or above zero. This suggests that relative to the untrained condition accuracy was lower in both the tying and naming conditions, but slighly higher in the combined condition.

There also appeared to be an effect of training type on RT (see Supplementary Figure 1B). Inspection of the posterior distribution for the fixed effects of training type revealed values which primarily fell below zero. This suggests that relative to knots that received no training, participants responded faster to knots that received naming, tying and both naming and tying training.

(ref:fixef-caption) Fixed Effects for the Most Complex Model for (A) Accuracy and (B) Reaction Time. Points represent the median value of the posterior distribution for that estimate, the thicker line represents 66th percentile, while the thinner line is the 95th percentile of the distribution. The untrained condition was the reference group.

```{r fixef-plot, fig.cap = "(ref:fixef-caption)"}
knitr::include_graphics("../../figures/manifest/fixef.jpeg")
```

## LBA Analysis ##

### Sampling ###

For each model we used three times as many chains were used as model parameters. Sampling was carried out in two steps. First, sampling was carried out separately for individual participants in order to get reasonable start points for hierarchical sampling. The results of this step were then used as starting points for sampling the full hierarchical sample. During the initial burn-in-period there was a probability of .05 that a crossover step was replaced with a migration step. After burn in only crossover steps were used and sampling continued until the proportional scale reduction factor ($\hat{R}$) was less than 1.1 for all parameters, and also the multivariate version was less than 1.1 (Brooks & Gelman, 1998). Hierarchical estimation assumed independent normal population distributions for each model parameter. Population-mean start points were calculated from the mean of the individual-subject posterior medians and population standard deviation from their standard deviations, with each chain getting a slightly different random perturbation of these values. Hierarchical sampling used probability .05 migration steps at both levels of the hierarchy during burn in and only crossover steps thereafter with thinning set at 10 (i.e., only every 10th sample was kept), with sampling continuing until $\hat{R}$ for all parameters at all levels, and the multivariate $\hat{R}$ values, were all less than 1.1. The final set of chains were also inspected visually to confirm convergence.

### Priors ###

Priors were chosen to have little influence on estimation. Priors were normal distributions that were truncated below zero for B, A and sv parameters, and truncated at 0.1s for the t0 parameter (assuming that responses made in less than 0.1s are implausible). The t0 parameter was truncated above by 1s. There were no other truncations, so the v prior was unbounded. The prior mean for B was 1 and for A 0.5. The v parameter for the true accumulator was given a prior mean of 1, while the mismatching accumulator was given a prior mean of 0. The sv parameter for the matching accumulator had a prior mean of 0.5. The t0 parameter had a prior mean of 0.3s. All priors had a standard deviation of 2. Mean parameters of population distributions were assumed to have priors of the same form as for individual estimation, and the standard deviations of hyper parameters were assumed to have exponential distributions with a scale parameter of one. Plots of prior and posterior distributions revealed strong updating (i.e., posteriors dominated priors), making it clear that the prior assumptions had little influence on posterior estimates (see Supplementary Figure 2 for an example of how the priors were updated for hyperparameters).

(ref:prior-post-caption) Prior and Posterior Graphs. Red lines represent priors, while black lines represent posteriors. Only a selection of all the parameters are shown here.

```{r prior-post-plot, fig.cap = "(ref:prior-post-caption)"}
knitr::include_graphics("../../figures/ea/pp.pdf")
```

### Model fit ###

Supplementary Figures 3 display the fits of the LBA model to the data in terms of defective cumulative distribution functions (lines) and 10th, 30th, 50th, 70th and 90th percentiles (points from left to right) averaged over participants. Thick black lines and open points correspond to the data and the think grey lines solid black points to the model prediction averaged over posterior samples. The grey points correspond to percentile predictions for 100 randomly selected sets of posterior parameter samples, so their spread gives an idea of the uncertainty in the model’s predictions. As can be seen from the figure the average fit of the selected LBA model was reasonable.

(ref:model-fit-caption) Cumulative distribution functions for data (thick lines) and fits (line grey lines) of the LBA model. Each panel contains results for both same and different responses at each level of stimulus (match and mismatch) and training type (name, tie, both, untrained). Symbols mark the 10th, 30th, 50th, 70th and 90th percentile (solid for average fits, open for data). Grey points are 500 percentile estimates from fits for random draws from posterior samples; the grey line and black solid points are the average of these 500 fits.

```{r model-fit-plot, fig.cap = "(ref:model-fit-caption)"}
knitr::include_graphics("../../figures/ea/KN_fit.pdf")
```

### 2024-12-06 manuscript/supplementary/supplementary.tex
added a supplementary file

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

\makeatletter
\usepackage{etoolbox}
\patchcmd{\maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\raggedbottom
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdflang={en-EN},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{\phantom{0}}
\date{}

\shorttitle{Decision models and experience-dependent plasticity}

\affiliation{\phantom{0}}

\begin{document}

\section{Supplementary Materials}\label{supplementary-materials}

\subsection{Analysis of Observed Variables}\label{analysis-of-observed-variables}

In addition to our evidence accumulation modelling analysis, we first analysed accuracy and reaction time (RT). Analyses was conducted using a Bayesian estimation approach to multilevel modelling (McElreath, 2020). Specifically, we used the Bayesian modelling package ``brms'' to run multilevel models in the R (Bürkner, 2017).

Models were built incrementally towards the most complex model. This meant that all fixed and varying effects that the design would permit were included in the full model (Barr et al., 2013). Model 0 for both accuracy and reaction time were intercept only models so that we could compare all subsequent models that included effects of interest to a model without any predictors. The most complex model included an effect of training type (naming, tying, both, untrained). Shifted lognormal model was used to fit reaction time, while accuracy data was fit with a Bernoulli model. Priors were set using a weakly informative approach (see Table 1 for all priors used for modelling) (Gelman, 2006). The formula for the full model (Model 1) used to fit reaction time data is specified below:

\[rt \sim 1 + training type + \\
(1 + training type | pid), \\
ndt \sim (1 | pid)\]

Note: RT = reaction time (ms); training type = training condition (untrained vs.~naming vs.~tying vs.~both); pid = subject/participant identifier; ndt = non-decision time.

The priors we used followed a weakly informative approach and are reported in Supplementary Table 1.

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:prior-table}Priors used for models.}

\begin{tabular}{llll}
\toprule
Variable & \multicolumn{1}{c}{Prior} & \multicolumn{1}{c}{Class} & \multicolumn{1}{c}{dpar}\\
\midrule
Accuracy & normal (0,1) & Intercept & \\
 & normal (0,.5) & sd & ndt\\
 & normal (0,.5) & b & \\
 & Lkj(2) & cor & \\
Reaction time & normal (6.68,0.5) & Intercept & \\
 & normal (5.99,0.5) & Intercept & ndt\\
 & normal (0,.5) & b & \\
 & normal (0,.5) & sd & \\
 & normal (0,.5) & sd & ndt\\
 & normal (0,.5) & sigma & \\
 & Lkj(2) & cor & \\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} dpar = distributional parameter; sd = standard deviation; b = fixed effect; cor = correlation; ndt = nondecision time.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

There was some evidence for relatively small effects of training type on accuracy (see Supplementary Figure 1A). The posterior distribution for the effect of each training type overlapped with zero, but did have values which fell mainly below or above zero. This suggests that relative to the untrained condition accuracy was lower in both the tying and naming conditions, but slighly higher in the combined condition.

There also appeared to be an effect of training type on RT (see Supplementary Figure 1B). Inspection of the posterior distribution for the fixed effects of training type revealed values which primarily fell below zero. This suggests that relative to knots that received no training, participants responded faster to knots that received naming, tying and both naming and tying training.

\begin{figure}[H]

{\centering \includegraphics[height=0.67\textheight,]{../../figures/manifest/fixef}

}

\caption{Fixed Effects for the Most Complex Model for (A) Accuracy and (B) Reaction Time. Points represent the median value of the posterior distribution for that estimate, the thicker line represents 66th percentile, while the thinner line is the 95th percentile of the distribution. The untrained condition was the reference group.}\label{fig:fixef-plot}
\end{figure}

\subsection{LBA Analysis}\label{lba-analysis}

\subsubsection{Sampling}\label{sampling}

For each model we used three times as many chains were used as model parameters. Sampling was carried out in two steps. First, sampling was carried out separately for individual participants in order to get reasonable start points for hierarchical sampling. The results of this step were then used as starting points for sampling the full hierarchical sample. During the initial burn-in-period there was a probability of .05 that a crossover step was replaced with a migration step. After burn in only crossover steps were used and sampling continued until the proportional scale reduction factor (\(\hat{R}\)) was less than 1.1 for all parameters, and also the multivariate version was less than 1.1 (Brooks \& Gelman, 1998). Hierarchical estimation assumed independent normal population distributions for each model parameter. Population-mean start points were calculated from the mean of the individual-subject posterior medians and population standard deviation from their standard deviations, with each chain getting a slightly different random perturbation of these values. Hierarchical sampling used probability .05 migration steps at both levels of the hierarchy during burn in and only crossover steps thereafter with thinning set at 10 (i.e., only every 10th sample was kept), with sampling continuing until \(\hat{R}\) for all parameters at all levels, and the multivariate \(\hat{R}\) values, were all less than 1.1. The final set of chains were also inspected visually to confirm convergence.

\subsubsection{Priors}\label{priors}

Priors were chosen to have little influence on estimation. Priors were normal distributions that were truncated below zero for B, A and sv parameters, and truncated at 0.1s for the t0 parameter (assuming that responses made in less than 0.1s are implausible). The t0 parameter was truncated above by 1s. There were no other truncations, so the v prior was unbounded. The prior mean for B was 1 and for A 0.5. The v parameter for the true accumulator was given a prior mean of 1, while the mismatching accumulator was given a prior mean of 0. The sv parameter for the matching accumulator had a prior mean of 0.5. The t0 parameter had a prior mean of 0.3s. All priors had a standard deviation of 2. Mean parameters of population distributions were assumed to have priors of the same form as for individual estimation, and the standard deviations of hyper parameters were assumed to have exponential distributions with a scale parameter of one. Plots of prior and posterior distributions revealed strong updating (i.e., posteriors dominated priors), making it clear that the prior assumptions had little influence on posterior estimates (see Supplementary Figure 2 for an example of how the priors were updated for hyperparameters).

\begin{figure}[H]

{\centering \includegraphics[height=0.67\textheight,]{../../figures/ea/pp}

}

\caption{Prior and Posterior Graphs. Red lines represent priors, while black lines represent posteriors. Only a selection of all the parameters are shown here.}\label{fig:prior-post-plot}
\end{figure}

\subsubsection{Model fit}\label{model-fit}

Supplementary Figures 3 display the fits of the LBA model to the data in terms of defective cumulative distribution functions (lines) and 10th, 30th, 50th, 70th and 90th percentiles (points from left to right) averaged over participants. Thick black lines and open points correspond to the data and the think grey lines solid black points to the model prediction averaged over posterior samples. The grey points correspond to percentile predictions for 100 randomly selected sets of posterior parameter samples, so their spread gives an idea of the uncertainty in the model's predictions. As can be seen from the figure the average fit of the selected LBA model was reasonable.

\begin{figure}[H]

{\centering \includegraphics[height=0.67\textheight,]{../../figures/ea/KN_fit}

}

\caption{Cumulative distribution functions for data (thick lines) and fits (line grey lines) of the LBA model. Each panel contains results for both same and different responses at each level of stimulus (match and mismatch) and training type (name, tie, both, untrained). Symbols mark the 10th, 30th, 50th, 70th and 90th percentile (solid for average fits, open for data). Grey points are 500 percentile estimates from fits for random draws from posterior samples; the grey line and black solid points are the average of these 500 fits.}\label{fig:model-fit-plot}
\end{figure}

\end{document}

### 2024-12-06 manuscript/supplementary/supplementary.Rmd
minor tweaks

@@
 Shifted lognormal model was used to fit reaction time, while accuracy data was fit with a Bernoulli model.
-Priors were set using a weakly informative approach (see Table 1 for all priors used for modelling) (Gelman, 2006).
+Priors were set using a weakly informative approach (see Supplementary Table 1 for all priors used for modelling) (Gelman, 2006).
 The formula for the full model (Model 1) used to fit reaction time data is specified below:
@@
 Note: RT = reaction time (ms); training type = training condition (untrained vs. naming vs. tying vs. both); pid = subject/participant identifier; ndt = non-decision time.
-
-The priors we used followed a weakly informative approach and are reported in Supplementary Table 1.
 

### 2024-12-06 manuscript/supplementary/supplementary.tex
minor tweaks

@@
 Note: RT = reaction time (ms); training type = training condition (untrained vs.~naming vs.~tying vs.~both); pid = subject/participant identifier; ndt = non-decision time.
-
-The priors we used followed a weakly informative approach and are reported in Supplementary Table 1.
 

### 2024-12-09 manuscript/supplementary/supplementary.Rmd
updated supps

@@
 
-```{r papaja-terms-settings}
-# supp_terms <- getOption("papaja.terms")
-# supp_terms$table <- "Supplementary Table"
-# supp_terms$figure <- "Supplementary Figure"
-# options("papaja.terms" = supp_terms) 
-```
+<!-- the below two lines directly change the default Figure and Table naming to Supplementary -->
+<!-- see here for more details - https://stackoverflow.com/questions/47173279/internationalization-r-knitr-figure-caption-label -->
 
-# Supplementary Materials #
+\renewcommand{\figurename}{Supplementary Figure}
+\renewcommand{\tablename}{Supplemetentary Table}
 
-## Analysis of Observed Variables ##
+# Supplementary Materials
 
-In addition to our evidence accumulation modelling analysis, we first analysed accuracy and reaction time (RT).
-Analyses was conducted using a Bayesian estimation approach to multilevel modelling (McElreath, 2020).
-Specifically, we used the Bayesian modelling package “brms” to run multilevel models in the R (Bürkner, 2017).
+## Analysis of Observed Variables
+
+In addition to our evidence accumulation modelling analysis, we also analysed accuracy and reaction time (RT) data separately using multi-level regression.
+To do so, we used a Bayesian estimation approach to regression (McElreath, 2020).
+Specifically, we used the R package “brms” to build multi-level regression models (Bürkner, 2017).
 
@@
 Model 0 for both accuracy and reaction time were intercept only models so that we could compare all subsequent models that included effects of interest to a model without any predictors.
-The most complex model included an effect of training type (naming, tying, both, untrained).
-Shifted lognormal model was used to fit reaction time, while accuracy data was fit with a Bernoulli model.
-Priors were set using a weakly informative approach (see Supplementary Table 1 for all priors used for modelling) (Gelman, 2006).
-The formula for the full model (Model 1) used to fit reaction time data is specified below:
+The most complex model included an effect of training type (untrained, name, tie, both).
+A shifted lognormal model was used to fit reaction time data, whereas accuracy data was fit with a Bernoulli model.
+Priors were set using a weakly informative approach (Gelman, 2006).
+Supplementary Table 1 provides details of the priors used in these models.
+The formulas for the full models (Model 1) used to fit reaction time and accuracy data are specified below: $$rt \sim 1 + training type + \\
+(1 + training type | pid), \\
+ndt \sim (1 | pid)$$ $$acc \sim 1 + training type + \\
+(1 + training type | pid)$$ *Note:* RT = reaction time (ms); acc= accuracy (0,1); training type = training condition (untrained vs.
+naming vs.
+tying vs.
+both); pid = subject/participant identifier; ndt = non-decision time.
 
-$$rt \sim 1 + training type + \\
-(1 + training type | pid), \\
-ndt \sim (1 | pid)$$
-
-Note: RT = reaction time (ms); training type = training condition (untrained vs. naming vs. tying vs. both); pid = subject/participant identifier; ndt = non-decision time.
-
-(ref:prior-table-caption) Priors used for models.
+(ref:prior-table-caption) Priors used for the separate analysis of RT and accuracy data.
 
@@
 
+\newpage
+
 There was some evidence for relatively small effects of training type on accuracy (see Supplementary Figure 1A).
 The posterior distribution for the effect of each training type overlapped with zero, but did have values which fell mainly below or above zero.
-This suggests that relative to the untrained condition accuracy was lower in both the tying and naming conditions, but slighly higher in the combined condition.
+This suggests that relative to the untrained condition, accuracy was lower in both the tying and naming conditions, but slighly higher in the combined condition.
 
-There also appeared to be an effect of training type on RT (see Supplementary Figure 1B).
+There also appeared to be relatively small effects of training type on RT (see Supplementary Figure 1B).
 Inspection of the posterior distribution for the fixed effects of training type revealed values which primarily fell below zero.
@@
 Points represent the median value of the posterior distribution for that estimate, the thicker line represents 66th percentile, while the thinner line is the 95th percentile of the distribution.
-The untrained condition was the reference group.
+The untrained condition was the reference group in these regression models.
 
@@
 
-## LBA Analysis ##
+## LBA Analysis
 
-### Sampling ###
+### Sampling
 
-For each model we used three times as many chains were used as model parameters.
+As much as possible, we used settings that were recommended for hierarchical sampling by the authors of the DMC software (Heathcote et al., 2019).
 Sampling was carried out in two steps.
@@
 During the initial burn-in-period there was a probability of .05 that a crossover step was replaced with a migration step.
-After burn in only crossover steps were used and sampling continued until the proportional scale reduction factor ($\hat{R}$) was less than 1.1 for all parameters, and also the multivariate version was less than 1.1 (Brooks & Gelman, 1998).
+After burn-in only crossover steps were used and sampling continued until the proportional scale reduction factor ($\hat{R}$) was less than 1.1 for all parameters, and also the multivariate version was less than 1.1 (Brooks & Gelman, 1998).
 Hierarchical estimation assumed independent normal population distributions for each model parameter.
@@
 The final set of chains were also inspected visually to confirm convergence.
+For each model we used three times as many chains as model parameters.
 
-### Priors ###
+### Priors
 
@@
 The sv parameter for the matching accumulator had a prior mean of 0.5.
-The t0 parameter had a prior mean of 0.3s.
+The t0 parameter had a prior mean of 0.2s.
 All priors had a standard deviation of 2.
 Mean parameters of population distributions were assumed to have priors of the same form as for individual estimation, and the standard deviations of hyper parameters were assumed to have exponential distributions with a scale parameter of one.
-Plots of prior and posterior distributions revealed strong updating (i.e., posteriors dominated priors), making it clear that the prior assumptions had little influence on posterior estimates (see Supplementary Figure 2 for an example of how the priors were updated for hyperparameters).
+
+(ref:prior-lba-table-caption) Priors used for the LBA analysis.
+
+(ref:prior-lba-table-note) A = start point; B = threshold; mean_v_true = mean drift rate for correct responses; mean_v_false = mean drift rate for incorrect responses; sd_v_true = standard deviation of the mean drift rate for correct responses; SD = standard deviation; lb = lower bound; ub = upper bound.
+Two variables were given constant values to enable model fitting and these were set as follows: sd_v_false = 1, st0 = 0.
+
+```{r prior-lba-table}
+prior_lba_table <- tibble(
+  parameter = c("A", "B", "t0", "mean_v_true", "mean_v_false", "sd_v_true", "sd_v_false", "st0"),
+  mean = c(1, .5, .2, 1, 0, .5, 1, 0),
+  sd = c(rep(2, times = 6), NA, NA),
+  lb = c(0, 0, 0.1, NA, NA, NA, NA, NA),
+  ub = c(NA, NA, 1, NA, NA, NA, NA, NA)
+) %>%
+  mutate(across(everything(), ~as.character(.x))) %>% 
+  mutate(across(everything(), ~replace_na(.x, "-")))
+
+apa_table(
+  prior_lba_table,
+  caption = "(ref:prior-lba-table-caption)",
+  note = "(ref:prior-lba-table-note)"
+) 
+```
+
+\newpage
+
+Plots of prior and posterior distributions revealed strong updating (i.e., posteriors dominated priors), making it clear that the prior assumptions had little influence on posterior estimates (see Supplementary Figure 2).
 
@@
 
-### Model fit ###
+### Model fit
 
-Supplementary Figures 3 display the fits of the LBA model to the data in terms of defective cumulative distribution functions (lines) and 10th, 30th, 50th, 70th and 90th percentiles (points from left to right) averaged over participants.
-Thick black lines and open points correspond to the data and the think grey lines solid black points to the model prediction averaged over posterior samples.
+Supplementary Figures 3 displays the fits of the LBA model to the data in terms of defective cumulative distribution functions (lines) and 10th, 30th, 50th, 70th and 90th percentiles (points from left to right) averaged over participants.
+Thick black lines and open points correspond to the data and the thin grey lines and solid black points correspond to the model predictions averaged over posterior samples.
 The grey points correspond to percentile predictions for 100 randomly selected sets of posterior parameter samples, so their spread gives an idea of the uncertainty in the model’s predictions.
-As can be seen from the figure the average fit of the selected LBA model was reasonable.
+As can be seen from the Supplementary Figure 3, the average fit of the selected LBA model was reasonable.
 
 (ref:model-fit-caption) Cumulative distribution functions for data (thick lines) and fits (line grey lines) of the LBA model.
-Each panel contains results for both same and different responses at each level of stimulus (match and mismatch) and training type (name, tie, both, untrained).
+Each panel contains results for both same and different responses at each level of stimulus (match and mismatch) and training type (untrained, name, tie, both).
 Symbols mark the 10th, 30th, 50th, 70th and 90th percentile (solid for average fits, open for data).

### 2024-12-09 manuscript/supplementary/supplementary.tex
updated supps

@@
 
+\renewcommand{\figurename}{Supplementary Figure}
+\renewcommand{\tablename}{Supplemetentary Table}
+
 \section{Supplementary Materials}\label{supplementary-materials}
@@
 
-In addition to our evidence accumulation modelling analysis, we first analysed accuracy and reaction time (RT).
-Analyses was conducted using a Bayesian estimation approach to multilevel modelling (McElreath, 2020).
-Specifically, we used the Bayesian modelling package ``brms'' to run multilevel models in the R (Bürkner, 2017).
+In addition to our evidence accumulation modelling analysis, we also analysed accuracy and reaction time (RT) data separately using multi-level regression.
+To do so, we used a Bayesian estimation approach to regression (McElreath, 2020).
+Specifically, we used the R package ``brms'' to build multi-level regression models (Bürkner, 2017).
 
@@
 Model 0 for both accuracy and reaction time were intercept only models so that we could compare all subsequent models that included effects of interest to a model without any predictors.
-The most complex model included an effect of training type (naming, tying, both, untrained).
-Shifted lognormal model was used to fit reaction time, while accuracy data was fit with a Bernoulli model.
-Priors were set using a weakly informative approach (see Supplementary Table 1 for all priors used for modelling) (Gelman, 2006).
-The formula for the full model (Model 1) used to fit reaction time data is specified below:
-
-\[rt \sim 1 + training type + \\
+The most complex model included an effect of training type (untrained, name, tie, both).
+A shifted lognormal model was used to fit reaction time data, whereas accuracy data was fit with a Bernoulli model.
+Priors were set using a weakly informative approach (Gelman, 2006).
+Supplementary Table 1 provides details of the priors used in these models.
+The formulas for the full models (Model 1) used to fit reaction time and accuracy data are specified below: \[rt \sim 1 + training type + \\
 (1 + training type | pid), \\
-ndt \sim (1 | pid)\]
-
-Note: RT = reaction time (ms); training type = training condition (untrained vs.~naming vs.~tying vs.~both); pid = subject/participant identifier; ndt = non-decision time.
+ndt \sim (1 | pid)\] \[acc \sim 1 + training type + \\
+(1 + training type | pid)\] \emph{Note:} RT = reaction time (ms); acc= accuracy (0,1); training type = training condition (untrained vs.~naming vs.~tying vs.~both); pid = subject/participant identifier; ndt = non-decision time.
 
@@
 
-\caption{\label{tab:prior-table}Priors used for models.}
+\caption{\label{tab:prior-table}Priors used for the separate analysis of RT and accuracy data.}
 
@@
 Points represent the median value of the posterior distribution for that estimate, the thicker line represents 66th percentile, while the thinner line is the 95th percentile of the distribution.
-The untrained condition was the reference group.}\label{fig:fixef-plot}
+The untrained condition was the reference group in these regression models.}\label{fig:fixef-plot}
 \end{figure}
@@
 
-For each model we used three times as many chains were used as model parameters.
+As much as possible, we used settings that were recommended for hierarchical sampling by the authors of the DMC software (Heathcote et al., 2019).
 Sampling was carried out in two steps.
@@
 During the initial burn-in-period there was a probability of .05 that a crossover step was replaced with a migration step.
-After burn in only crossover steps were used and sampling continued until the proportional scale reduction factor (\(\hat{R}\)) was less than 1.1 for all parameters, and also the multivariate version was less than 1.1 (Brooks \& Gelman, 1998).
+After burn-in only crossover steps were used and sampling continued until the proportional scale reduction factor (\(\hat{R}\)) was less than 1.1 for all parameters, and also the multivariate version was less than 1.1 (Brooks \& Gelman, 1998).
 Hierarchical estimation assumed independent normal population distributions for each model parameter.
@@
 The final set of chains were also inspected visually to confirm convergence.
+For each model we used three times as many chains as model parameters.
 
@@
 The sv parameter for the matching accumulator had a prior mean of 0.5.
-The t0 parameter had a prior mean of 0.3s.
+The t0 parameter had a prior mean of 0.2s.
 All priors had a standard deviation of 2.
 Mean parameters of population distributions were assumed to have priors of the same form as for individual estimation, and the standard deviations of hyper parameters were assumed to have exponential distributions with a scale parameter of one.
-Plots of prior and posterior distributions revealed strong updating (i.e., posteriors dominated priors), making it clear that the prior assumptions had little influence on posterior estimates (see Supplementary Figure 2 for an example of how the priors were updated for hyperparameters).
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:prior-lba-table}Priors used for the LBA analysis.}
+
+\begin{tabular}{lllll}
+\toprule
+parameter & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{sd} & \multicolumn{1}{c}{lb} & \multicolumn{1}{c}{ub}\\
+\midrule
+A & 1 & 2 & 0 & -\\
+B & 0.5 & 2 & 0 & -\\
+t0 & 0.2 & 2 & 0.1 & 1\\
+mean\_v\_true & 1 & 2 & - & -\\
+mean\_v\_false & 0 & 2 & - & -\\
+sd\_v\_true & 0.5 & 2 & - & -\\
+sd\_v\_false & 1 & - & - & -\\
+st0 & 0 & - & - & -\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} A = start point; B = threshold; mean\_v\_true = mean drift rate for correct responses; mean\_v\_false = mean drift rate for incorrect responses; sd\_v\_true = standard deviation of the mean drift rate for correct responses; SD = standard deviation; lb = lower bound; ub = upper bound.
+Two variables were given constant values to enable model fitting and these were set as follows: sd\_v\_false = 1, st0 = 0.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\newpage
+
+Plots of prior and posterior distributions revealed strong updating (i.e., posteriors dominated priors), making it clear that the prior assumptions had little influence on posterior estimates (see Supplementary Figure 2).
 
@@
 
-Supplementary Figures 3 display the fits of the LBA model to the data in terms of defective cumulative distribution functions (lines) and 10th, 30th, 50th, 70th and 90th percentiles (points from left to right) averaged over participants.
-Thick black lines and open points correspond to the data and the think grey lines solid black points to the model prediction averaged over posterior samples.
+Supplementary Figures 3 displays the fits of the LBA model to the data in terms of defective cumulative distribution functions (lines) and 10th, 30th, 50th, 70th and 90th percentiles (points from left to right) averaged over participants.
+Thick black lines and open points correspond to the data and the thin grey lines and solid black points correspond to the model predictions averaged over posterior samples.
 The grey points correspond to percentile predictions for 100 randomly selected sets of posterior parameter samples, so their spread gives an idea of the uncertainty in the model's predictions.
-As can be seen from the figure the average fit of the selected LBA model was reasonable.
+As can be seen from the Supplementary Figure 3, the average fit of the selected LBA model was reasonable.
 
@@
 \caption{Cumulative distribution functions for data (thick lines) and fits (line grey lines) of the LBA model.
-Each panel contains results for both same and different responses at each level of stimulus (match and mismatch) and training type (name, tie, both, untrained).
+Each panel contains results for both same and different responses at each level of stimulus (match and mismatch) and training type (untrained, name, tie, both).
 Symbols mark the 10th, 30th, 50th, 70th and 90th percentile (solid for average fits, open for data).

### 2024-12-09 manuscript/supplementary/supplementary.Rmd
updated formula text spacing

@@
 <!-- the below two lines directly change the default Figure and Table naming to Supplementary -->
+
 <!-- see here for more details - https://stackoverflow.com/questions/47173279/internationalization-r-knitr-figure-caption-label -->
@@
 Supplementary Table 1 provides details of the priors used in these models.
-The formulas for the full models (Model 1) used to fit reaction time and accuracy data are specified below: $$rt \sim 1 + training type + \\
+The formulas for the full models (Model 1) used to fit reaction time and accuracy data are specified below:
+$$rt \sim 1 + training type + \\
 (1 + training type | pid), \\
-ndt \sim (1 | pid)$$ $$acc \sim 1 + training type + \\
-(1 + training type | pid)$$ *Note:* RT = reaction time (ms); acc= accuracy (0,1); training type = training condition (untrained vs.
-naming vs.
-tying vs.
-both); pid = subject/participant identifier; ndt = non-decision time.
+ndt \sim (1 | pid)$$ 
+$$acc \sim 1 + training type + \\
+(1 + training type | pid)$$ 
+*Note:* RT = reaction time (ms); acc= accuracy (0,1); training type = training condition (untrained vs. naming vs. tying vs. both); pid = subject/participant identifier; ndt = non-decision time.
 

### 2024-12-09 manuscript/supplementary/supplementary.tex
updated formula text spacing

@@
 Supplementary Table 1 provides details of the priors used in these models.
-The formulas for the full models (Model 1) used to fit reaction time and accuracy data are specified below: \[rt \sim 1 + training type + \\
+The formulas for the full models (Model 1) used to fit reaction time and accuracy data are specified below:
+\[rt \sim 1 + training type + \\
 (1 + training type | pid), \\
-ndt \sim (1 | pid)\] \[acc \sim 1 + training type + \\
-(1 + training type | pid)\] \emph{Note:} RT = reaction time (ms); acc= accuracy (0,1); training type = training condition (untrained vs.~naming vs.~tying vs.~both); pid = subject/participant identifier; ndt = non-decision time.
+ndt \sim (1 | pid)\]
+\[acc \sim 1 + training type + \\
+(1 + training type | pid)\]
+\emph{Note:} RT = reaction time (ms); acc= accuracy (0,1); training type = training condition (untrained vs.~naming vs.~tying vs.~both); pid = subject/participant identifier; ndt = non-decision time.
 

### 2025-02-03 manuscript/manuscript.Rmd
updated the manuscript and supps to reflect editor feedback

@@
 In addition, the hypotheses and planned analysis for this paper were preregistered in advance (see our pre-registration here: [https://aspredicted.org/6ztj-45s5.pdf](https://aspredicted.org/6ztj-45s5.pdf)).
+Given that we used secondary data in this study, we did not have a stopping rule in terms of data collection because we did not collect any data.
+Instead, we simply aimed to use as much of the existing data as possible basd on availability.
+
 We deviated from our pre-registration in one way.
@@
 This study used fMRI to examine brain activity whilst participants completed a speeded perceptual discrimination task before and after training.
-The data used in the current study, therefore, were collected in or before 2012.
+The data used in the current study, therefore, were collected in 2006.
 Training consisted of participants learning to name 10 knots, tie 10 knots and name and tie a further 10 knots, while a final 10 knots remained untrained (i.e., no information about how to tie the knot or what it was called was experienced during the training period).
@@
 The decision to include only the final training session in the LBA model meant that a further two participants were excluded from modelling as they did not complete the final session of the perceptual discrimination task.
-Therefore, 18 participants were included in the present study (M = 19.4 years, age ranged from 17 – 27 years).
+Therefore, 18 participants, all right-handed (Oldfield, 1971) and neurologically healthy undergraduate and graduate students, were included in the present study (M = 19.4 years, age ranged from 17 – 27 years).
+We do not have access to information on the gender of participants, but we note from the original publication that of the 20 participants that completed the fMRI component of the study, 14 were female (Cross et al., 2012).
+This means that our sample of 18 participants is predominantly female.
+
 Second, unlike Cross and colleagues who included the post-training session across all five days in their analysis of accuracy and RT, we included only the post-training session on the final day of training (Day 5 post-training).
@@
 
+Similarly, while we had originally planned to model the difference between the pre- and post-training data for each participant, due to model complexity we were limited to including the post-training session only.
+It is possible, therefore, that improved post-training scores in the trained conditions, rather than reflecting the operation of training, may instead be due to unbalanced pre-test scores between these conditions.
+However, it should be noted that there were no clear and obvious differences in RT or accuracy in the day 1, session 1 data (i.e., before any training had started; see supplementary materials).
+Therefore, we consider it quite unlikely that random variation in pre-training differences between conditions could account for our findings.
+
+In using secondary data analysis in the present study, we were also limited in what data was available for analysis.
+Indeed, we determined our sample size by aiming to use as much of the existing data as was possible.
+Consequently, the likely precision of our parameter estimates is unknown.
+Given this limitation, it’s important for future studies look to replicate the findings in the present study.
+
 It is also important to acknowledge constraints on the generality of our findings [@simons2017].

### 2025-02-03 manuscript/manuscript.tex
updated the manuscript and supps to reflect editor feedback

@@
 In addition, the hypotheses and planned analysis for this paper were preregistered in advance (see our pre-registration here: \url{https://aspredicted.org/6ztj-45s5.pdf}).
+Given that we used secondary data in this study, we did not have a stopping rule in terms of data collection because we did not collect any data.
+Instead, we simply aimed to use as much of the existing data as possible basd on availability.
+
 We deviated from our pre-registration in one way.
@@
 The decision to include only the final training session in the LBA model meant that a further two participants were excluded from modelling as they did not complete the final session of the perceptual discrimination task.
-Therefore, 18 participants were included in the present study (M = 19.4 years, age ranged from 17 -- 27 years).
+Therefore, 18 participants, all right-handed (Oldfield, 1971) and neurologically healthy undergraduate and graduate students, were included in the present study (M = 19.4 years, age ranged from 17 -- 27 years).
+We do not have access to information on the gender of participants, but we note from the original publication that of the 20 participants that completed the fMRI component of the study, 14 were female (Cross et al., 2012).
+This means that our sample of 18 participants is predominantly female.
+
 Second, unlike Cross and colleagues who included the post-training session across all five days in their analysis of accuracy and RT, we included only the post-training session on the final day of training (Day 5 post-training).
@@
 Future studies should, therefore, look to collect enough data per session to enable a computational modelling approach that can examine the time course of learning at both the trial and session level.
+
+Similarly, while we had originally planned to model the difference between the pre- and post-training data for each participant, due to model complexity we were limited to including the post-training session only.
+It is possible, therefore, that improved post-training scores in the trained conditions, rather than reflecting the operation of training, may instead be due to unbalanced pre-test scores between these conditions.
+However, it should be noted that there were no clear and obvious differences in RT or accuracy in the day 1, session 1 data (i.e., before any training had started; see supplementary materials).
+Therefore, we consider it quite unlikely that random variation in pre-training differences between conditions could account for our findings.
+
+In using secondary data analysis in the present study, we were also limited in what data was available for analysis.
+Indeed, we determined our sample size by aiming to use as much of the existing data as was possible.
+Consequently, the likely precision of our parameter estimates is unknown.
+Given this limitation, it's important for future studies look to replicate the findings in the present study.
 

### 2025-02-03 manuscript/supplementary/supplementary.Rmd
updated the manuscript and supps to reflect editor feedback

@@
 
+### Day 1, Session 1 Data ###
+
+We also visually checked for any clear and obvious differences between training conditions that could have existed before any training had occurred (see Supplementary Figure 2). 
+In other words, we checked for random pre-training differences in RT and accuracy that might have existed in the Day 1, Session 1 data.
+
+(ref:day1-caption) Accuracy and Reaction Time by Training Type for the Day 1 and Session 1 data (i.e., before any training had occurred).
+(A) Percent correct on the perceptual discrimination task by training type.
+(B) Mean reaction time (ms) on the perceptual discrimination task by training type.
+Black points denote group means, while error bars represent within subjects’ standard errors of the mean.
+Grey points denote individual subject means.
+
+```{r day1-plot, fig.cap = "(ref:day1-caption)"}
+knitr::include_graphics("../../figures/descriptive/day1_session1_violin_acc_rt.jpeg")
+```
+
+At least in terms of accuracy and RT when analysed separately, there appears to be no clear and obvious pre-training differences between the conditions.
+Moreover, for RTs, any small numerical differences between conditions are in the opposite direction to the effect of training that we observed in RT, which is that trained conditions became faster than the untrained condition.
+Therefore, it seems unlikely that pre-existing, chance differences between conditions could account for our findings.
+
 ## LBA Analysis
@@
 
-Plots of prior and posterior distributions revealed strong updating (i.e., posteriors dominated priors), making it clear that the prior assumptions had little influence on posterior estimates (see Supplementary Figure 2).
+Plots of prior and posterior distributions revealed strong updating (i.e., posteriors dominated priors), making it clear that the prior assumptions had little influence on posterior estimates (see Supplementary Figure 3).
 
@@
 
-Supplementary Figures 3 displays the fits of the LBA model to the data in terms of defective cumulative distribution functions (lines) and 10th, 30th, 50th, 70th and 90th percentiles (points from left to right) averaged over participants.
+Supplementary Figures 4 displays the fits of the LBA model to the data in terms of defective cumulative distribution functions (lines) and 10th, 30th, 50th, 70th and 90th percentiles (points from left to right) averaged over participants.
 Thick black lines and open points correspond to the data and the thin grey lines and solid black points correspond to the model predictions averaged over posterior samples.
 The grey points correspond to percentile predictions for 100 randomly selected sets of posterior parameter samples, so their spread gives an idea of the uncertainty in the model’s predictions.
-As can be seen from the Supplementary Figure 3, the average fit of the selected LBA model was reasonable.
+As can be seen from the Supplementary Figure 4, the average fit of the selected LBA model was reasonable.
 

### 2025-02-03 manuscript/supplementary/supplementary.tex
updated the manuscript and supps to reflect editor feedback

@@
 
+\subsubsection{Day 1, Session 1 Data}\label{day-1-session-1-data}
+
+We also visually checked for any clear and obvious differences between training conditions that could have existed before any training had occurred (see Supplementary Figure 2).
+In other words, we checked for random pre-training differences in RT and accuracy that might have existed in the Day 1, Session 1 data.
+
+\begin{figure}[H]
+
+{\centering \includegraphics[height=0.67\textheight,]{../../figures/descriptive/day1_session1_violin_acc_rt}
+
+}
+
+\caption{Accuracy and Reaction Time by Training Type for the Day 1 and Session 1 data (i.e., before any training had occurred).
+(A) Percent correct on the perceptual discrimination task by training type.
+(B) Mean reaction time (ms) on the perceptual discrimination task by training type.
+Black points denote group means, while error bars represent within subjects' standard errors of the mean.
+Grey points denote individual subject means.}\label{fig:day1-plot}
+\end{figure}
+
+At least in terms of accuracy and RT when analysed separately, there appears to be no clear and obvious pre-training differences between the conditions.
+Moreover, for RTs, any small numerical differences between conditions are in the opposite direction to the effect of training that we observed in RT, which is that trained conditions became faster than the untrained condition.
+Therefore, it seems unlikely that pre-existing, chance differences between conditions could account for our findings.
+
 \subsection{LBA Analysis}\label{lba-analysis}
@@
 
-Supplementary Figures 3 displays the fits of the LBA model to the data in terms of defective cumulative distribution functions (lines) and 10th, 30th, 50th, 70th and 90th percentiles (points from left to right) averaged over participants.
+Supplementary Figures 4 displays the fits of the LBA model to the data in terms of defective cumulative distribution functions (lines) and 10th, 30th, 50th, 70th and 90th percentiles (points from left to right) averaged over participants.
 Thick black lines and open points correspond to the data and the thin grey lines and solid black points correspond to the model predictions averaged over posterior samples.
 The grey points correspond to percentile predictions for 100 randomly selected sets of posterior parameter samples, so their spread gives an idea of the uncertainty in the model's predictions.
-As can be seen from the Supplementary Figure 3, the average fit of the selected LBA model was reasonable.
+As can be seen from the Supplementary Figure 4, the average fit of the selected LBA model was reasonable.
 

### 2025-04-01 manuscript/manuscript.Rmd
minor updates to the manuscript

@@
     affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "School of Psychological Sciences, 16 University Avenue, Macquarie University, NSW 2109"
-    email         : "samantha.parker@students.mq.edu.au"
+    # corresponding : yes    # Define only one corresponding author
+    # address       : "School of Psychological Sciences, 16 University Avenue, Macquarie University, NSW 2109"
+    # email         : "samantha.parker@students.mq.edu.au"
     role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
@@
     affiliation   : "2"
+    corresponding : yes    # Define only one corresponding author
+    email         : "richard.ramsey@hest.ethz.ch"
     role:
@@
 
-  *Public significance statement:* The results of this study show that multi-modal training, which spans linguistic and action-based content, increases the quality of information that is gained through perception to make a decision.
+  <!-- *Public significance statement:* The results of this study show that multi-modal training, which spans linguistic and action-based content, increases the quality of information that is gained through perception to make a decision.
 These results provide a novel computational account of performance benefits that are often observed from multi-modal training, which will aid theory development on learning and plasticity within cognitive science.
+-->
 
@@
 keywords          : "evidence accumulation modelling, training, learning, action, naming, cognitive mechanisms, plasticity"
-wordcount         : "6698"
+wordcount         : "6967"
 bibliography      : ["references.bib", "r-references.bib"]
@@
 
-We applied the LBA model to a previously published dataset from Cross and colleagues (2012).
-This study used fMRI to examine brain activity whilst participants completed a speeded perceptual discrimination task before and after training.
+We applied the LBA model to a previously published dataset from (Cross et al., 2012).
+Cross and colleagues (2012) used fMRI to examine brain activity whilst participants completed a speeded perceptual discrimination task before and after training.
 The data used in the current study, therefore, were collected in 2006.
@@
 There was some evidence of an effect of training type on accuracy (see Figure 1A).
-Relative to the untrained condition (M = 87.4, SD = 33.3) accuracy was higher for knots that received both naming and tying training (M = 88.9, SD = 31.5), but was lower in both the tying (M = 85.1, SD = 35.6) and naming conditions (M = 83.8, SD = 36.9).
-There also appeared to be an effect of training type in RT (see Figure 1B) relative to knots that received no training (M = 1139 ms, SD = 345 ms), participants responded faster to knots that received naming training (M = 1055 ms, SD = 347 ms), tying training (M = 1119 ms, SD = 356 ms) and knots that received both naming and tying training tying training (M = 1082 ms, SD = 344 ms).
+Relative to the untrained condition (M = 87.4, SEM = 7.84) accuracy was higher for knots that received both naming and tying training (M = 88.9, SEM = 7.42), but was lower in both the tying (M = 85.1, SEM = 8.40) and naming conditions (M = 83.8, SEM = 8.71).
+There also appeared to be an effect of training type in RT (see Figure 1B) relative to knots that received no training (M = 1139 ms, SEM = 81.2 ms), participants responded faster to knots that received naming training (M = 1055 ms, SEM = 81.9 ms), tying training (M = 1119 ms, SEM = 83.9 ms) and knots that received both naming and tying training tying training (M = 1082 ms, SEM = 81.1 ms).
 
@@
 
-Inspection of the posterior distributions for the threshold parameter of the LBA model revealed evidence to suggest that thresholds significantly differed by Training Type.
+Inspection of the posterior distributions for the threshold parameter of the LBA model revealed evidence to suggest that thresholds differed by Training Type.
 Specifically, thresholds were lower in all three training conditions, naming (0.76 [0.64, 0.88]), tying, (0.68 [0.57, 0.79]) and both naming and tying training (1.01 [0.84, 1.19]) relative to the untrained condition (2.80 [2.60, 3.03]) (see Figure 2A).
@@
 
-The aim of the present study was to use evidence accumulation modelling to investigate the cognitive mechanisms that underlie linguistic and action-based training in a simple knot-tying and knot-naming task.
+The aim of the present study was to use evidence accumulation modelling to investigate the cognitive mechanisms that underlie linguistic and action-based training in a knot-tying and knot-naming task.
 Our results revealed that the effects of training are multifaceted, in terms of the latent cognitive processes involved.
@@
 
-A second interpretation is that the unique combination of linguistic and action-based training may somehow enhance the quality and quantity of information accumulation during decision making.
-Such a qualitative interpretation would be consistent with prior studies that have reported multi-modal training protocols to lead to greater improvements in cognitive functions such as visuospatial working and episodic memory, executive functioning and the speed of information processing than single-function training protocols, as well as studies that report multi-model training protocols to engage a broad network of sensorimotor brain regions more than unimodal training protocols [@kirschAdditiveRoutesAction2015].
+A second interpretation is that the unique combination of linguistic and action-based training may lead to a qualitative difference in information accumulation during decision making.
+Such a qualitative interpretation would be consistent with prior studies that have shown that compared to uni-modal training protocols, multi-modal training leads to greater improvements in cognitive domains such as working memory and propblem solving [@ward2017], as well as greater engagement of a broad network of sensorimotor brain regions [@kirschAdditiveRoutesAction2015].
 In the present study, we were unable to tease apart whether the results reflect a dose-response effect or instead reflect a qualitatively different impact of multi-modal training.

### 2025-04-01 manuscript/manuscript.tex
minor updates to the manuscript

@@
 \makeatother
-\keywords{evidence accumulation modelling, training, learning, action, naming, cognitive mechanisms, plasticity\newline\indent Word count: 6698}
+\keywords{evidence accumulation modelling, training, learning, action, naming, cognitive mechanisms, plasticity\newline\indent Word count: 6967}
 \usepackage{lineno}
@@
 
-Correspondence concerning this article should be addressed to Samantha Parker, School of Psychological Sciences, 16 University Avenue, Macquarie University, NSW 2109.
-E-mail: \href{mailto:samantha.parker@students.mq.edu.au}{\nolinkurl{samantha.parker@students.mq.edu.au}}
+Correspondence concerning this article should be addressed to Richard Ramsey. E-mail: \href{mailto:richard.ramsey@hest.ethz.ch}{\nolinkurl{richard.ramsey@hest.ethz.ch}}
 
@@
 Overall, in applying this computational approach to accuracy and reaction time data, we uncover new insights into the mechanisms that govern experience-dependent plasticity.
-
-\emph{Public significance statement:} The results of this study show that multi-modal training, which spans linguistic and action-based content, increases the quality of information that is gained through perception to make a decision.
-These results provide a novel computational account of performance benefits that are often observed from multi-modal training, which will aid theory development on learning and plasticity within cognitive science.
 }
@@
 
-Inspection of the posterior distributions for the threshold parameter of the LBA model revealed evidence to suggest that thresholds significantly differed by Training Type.
+Inspection of the posterior distributions for the threshold parameter of the LBA model revealed evidence to suggest that thresholds differed by Training Type.
 Specifically, thresholds were lower in all three training conditions, naming (0.76 {[}0.64, 0.88{]}), tying, (0.68 {[}0.57, 0.79{]}) and both naming and tying training (1.01 {[}0.84, 1.19{]}) relative to the untrained condition (2.80 {[}2.60, 3.03{]}) (see Figure 2A).
@@
 
-A second interpretation is that the unique combination of linguistic and action-based training may somehow enhance the quality and quantity of information accumulation during decision making.
-Such a qualitative interpretation would be consistent with prior studies that have reported multi-modal training protocols to lead to greater improvements in cognitive functions such as visuospatial working and episodic memory, executive functioning and the speed of information processing than single-function training protocols, as well as studies that report multi-model training protocols to engage a broad network of sensorimotor brain regions more than unimodal training protocols (Kirsch \& Cross, 2015).
+A second interpretation is that the unique combination of linguistic and action-based training may lead to a qualitative difference in information accumulation during decision making.
+Such a qualitative interpretation would be consistent with prior studies that have shown that compared to uni-modal training protocols, multi-modal training leads to greater improvements in cognitive domains such as working memory and propblem solving (Ward et al., 2017), as well as greater engagement of a broad network of sensorimotor brain regions (Kirsch \& Cross, 2015).
 In the present study, we were unable to tease apart whether the results reflect a dose-response effect or instead reflect a qualitatively different impact of multi-modal training.
@@
 It may also be one reason for the wide variety of training-induced outcomes that are observed across different tasks and training protocols, as it is possible that different types and amounts of training can impact underlying cognitive processes in different ways.
-And this is one clear benefit to understanding cognitive processes that is provided by taking a more mathematical approach to theory building in psychology and cognitive neuroscience, as it forces a more explicit formulation of the relationship between parts of a system that are under investigation (Hintzman, 1991; Yarkoni, 2022/ed).
+And this is one clear benefit to understanding cognitive processes that is provided by taking a more mathematical approach to theory building in psychology and cognitive neuroscience, as it forces a more explicit formulation of the relationship between parts of a system that are under investigation (Hintzman, 1991; Yarkoni, 2022).
 
@@
 
+\bibitem[\citeproctext]{ref-ward2017}
+Ward, N., Paul, E., Watson, P., Cooke, G.
+E., Hillman, C.
+H., Cohen, N.
+J., \ldots{} Barbey, A.
+K.
+(2017).
+Enhanced {Learning} through {Multimodal Training}: {Evidence} from a {Comprehensive Cognitive}, {Physical Fitness}, and {Neuroscience Intervention}.
+\emph{Scientific Reports}, \emph{7}(1), 5808.
+\url{https://doi.org/10.1038/s41598-017-06237-5}
+
 \bibitem[\citeproctext]{ref-weisberg2007}
@@
 \bibitem[\citeproctext]{ref-yarkoni2022}
-Yarkoni, T. (2022/ed). The generalizability crisis. \emph{Behavioral and Brain Sciences}, \emph{45}, e1. \url{https://doi.org/10.1017/S0140525X20001685}
+Yarkoni, T. (2022). The generalizability crisis. \emph{Behavioral and Brain Sciences}, \emph{45}, e1. \url{https://doi.org/10.1017/S0140525X20001685}
 

### 2025-04-01 manuscript/manuscript.Rmd
Minor updates

@@
     corresponding : yes    # Define only one corresponding author
+    address       : "ETH Zurich"
     email         : "richard.ramsey@hest.ethz.ch"

### 2025-04-29 sim_data.Rmd
added a script to simulate data for code checking purposes

---
title: "sim_data"
author: "Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file takes fitted regression models from the manifest analysis and uses them to simulate RT and accuracy data that has similar properties to the real data.

Since we cannot share the original data publicly because the ethical approval was not in place to do so when the data were collected in 2006, the purpose of this simulated data is to allow others to check the coding pipeline that we used.

Therefore, using this data will NOT produce the same results as we report in the manuscript, since the data are different. But the simulated data should resemble the structure of the real data.

Also note that for simplicity, we just use the manifest regression models and not the LBA models to generate reaction time and accuracy data. The reason for doing so is that our main aim is to provide fairly similar data to the original so that folks can reproduce our analytical pipeline, rather than any other aim that might rely on the specifics of using a LBA model.

# load libraries #

```{r load-pkg}
pkg <- c("tidyverse", "RColorBrewer", "patchwork", "brms", "tidybayes", 
         "ggdist", "future", "bayesplot", "cmdstanr", "parallel", "rstan")

lapply(pkg, library, character.only = TRUE)
```

# plot settings #

theme settings for ggplot

```{r, eval = F}
theme_set(
  theme_bw() +
    theme(text = element_text(size = 18, face = "bold"), 
          title = element_text(size = 18, face = "bold"),
          legend.position = "bottom")
)

## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)
```

# package settings #

```{r}
options(brms.backend = "cmdstanr",
        mc.cores = parallel::detectCores(),
        future.fork.enable = TRUE,
        future.rng.onMisuse = "ignore") ## automatically set in RStudio

rstan_options(auto_write = TRUE)

supportsMulticore()

detectCores()
```

# 1. load the models and the raw (original) data #

models

```{r}
## rt
b1 <- readRDS("models/manifest/b1.rds")

## accuracy
ab1 <- readRDS("models/manifest/ab1.rds")
```

data

```{r}
# rt data
data_rt <- read_csv("data/processed/data_rt.csv") %>% 
  mutate(PID=factor(PID),
         GROUP = factor(GROUP,
                        levels = c("untrained", "name", "tie", "both")))
head(data_rt)

# accuracy data
data_acc <- read_csv("data/processed/data_acc.csv") %>% 
    mutate(PID=factor(PID),
           GROUP = factor(GROUP,
                          levels = c("untrained", "name", "tie", "both")))
head(data_acc)
```

# 2. simulate accuracy data #

using the original data to define the design to make predictions on.

```{r}
# Step 1: Use the original data as the base for simulation
acc_preds <- data_acc %>%
  # This adds predicted values based on the posterior distribution
  add_predicted_draws(ab1,
                      seed = 123)
head(acc_preds)
glimpse(acc_preds)

# Step 2: For a single complete simulated dataset with same structure as original
acc_sim_data <- acc_preds %>%
  group_by(.row) %>%
  slice_sample(n = 1) %>%  # Take one random prediction per original observation
  ungroup()
head(acc_sim_data)
glimpse(acc_sim_data)
```

## create summary data ##

at the pid level

```{r}
acc_sim_pid <- acc_sim_data %>% 
  group_by(PID, GROUP) %>% 
  summarise(sum_acc = sum(.prediction), 
            mean_acc = mean(.prediction, na.rm = TRUE) * 100, 
            sd_acc = sd(.prediction, na.rm = TRUE) * 100)
head(acc_sim_pid)
```

at the group level

```{r}
acc_sim_g <- acc_sim_data %>% 
  group_by(GROUP) %>% 
  summarise(n=length(unique(PID)),
            sum_acc = sum(.prediction), 
            mean_acc = mean(.prediction, na.rm = TRUE) * 100, 
            sd_acc = sd(.prediction, na.rm = TRUE) * 100, 
            sem_acc = (sd_acc/sqrt(n)))
acc_sim_g

# # A tibble: 4 × 6
#   GROUP         n sum_acc mean_acc sd_acc sem_acc
#   <fct>     <int>   <int>    <dbl>  <dbl>   <dbl>
# 1 untrained    18     298     85.6   35.1    8.28
# 2 name         18     290     82.6   37.9    8.94
# 3 tie          18     312     89.1   31.2    7.34
# 4 both         18     308     87.7   32.8    7.74
```

## plot accuracy ##

```{r}
p2.1 <- ggplot(acc_sim_pid, aes(x = GROUP, y = mean_acc, 
                               fill = GROUP, colour = GROUP)) +
  geom_jitter(position=position_jitterdodge(dodge.width =1), 
              size = 2.5, colour="grey") +
  geom_violin(alpha = 0.5, position=pd2) +
  geom_errorbar(data = acc_sim_g, aes(ymin=mean_acc-sem_acc,
                                         ymax=mean_acc+sem_acc), 
                width=.3, linewidth =0.5, colour = "black", position=pd2) +
  geom_point(data = acc_sim_g, colour = "black", position=pd2, size =4) +
  geom_line(data=acc_sim_g, group=1, colour = "black") +
  xlab("Training Condition") + 
  ylab('Percentage Correct') + 
  scale_fill_brewer(palette = "Dark2") +
  scale_colour_brewer(palette = "Dark2") +
  theme(legend.position = "none")
p2.1
```

That looks reasonably similar to the descriptive violin plots in the main text.

# 3. simulate reaction time data #

using the original data

```{r}
# Step 1: Use the original data as the base for simulation
# note - we still use the full data here data_acc, to make sure we get predictions for the full dataset, rather than just correct trials. But now we use the RT model to make predictions in terms of RT rather than accuracy.

rt_preds <- data_acc %>%
  # This adds predicted values based on the posterior distribution
  add_predicted_draws(b1,
                      seed = 123)
head(rt_preds)
glimpse(rt_preds)

# Step 2: For a single complete simulated dataset with same structure as original
rt_sim_data <- rt_preds %>%
  group_by(.row) %>%
  slice_sample(n = 1) %>%  # Take one random prediction per original observation
  ungroup() 
head(rt_sim_data)
glimpse(rt_sim_data)
```

## create summary rt data ##

at the pid level

```{r}
rt_sim_pid <- rt_sim_data %>% 
  group_by(PID, GROUP) %>%
  summarise(mean_rt = mean(.prediction, na.rm = TRUE), 
            sd_rt = sd(.prediction, na.rm = TRUE))
head(rt_sim_pid)
```

at the group level

```{r}
rt_sim_g <- rt_sim_data %>% 
  group_by(GROUP) %>%
  summarise(n=length(unique(PID)),
            mean_rt = mean(.prediction, na.rm = TRUE), 
            sd_rt = sd(.prediction, na.rm = TRUE), 
            sem_rt = (sd_rt/sqrt(n)))
rt_sim_g

# # A tibble: 4 × 5
#   GROUP         n mean_rt sd_rt sem_rt
#   <fct>     <int>   <dbl> <dbl>  <dbl>
# 1 untrained    18   1149.  380.   89.5
# 2 name         18   1072.  382.   90.0
# 3 tie          18   1123.  334.   78.7
# 4 both         18   1029.  301.   70.9
```

## plot rt ##

```{r}
p3.1 <- ggplot(rt_sim_pid, aes(x = GROUP, y = mean_rt, 
                               fill = GROUP, colour = GROUP)) +
  geom_jitter(position=position_jitterdodge(dodge.width =1), 
              size = 2.5, colour="grey") +
  geom_violin(alpha = 0.5, position=pd2) +
  geom_errorbar(data = rt_sim_g, aes(ymin=mean_rt-sem_rt,
                                         ymax=mean_rt+sem_rt), 
                width=.3, linewidth =0.5, colour = "black", position=pd2) +
  geom_point(data = rt_sim_g, colour = "black", position=pd2, size =4) +
  geom_line(data=rt_sim_g, group=1, colour = "black") +
  xlab("Training Condition") + 
  ylab('Mean Reaction Time (ms)') + 
  scale_fill_brewer(palette = "Dark2") +
  scale_colour_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  scale_y_continuous(limits = c(800, 1600),
                     breaks = seq(800, 1600, 200))
p3.1
```

This also looks sensible, given the descriptives from the original data.

# 4. plot accuracy and rt together #

plot together

```{r}
p4.1 <- (p2.1 | p3.1) +
  plot_annotation(tag_levels = 'A')
p4.1

ggsave("figures/simulated/violin_acc_rt.jpeg",
       width = 10, height = 6, dpi = 800)
```

# 5. wrangle to create a simulated "raw" dataset #

here we combine simulated accuracy and reaction time data and wrangle it to have the same structure as the original data.

The purpose of doing so is so that folks can use this simulated data file to test our code.

## look at the actual raw data to get a sense of the structure ##

```{r}
raw <- read_csv("data/processed/day5_post_knots_data.csv")
head(raw)

# # A tibble: 6 × 14
#     PID RESPONSE    RT  STIM GROUP PICNOS1 PICNOS2 MATCH ORTN1 ORTN2 PICID1 PICID2   DAY SESSION
#   <dbl>    <dbl> <dbl> <dbl> <dbl>   <dbl>   <dbl> <dbl> <dbl> <dbl>  <dbl>  <dbl> <dbl>   <dbl>

colnames(raw)
# [1] "PID"      "RESPONSE" "RT"       "STIM"     "GROUP"    "PICNOS1"  "PICNOS2"  "MATCH"    "ORTN1"   
# [10] "ORTN2"    "PICID1"   "PICID2"   "DAY"      "SESSION" 
```

## wrangle the predicted accuracy data ##

```{r}
sim_raw_acc <- acc_sim_data |> 
  select(PID, GROUP, MATCH, .prediction) |> 
  mutate(RESPONSE = case_when(
    MATCH == 1 & .prediction == 1 ~ 1,  # MATCH 1, correct response
    MATCH == 1 & .prediction == 0 ~ 2,  # MATCH 1, incorrect response
    MATCH == 2 & .prediction == 1 ~ 2,  # MATCH 2, correct response
    MATCH == 2 & .prediction == 0 ~ 1,  # MATCH 2, incorrect response
    TRUE ~ NA_real_                    # Handle any other cases
  )) |> 
  select(-.prediction)
head(sim_raw_acc)
```

## wrangle the predicted reaction time data ##

```{r}
sim_raw_rt <- rt_sim_data |> 
  select(PID, GROUP, MATCH, .prediction) |> 
  rename(RT = .prediction)
head(sim_raw_rt)
```

## join them acc and rt together ##

```{r}
sim_raw_acc_rt <- sim_raw_acc |>
  mutate(RT = sim_raw_rt$RT)
head(sim_raw_acc_rt)
glimpse(sim_raw_acc_rt)
```

## join with the other raw data columns ##

```{r}
sim_raw <- raw |> 
  mutate(RESPONSE = sim_raw_acc$RESPONSE,
         RT = sim_raw_rt$RT)
head(sim_raw)
glimpse(sim_raw)
```

# 6. write out the simulated data #

```{r}
write_csv(sim_raw, "data/simulated/sim_raw.csv")
```

### 2025-04-29 wrangle.Rmd
added a script to simulate data for code checking purposes

@@
 head(raw)
+```
+
+And this is the simulated data for code checking purposes, as the raw data cannot be made publicly available. 
+If you have not requested the raw data privately, then uncomment the code chunk below and run the code.
+See the sim_data.Rmd script for details on how the data were simulated. 
+Note - the simulated data resemble the real data, but they will of course produce DIFFERENT results.
+
+```{r}
+# raw <- read_csv("data/simulated/sim_raw.csv")
+# head(raw)
 ```
